---
title: 'Figures and Tables: Assessing the Utility of the EAU Risk Stratification for
  Predicting Kidney Stone Recurrence'
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: false
    keep_tex: false
    toc: true
    toc_depth: 2
    number_sections: true
  html_document:
    toc: true
    toc_depth: '2'
    df_print: paged
  word_document:
    toc: true
    toc_depth: '2'
header-includes:
- \usepackage{graphicx}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{multirow}
- \usepackage{array}
- \usepackage{longtable}
- \usepackage{makecell}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(ggplot2)
library(tidyverse)
library(meta)
library(metafor)
library(scales)
library(ggh4x)
```

\newpage
# Tables

## Table 1. High Risk Conditions as per EAU Urolithiasis Guidelines

List of conditions associated with 'high risk' disease as per EAU Urolithiasis guidelines i.e. if an individual has any one of the scenarios/conditions detailed in this table then they are labelled as high risk. Availability in each Biobank is detailed. UKB = UK Biobank, AoU = All of Us.

\begin{landscape}
\begin{longtable}{p{3.5cm}p{8cm}cc}
\toprule
\textbf{Category} & \textbf{Factor} & \textbf{Availability in UKB} & \textbf{Availability in AoU} \\
\midrule
\endfirsthead
\toprule
\textbf{Category} & \textbf{Factor} & \textbf{Availability in UKB} & \textbf{Availability in AoU} \\
\midrule
\endhead
\multirow{8}{*}{\makecell[l]{General factors}} & Early onset of urolithiasis (especially children and teenagers) & Age at first stone <25 & Age at first stone <25 \\
& Familial stone formation & Data not available & Data not available \\
& Recurrent stone formers & Available & Available \\
& Short time since last stone episode & Available & Available \\
& Brushite-containing stones (CaHPO4.2H2O) & Stone analysis not available & Stone analysis not available \\
& Uric acid and urate-containing stones & Stone analysis not available & Stone analysis not available \\
& Infection stones & Stone analysis not available & Stone analysis not available \\
& Solitary kidney & Available & Available \\
\midrule
\multirow{10}{*}{\makecell[l]{Diseases associated\\with stone formation}} & Hyperparathyroidism & Available & Available \\
& Metabolic syndrome & Available & Available \\
& Nephrocalcinosis & Available & Available \\
& Polycystic kidney disease (PKD) & Available & Available \\
& GI diseases (jejuno-ileal bypass, intestinal resection, Crohn's disease, malabsorptive conditions, enteric hyperoxaluria after urinary diversion, exocrine pancreatic insufficiency) and bariatric surgery & Available & Available \\
& Increased levels of vitamin D & Available & Available \\
& Sarcoidosis & Available & Available \\
& Spinal cord injury, neurogenic bladder & Available & Available \\
& Ureteral stricture & Available & Available \\
\midrule
\multirow{7}{*}{\makecell[l]{Genetically determined\\stone formation}} & Cystinuria (type A, B and AB) & Available & Available \\
& Primary hyperoxaluria (PH) & Available & Available \\
& Renal tubular acidosis (RTA) type I & Available & Available \\
& 2,8-Dihydroxyadeninuria & Available & Available \\
& Xanthinuria & Available & Available \\
& Lesch-Nyhan syndrome & Available & Available \\
& Cystic fibrosis & Available & Available \\
\midrule
\multicolumn{2}{l}{Drug-induced stone formation} & & \\
\midrule
\multirow{6}{*}{\makecell[l]{Anatomical abnormalities\\associated with stone\\formation}} & Medullary sponge kidney (tubular ectasia) & Available & Available \\
& Ureteropelvic junction (UPJ) obstruction & Available & Available \\
& Calyceal diverticulum, calyceal cyst & Available & Available \\
& Vesico-uretero-renal reflux & Available & Available \\
& Horseshoe kidney & Available & Available \\
& Ureterocele & Available & Available \\
\midrule
\multirow{2}{*}{\makecell[l]{Environmental and\\professional factors}} & High ambient temperatures & Not available & Not available \\
& Chronic lead and cadmium exposure & Not available & Not available \\
\bottomrule
\end{longtable}
\end{landscape}

\newpage

## Table 2. Demographics

Demographics table for those with clinically significant kidney stone disease within the two Biobanks utilised for the present study. \textsuperscript{\#} At time of first stone event. * Derived from Kaplan-Meier survival curves on the 'any event' "virtual stone clinic" dataset (every participant contributes one row per transition they reach: 1→2, 2→3, 3→4, 4→5).

```{r table2-vsc-rates, include=FALSE}
# Load the virtual-stone-clinic KM rates (one row per horizon × cohort)
# produced by the source scripts (UKB Rmd / AoU notebook).
ukb_vsc <- read.csv("UKB Recurrence paper results/virtual_stone_clinic_recurrence_rates.csv",
                    check.names = FALSE)
aou_vsc <- read.csv("AoU Recurrence paper results/virtual_stone_clinic_recurrence_rates_aou.csv",
                    check.names = FALSE)

fmt_vsc <- function(df, h) {
  row <- df[df$horizon_years == h, , drop = FALSE]
  if (nrow(row) == 0 || !is.finite(row$rec_pct)) return("--")
  sprintf("%.0f\\%% (%.0f--%.0f\\%%)",
          row$rec_pct, row$rec_lo_pct, row$rec_hi_pct)
}

vsc_2_ukb  <- fmt_vsc(ukb_vsc, 2)
vsc_5_ukb  <- fmt_vsc(ukb_vsc, 5)
vsc_10_ukb <- fmt_vsc(ukb_vsc, 10)
vsc_2_aou  <- fmt_vsc(aou_vsc, 2)
vsc_5_aou  <- fmt_vsc(aou_vsc, 5)
vsc_10_aou <- fmt_vsc(aou_vsc, 10)
```

\begin{table}[H]
\centering
\small
\begin{tabular}{llcc}
\toprule
& & \textbf{UK Biobank} & \textbf{All of Us} \\
& & \textbf{(n=8,375)} & \textbf{(n=11,182)} \\
\midrule
\multicolumn{2}{l}{Age at First clinically significant stone event, mean $\pm$SD} & 52$\pm$11 & 52$\pm$15 \\
\multicolumn{2}{l}{Men, n (\%)} & 5,850 (70\%) & 5,038 (45\%) \\
\multicolumn{2}{l}{Follow-up, median years (IQR)} & 21.9 (15.0--40.4) & 7.3 (5.0--7.5) \\
\multicolumn{2}{l}{High Risk as per EAU\textsuperscript{\#}, n (\%)} & 3,103 (37\%) & 2,032 (18.2\%) \\
\midrule
\multirow{5}{*}{\makecell[l]{Initial Presentation/\\Intervention, n (\%)}} & PCNL & 471 (6\%) & 186 (2\%) \\
& ESWL & 1,287 (15\%) & 380 (3\%) \\
& URS & 207 (3\%) & 2,410 (21\%) \\
& Open surgery & 18 (0.2\%) & 38 (0.3\%) \\
& Ureteric Colic & 6,392 (76\%) & 7,342 (66\%) \\
\midrule
\multirow{3}{*}{\makecell[l]{Recurrence Rates,\\\% (95\% CI)*}} & 2-Year  & `r vsc_2_ukb`  & `r vsc_2_aou`  \\
& 5-Year  & `r vsc_5_ukb`  & `r vsc_5_aou`  \\
& 10-Year & `r vsc_10_ukb` & `r vsc_10_aou` \\
\bottomrule
\end{tabular}
\end{table}

\newpage

## Supplementary Table 1. Numbers of Patients with High-Risk Characteristics at First event

Numbers of patients with High-Risk characteristics at time of first stone event - for each analysis risk status is (re)ascertained at the point of presentation. NB -- patients can have more than one characteristic.

\begin{landscape}
\begin{longtable}{p{3.5cm}p{8cm}cc}
\toprule
\textbf{Category} & \textbf{Factor} & \textbf{UKB, n (\%)} & \textbf{AoU, n (\%)} \\
& & \textbf{Total n = 8,375} & \textbf{Total n = 11,182} \\
\midrule
\endfirsthead
\toprule
\textbf{Category} & \textbf{Factor} & \textbf{UKB, n (\%)} & \textbf{AoU, n (\%)} \\
\midrule
\endhead
\multirow{9}{*}{\makecell[l]{General factors}} & Early onset of urolithiasis & 83 (1\%) & 479 (4\%) \\
& Familial stone formation & Data not available & Data not available \\
& Recurrent stone formers & See data above & See data above \\
& Short time since last stone episode & See data above & See data above \\
& Brushite-containing stones & Stone analysis not available & Stone analysis not available \\
& Uric acid and urate-containing stones & Stone analysis not available & Stone analysis not available \\
& Infection stones & Stone analysis not available & Stone analysis not available \\
& Solitary kidney & 168 (0.9\%) & 4 (0.04\%) \\
& Immunosuppression & 38 (0.4\%) & 181 (2\%) \\
\midrule
\multirow{9}{*}{\makecell[l]{Diseases associated\\with stone formation}} & Hyperparathyroidism & 171 (2\%) & 374 (3\%) \\
& Metabolic syndrome & 2,317 (27\%) & 254 (2\%) \\
& Nephrocalcinosis & 12 (0.1\%) & 20 (0.2\%) \\
& Polycystic kidney disease (PKD) & 53 (0.6\%) & 58 (0.5\%) \\
& GI diseases and bariatric surgery & 527 (6\%) & 953 (9\%) \\
& Increased levels of vitamin D & 0 & 0 \\
& Sarcoidosis & 45 (0.5\%) & 84 (1\%) \\
& Spinal cord injury, neurogenic bladder & 111 (1.3\%) & 155 (1\%) \\
& Ureteral stricture & 325 (4\%) & 106 (1\%) \\
\midrule
\multirow{7}{*}{\makecell[l]{Genetically determined\\stone formation}} & Cystinuria (type A, B and AB) & 0 & 0 \\
& Primary hyperoxaluria (PH) & 0 & 0 \\
& Renal tubular acidosis (RTA) type I & 0 & 0 \\
& 2,8-Dihydroxyadeninuria & 0 & 0 \\
& Xanthinuria & 0 & 0 \\
& Lesch-Nyhan syndrome & 0 & 0 \\
& Cystic fibrosis & 1 (0.1\%) & 38 (0.3\%) \\
\midrule
\multicolumn{2}{l}{Drug-induced stone formation} & & \\
\midrule
\multirow{6}{*}{\makecell[l]{Anatomical abnormalities\\associated with stone\\formation}} & Medullary sponge kidney (tubular ectasia) & 12 (0.1\%) & 20 (0.2\%) \\
& Ureteropelvic junction (UPJ) obstruction & 98 (1.1\%) & 47 (0.4\%) \\
& Calyceal diverticulum, calyceal cyst & 0 & 0 \\
& Vesico-uretero-renal reflux & 9 (0.1\%) & 29 (0.3\%) \\
& Horseshoe kidney & 2 (0.1\%) & 0 \\
& Ureterocele & 6 (0.1\%) & 0 \\
\midrule
\multirow{2}{*}{\makecell[l]{Environmental and\\professional factors}} & High ambient temperatures & Not available & Not available \\
& Chronic lead and cadmium exposure & Not available & Not available \\
\bottomrule
\end{longtable}
\end{landscape}

\newpage

## Supplementary Table 2. Analyses Performed

Explanatory table of additional sensitivity analyses and outcome analyses performed at each starting point. *X* indicates the analysis was performed; *N/A* means the analysis is not applicable to that starting point. The "Short time" between events and "recurrent disease" definitions only apply from 2nd event onwards.For the "recurrent disease" the prior events includes the current stone event.

\begin{table}[H]
\centering
\small
\begin{tabular}{p{1.5cm}|p{2.4cm}|p{2.4cm}p{1.9cm}|ccc|p{4.6cm}}
\toprule
\textbf{\makecell[l]{Analysis\\type}}
& \textbf{Starting point}
& \multicolumn{2}{c|}{\textbf{Definition Exploration}}
& \multicolumn{3}{c|}{\textbf{Outcome Analyses}}
& \textbf{Outcome description} \\
&
& \makecell{`Short time'\\definition} & \makecell{`Recurrent'\\disease\\definition}
& \textbf{KM} & \textbf{DCA} & \textbf{ROC} & \\
\midrule
\multirow{4}{*}{Per event}
& 1\textsuperscript{st} event
& N/A & N/A
& X & X & X
& \multirow{5}{=}{\textbf{KM:} 1\textsuperscript{st} \textbf{subsequent} event (time-to-event, all included).\\[4pt]\textbf{DCA + ROC:} 1, 2, 3 \textbf{subsequent} events (binary; censored <5y removed).} \\
\cmidrule(lr){2-7}
& 2\textsuperscript{nd} event
& \multirow{4}{=}{\centering 6 → 24 mo, 3-mo increments}
& \multirow{4}{=}{\centering 2, 3, 4 \textbf{prior} events}
& X & X & X & \\
\cmidrule(lr){2-2}\cmidrule(lr){5-7}
& 3\textsuperscript{rd} event
& & & X & X & X & \\
\cmidrule(lr){2-2}\cmidrule(lr){5-7}
& 4\textsuperscript{th} event
& & & X & X & X & \\
\cmidrule(lr){1-2}\cmidrule(lr){5-7}
Any event
& \makecell[l]{Any stone\\presentation\\(1\textsuperscript{st} → 4\textsuperscript{th})}
& & & X & X & X & \\
\bottomrule
\end{tabular}
\end{table}

\newpage

## Supplementary Table 3. Inter-event time by transition

Descriptive statistics of the time between consecutive stone events at each transition, derived from Kaplan Meier plots of the entire transitions dataset. The attenuation analyses (computed upstream; not shown as a panel) show that the *count* of prior events discriminates better than any binary cut-off on "short-time" between stone events.N = number of participants who experienced the *subsequent* event of each transition (e.g. second event after first event). The "Within X" rows are the cumulative proportion of patients (who recurred) whose next event occurred within the stated window.

```{r supp-table-3-inter-event, include=FALSE}
# Robust loader: if either CSV is missing, use an empty data frame with the
# expected schema so the inline `r ...` calls below still render "--" rather
# than blowing up the knit.
.iet_schema <- data.frame(
  transition = character(0), n = integer(0),
  mean_months = numeric(0), sd_months = numeric(0),
  median_months = numeric(0), q1_months = numeric(0), q3_months = numeric(0),
  pct_within_6mo = numeric(0), pct_within_1yr = numeric(0),
  pct_within_2yr = numeric(0), pct_within_5yr = numeric(0)
)
load_iet <- function(path) {
  if (file.exists(path)) {
    read.csv(path, check.names = FALSE)
  } else {
    message("Note: ", path, " not found — Sup Table 3 will render placeholders.")
    .iet_schema
  }
}
ukb_iet <- load_iet("UKB Recurrence paper results/inter_event_time_summary.csv")
aou_iet <- load_iet("AoU Recurrence paper results/inter_event_time_summary_aou.csv")

fmt_mean <- function(df, tr) {
  r <- df[df$transition == tr, , drop = FALSE]
  if (nrow(r) == 0) return("--")
  sprintf("%.1f $\\pm$ %.1f", r$mean_months, r$sd_months)
}
fmt_med <- function(df, tr) {
  r <- df[df$transition == tr, , drop = FALSE]
  if (nrow(r) == 0) return("--")
  sprintf("%.1f (%.1f--%.1f)", r$median_months, r$q1_months, r$q3_months)
}
fmt_pct <- function(df, tr, col) {
  r <- df[df$transition == tr, , drop = FALSE]
  if (nrow(r) == 0) return("--")
  sprintf("%.1f\\%%", r[[col]])
}
fmt_n <- function(df, tr) {
  r <- df[df$transition == tr, , drop = FALSE]
  if (nrow(r) == 0) return("--")
  format(r$n, big.mark = ",")
}
```

\begin{table}[H]
\centering
\small
\begin{tabular}{lcccc}
\toprule
\textbf{Transition} & \textbf{1$\rightarrow$2} & \textbf{2$\rightarrow$3} & \textbf{3$\rightarrow$4} & \textbf{4$\rightarrow$5} \\
\midrule
\multicolumn{5}{l}{\textit{UK Biobank}} \\
\midrule
N (recurred) & `r fmt_n(ukb_iet, "1→2")` & `r fmt_n(ukb_iet, "2→3")` & `r fmt_n(ukb_iet, "3→4")` & `r fmt_n(ukb_iet, "4→5")` \\
Median (IQR) (months) & `r fmt_med(ukb_iet, "1→2")` & `r fmt_med(ukb_iet, "2→3")` & `r fmt_med(ukb_iet, "3→4")` & `r fmt_med(ukb_iet, "4→5")` \\
Within 1 yr   & `r fmt_pct(ukb_iet, "1→2", "pct_within_1yr")` & `r fmt_pct(ukb_iet, "2→3", "pct_within_1yr")` & `r fmt_pct(ukb_iet, "3→4", "pct_within_1yr")` & `r fmt_pct(ukb_iet, "4→5", "pct_within_1yr")` \\
Within 2 yr   & `r fmt_pct(ukb_iet, "1→2", "pct_within_2yr")` & `r fmt_pct(ukb_iet, "2→3", "pct_within_2yr")` & `r fmt_pct(ukb_iet, "3→4", "pct_within_2yr")` & `r fmt_pct(ukb_iet, "4→5", "pct_within_2yr")` \\
Within 5 yr   & `r fmt_pct(ukb_iet, "1→2", "pct_within_5yr")` & `r fmt_pct(ukb_iet, "2→3", "pct_within_5yr")` & `r fmt_pct(ukb_iet, "3→4", "pct_within_5yr")` & `r fmt_pct(ukb_iet, "4→5", "pct_within_5yr")` \\
\midrule
\multicolumn{5}{l}{\textit{All of Us}} \\
\midrule
N (recurred) & `r fmt_n(aou_iet, "1→2")` & `r fmt_n(aou_iet, "2→3")` & `r fmt_n(aou_iet, "3→4")` & `r fmt_n(aou_iet, "4→5")` \\
Median (IQR) (months) & `r fmt_med(aou_iet, "1→2")` & `r fmt_med(aou_iet, "2→3")` & `r fmt_med(aou_iet, "3→4")` & `r fmt_med(aou_iet, "4→5")` \\
Within 1 yr   & `r fmt_pct(aou_iet, "1→2", "pct_within_1yr")` & `r fmt_pct(aou_iet, "2→3", "pct_within_1yr")` & `r fmt_pct(aou_iet, "3→4", "pct_within_1yr")` & `r fmt_pct(aou_iet, "4→5", "pct_within_1yr")` \\
Within 2 yr   & `r fmt_pct(aou_iet, "1→2", "pct_within_2yr")` & `r fmt_pct(aou_iet, "2→3", "pct_within_2yr")` & `r fmt_pct(aou_iet, "3→4", "pct_within_2yr")` & `r fmt_pct(aou_iet, "4→5", "pct_within_2yr")` \\
Within 5 yr   & `r fmt_pct(aou_iet, "1→2", "pct_within_5yr")` & `r fmt_pct(aou_iet, "2→3", "pct_within_5yr")` & `r fmt_pct(aou_iet, "3→4", "pct_within_5yr")` & `r fmt_pct(aou_iet, "4→5", "pct_within_5yr")` \\
\bottomrule
\end{tabular}
\end{table}

```{r supp-table-3b-classifier-perf, include=FALSE}
# Discriminatory performance of the binary "≥2 prior events (no EAU)"
# classifier for 5-year recurrence on the whole-dataset transitions sample.
# Values come from the per-cohort cluster-bootstrap output, which now
# includes a "≥2 prior events (no EAU)" row alongside the EAU-augmented
# classifiers in `recurrent_disease_whole_dataset_metrics*.csv`.
.load_two_plus <- function(path) {
  if (!file.exists(path)) return(NULL)
  d <- read.csv(path, check.names = FALSE, stringsAsFactors = FALSE)
  hit <- d[d$Comparison == "≥2 prior events (no EAU)", , drop = FALSE]
  if (nrow(hit) == 0) return(NULL)
  hit
}
ukb_2p <- .load_two_plus("UKB Recurrence paper results/recurrent_disease_whole_dataset_metrics.csv")
aou_2p <- .load_two_plus("AoU Recurrence paper results/recurrent_disease_whole_dataset_metrics_aou.csv")

# DerSimonian-Laird random-effects pool of each metric on the natural scale.
.re_pool_simple <- function(est, lo, hi) {
  se <- (hi - lo) / (2 * 1.96)
  ok <- is.finite(se) & se > 0 & is.finite(est)
  est <- est[ok]; vi <- se[ok]^2
  k <- length(est)
  if (k == 0) return(c(est = NA, lo = NA, hi = NA))
  if (k == 1) return(c(est = est, lo = est - 1.96*sqrt(vi), hi = est + 1.96*sqrt(vi)))
  w_fe <- 1 / vi
  fe   <- sum(w_fe * est) / sum(w_fe)
  Q    <- sum(w_fe * (est - fe)^2)
  C    <- sum(w_fe) - sum(w_fe^2)/sum(w_fe)
  tau2 <- max(0, (Q - (k - 1)) / C)
  w_re <- 1 / (vi + tau2)
  pe   <- sum(w_re * est) / sum(w_re)
  pse  <- sqrt(1 / sum(w_re))
  c(est = pe, lo = pe - 1.96*pse, hi = pe + 1.96*pse)
}

fmt_metric <- function(v) {
  if (length(v) == 0 || any(is.na(v))) return("--")
  sprintf("%.3f (%.3f--%.3f)", v["est"], v["lo"], v["hi"])
}

get_metric <- function(d, val, lo, hi) {
  if (is.null(d)) return(NULL)
  c(d[[val]], d[[lo]], d[[hi]])
}

# Build per-metric row for AUC / Sens / Spec / PPV / NPV
build_row <- function(val_col, lo_col, hi_col) {
  ukb_v <- if (is.null(ukb_2p)) NULL else c(est = ukb_2p[[val_col]], lo = ukb_2p[[lo_col]], hi = ukb_2p[[hi_col]])
  aou_v <- if (is.null(aou_2p)) NULL else c(est = aou_2p[[val_col]], lo = aou_2p[[lo_col]], hi = aou_2p[[hi_col]])
  meta_v <- if (!is.null(ukb_v) && !is.null(aou_v))
    .re_pool_simple(c(ukb_v["est"], aou_v["est"]),
                    c(ukb_v["lo"],  aou_v["lo"]),
                    c(ukb_v["hi"],  aou_v["hi"]))
    else NULL
  c(fmt_metric(ukb_v), fmt_metric(aou_v), fmt_metric(meta_v))
}

auc_row  <- build_row("AUC_val",         "AUC_lo",         "AUC_hi")
sens_row <- build_row("Sensitivity_val", "Sensitivity_lo", "Sensitivity_hi")
spec_row <- build_row("Specificity_val", "Specificity_lo", "Specificity_hi")
ppv_row  <- build_row("PPV_val",         "PPV_lo",         "PPV_hi")
npv_row  <- build_row("NPV_val",         "NPV_lo",         "NPV_hi")
```

\textbf{Discriminatory performance of "≥2 prior events" as a classifier for 5-year recurrence}

Same whole-dataset transitions sample as main-text Figure 2 and Sup Fig 17 (one row per participant per transition reached, with patient-level cluster bootstrap inference, B = 1000). The "Meta-analysis" column is the DerSimonian-Laird random-effects pool of UKB and AoU. Per-cohort 95% confidence intervals come from the cluster-bootstrap percentile distribution.

\begin{table}[H]
\centering
\small
\begin{tabular}{lccc}
\toprule
\textbf{Metric (95\% CI)} & \textbf{UK Biobank} & \textbf{All of Us} & \textbf{Meta-analysis} \\
\midrule
AUC          & `r auc_row[1]`  & `r auc_row[2]`  & `r auc_row[3]`  \\
Sensitivity  & `r sens_row[1]` & `r sens_row[2]` & `r sens_row[3]` \\
Specificity  & `r spec_row[1]` & `r spec_row[2]` & `r spec_row[3]` \\
PPV          & `r ppv_row[1]`  & `r ppv_row[2]`  & `r ppv_row[3]`  \\
NPV          & `r npv_row[1]`  & `r npv_row[2]`  & `r npv_row[3]`  \\
\bottomrule
\end{tabular}
\end{table}

\newpage

## Supplementary Table 4. Pairwise classifier comparisons (whole-dataset analysis, Figure 2)

Pairwise tests were computed within each cohort on the entire transitions-long sample using a non-parametric cluster bootstrap that resamples PARTICIPANTS (not transitions) — addressing the within-patient correlation introduced when one participant contributes multiple transition-rows. Cluster-bootstrap two-sided p-values are then combined across cohorts via Fisher's method. Pooled AUCs use DerSimonian-Laird random-effects meta-analysis (UKB + AoU); between-cohort heterogeneity for each classifier (Cochran's $Q$, $I^2$, $\tau^2$, $p_Q$) is reported separately in **Supplementary Table 5**. The six comparison families correspond to the analysis in main-text Figure 2.

```{r supp-table-4-pairwise-comparisons, results='asis'}
# --- Load pooled meta-AUC table (used for Figure 2) and pairwise DeLong tables ---
load_or_empty_pair <- function(path) {
  if (file.exists(path)) {
    read.csv(path, check.names = FALSE, stringsAsFactors = FALSE)
  } else {
    message("Note: ", path, " not found — Sup Table 4 will report 'NA'.")
    data.frame(classifier_a = character(0), classifier_b = character(0),
               delong_p = numeric(0))
  }
}
ukb_pair <- load_or_empty_pair("UKB Recurrence paper results/recurrent_disease_whole_dataset_pairwise_delong.csv")
aou_pair <- load_or_empty_pair("AoU Recurrence paper results/recurrent_disease_whole_dataset_pairwise_delong_aou.csv")

# Per-cohort AUCs (already loaded by Figure 2 chunk; reload defensively here
# so this chunk works even if knitted in isolation)
load_or_empty_metrics <- function(path) {
  if (file.exists(path)) {
    read.csv(path, check.names = FALSE, stringsAsFactors = FALSE)
  } else {
    message("Note: ", path, " not found.")
    data.frame(Comparison = character(0), AUC_val = numeric(0),
               AUC_lo = numeric(0), AUC_hi = numeric(0))
  }
}
ukb_m <- load_or_empty_metrics("UKB Recurrence paper results/recurrent_disease_whole_dataset_metrics.csv")
aou_m <- load_or_empty_metrics("AoU Recurrence paper results/recurrent_disease_whole_dataset_metrics_aou.csv")

# DerSimonian-Laird random-effects meta-analysis of AUC for a given classifier,
# with between-cohort heterogeneity statistics (Cochran's Q, I², τ², df, p_Q).
# Cohort-specific AUCs come from the cluster-bootstrap CIs in the per-cohort
# whole-dataset metrics CSVs.
ivm_auc <- function(label) {
  rows <- rbind(
    ukb_m[ukb_m$Comparison == label, c("AUC_val","AUC_lo","AUC_hi"), drop = FALSE],
    aou_m[aou_m$Comparison == label, c("AUC_val","AUC_lo","AUC_hi"), drop = FALSE]
  )
  na_out <- c(est = NA_real_, lo = NA_real_, hi = NA_real_,
              Q = NA_real_, df = NA_real_, I2 = NA_real_, tau2 = NA_real_,
              p_Q = NA_real_, k = NA_real_)
  if (nrow(rows) == 0) return(na_out)
  se <- (rows$AUC_hi - rows$AUC_lo) / (2 * 1.96)
  ok <- is.finite(se) & se > 0 & is.finite(rows$AUC_val)
  est <- rows$AUC_val[ok]; se <- se[ok]; vi <- se^2
  k <- length(est)
  if (k == 0) return(na_out)
  if (k == 1) return(c(est = est, lo = est - 1.96*se, hi = est + 1.96*se,
                       Q = NA_real_, df = NA_real_, I2 = NA_real_,
                       tau2 = NA_real_, p_Q = NA_real_, k = 1))
  w_fe  <- 1 / vi
  fe_pe <- sum(w_fe * est) / sum(w_fe)
  Q     <- sum(w_fe * (est - fe_pe)^2)
  df_Q  <- k - 1
  C     <- sum(w_fe) - sum(w_fe^2) / sum(w_fe)
  tau2  <- max(0, (Q - df_Q) / C)
  I2    <- max(0, (Q - df_Q) / Q) * 100   # Higgins & Thompson (2002)
  p_Q   <- 1 - pchisq(Q, df = df_Q)
  w_re <- 1 / (vi + tau2)
  pe   <- sum(w_re * est) / sum(w_re)
  pse  <- sqrt(1 / sum(w_re))
  c(est = pe, lo = pe - 1.96 * pse, hi = pe + 1.96 * pse,
    Q = Q, df = df_Q, I2 = I2, tau2 = tau2, p_Q = p_Q, k = k)
}

# Look up the DeLong p in a pairwise table (handles either order of a/b)
lookup_p <- function(tbl, a, b) {
  hit <- tbl[(tbl$classifier_a == a & tbl$classifier_b == b) |
             (tbl$classifier_a == b & tbl$classifier_b == a), "delong_p"]
  if (length(hit) == 0) NA_real_ else hit[1]
}

fisher_combine <- function(ps) {
  ps <- ps[is.finite(ps) & ps > 0 & ps <= 1]
  if (length(ps) < 1) return(NA_real_)
  if (length(ps) == 1) return(ps)
  X <- -2 * sum(log(ps))
  1 - pchisq(X, df = 2 * length(ps))
}

fmt_auc_ci <- function(v) {
  # Only check the three fields we actually use; ivm_auc() now also returns
  # heterogeneity statistics (Q, df, I², τ², p_Q, k) which can legitimately
  # be NA for single-cohort cases without invalidating the est/lo/hi triple.
  if (any(is.na(c(v["est"], v["lo"], v["hi"])))) return("--")
  sprintf("%.3f (%.3f--%.3f)", v["est"], v["lo"], v["hi"])
}
fmt_p_combined <- function(p) {
  if (is.na(p)) return("--")
  if (p < 0.001) return("<0.001")
  sprintf("%.3f", p)
}

# --- Define the 5 comparison families ---
all_classifiers <- c(
  "EAU only",
  "EAU + Short Time ≤6mo", "EAU + Short Time ≤24mo",
  "EAU + ≥2 events", "EAU + ≥3 events", "EAU + ≥4 events",
  "EAU + ≥2 events + Short Time ≤6mo",
  "EAU + ≥2 events + Short Time ≤24mo",
  "EAU + ≥3 events + Short Time ≤6mo",
  "EAU + ≥3 events + Short Time ≤24mo",
  "EAU + ≥4 events + Short Time ≤6mo",
  "EAU + ≥4 events + Short Time ≤24mo"
)
ST    <- c("EAU + Short Time ≤6mo", "EAU + Short Time ≤24mo")
RD    <- c("EAU + ≥2 events", "EAU + ≥3 events", "EAU + ≥4 events")
RDST  <- setdiff(all_classifiers, c("EAU only", ST, RD))

family_specs <- list(
  list(name = "1. EAU only vs EAU + Short Time (no recurrent disease)",
       a = rep("EAU only", length(ST)), b = ST),
  list(name = "2. EAU only vs EAU + Recurrent Disease (no short time)",
       a = rep("EAU only", length(RD)), b = RD),
  list(name = "3. EAU only vs EAU + Recurrent Disease + Short Time",
       a = rep("EAU only", length(RDST)), b = RDST),
  list(name = "4. EAU + Short Time vs EAU + Recurrent Disease (no short time)",
       a = rep(ST, each = length(RD)), b = rep(RD, length(ST))),
  list(name = "5. EAU + Short Time vs EAU + Recurrent Disease + Short Time",
       a = rep(ST, each = length(RDST)), b = rep(RDST, length(ST))),
  list(name = "6. EAU + Recurrent Disease (no short time) vs EAU + Recurrent Disease + Short Time",
       a = rep(RD, each = length(RDST)), b = rep(RDST, length(RD)))
)

rows_list <- lapply(family_specs, function(fs) {
  do.call(rbind, lapply(seq_along(fs$a), function(i) {
    a <- fs$a[i]; b <- fs$b[i]
    p_ukb <- lookup_p(ukb_pair, a, b)
    p_aou <- lookup_p(aou_pair, a, b)
    p_pool <- fisher_combine(c(p_ukb, p_aou))
    auc_a <- ivm_auc(a); auc_b <- ivm_auc(b)
    data.frame(
      Family = fs$name,
      A = a, B = b,
      `AUC A pooled (95% CI)` = fmt_auc_ci(auc_a),
      `AUC B pooled (95% CI)` = fmt_auc_ci(auc_b),
      `UKB cluster-boot p` = fmt_p_combined(p_ukb),
      `AoU cluster-boot p` = fmt_p_combined(p_aou),
      `Fisher combined p` = fmt_p_combined(p_pool),
      check.names = FALSE,
      stringsAsFactors = FALSE
    )
  }))
})
all_rows <- do.call(rbind, rows_list)

# --- Render via kableExtra with family group headers ---
suppressMessages({ library(kableExtra) })
display <- all_rows %>% dplyr::select(-Family)
group_index <- table(factor(all_rows$Family, levels = sapply(family_specs, `[[`, "name")))

kbl(display, format = "latex", booktabs = TRUE, escape = FALSE,
    longtable = TRUE,
    col.names = c("High Risk Definition A", "High Risk Definition B",
                  "AUC A (95\\% CI)", "AUC B (95\\% CI)",
                  "UKB cluster-boot $p$",
                  "AoU cluster-boot $p$",
                  "Fisher combined $p$")) %>%
  kable_styling(latex_options = c("repeat_header", "hold_position"),
                font_size = 7) %>%
  pack_rows(index = group_index) %>%
  # Constrain all column widths so the 7-col longtable fits inside the
  # 16.5-cm text width without truncating the right-most (Fisher combined)
  # column.
  column_spec(1, width = "3.5cm") %>%
  column_spec(2, width = "3.5cm") %>%
  column_spec(3, width = "2.0cm") %>%
  column_spec(4, width = "2.0cm") %>%
  column_spec(5, width = "1.5cm") %>%
  column_spec(6, width = "1.5cm") %>%
  column_spec(7, width = "1.5cm") %>%
  # Vertically merge consecutive duplicate values in column 1 (High Risk
  # Definition A) and column 3 (AUC A). pack_rows boundaries naturally
  # break the merge, so collapsing happens within each family block only.
  collapse_rows(columns = c(1, 3), valign = "middle", latex_hline = "none")
```

\newpage

## Supplementary Table 5. Between-cohort heterogeneity for the whole-dataset pooled AUCs

Heterogeneity statistics to accompany Figure 2.

\begin{landscape}

```{r supp-table-5-heterogeneity, results='asis'}
# Reuses ukb_m, aou_m, ivm_auc(), all_classifiers from the Sup Table 4 chunk.
# ivm_auc() now returns Q, df, I2, tau2, p_Q in addition to est/lo/hi.
fmt_p_q <- function(p) {
  if (is.na(p)) return("--")
  if (p < 0.001) return("<0.001")
  sprintf("%.3f", p)
}
fmt_q   <- function(q)  if (is.na(q))  "--" else sprintf("%.2f", q)
fmt_i2  <- function(i)  if (is.na(i))  "--" else sprintf("%.1f\\%%", i)
fmt_t2  <- function(t)  if (is.na(t))  "--" else sprintf("%.2e", t)
fmt_per_cohort <- function(metrics_df, label) {
  r <- metrics_df[metrics_df$Comparison == label, , drop = FALSE]
  if (nrow(r) == 0) return("--")
  sprintf("%.3f (%.3f--%.3f)",
          as.numeric(r$AUC_val[1]),
          as.numeric(r$AUC_lo[1]),
          as.numeric(r$AUC_hi[1]))
}

het_rows <- do.call(rbind, lapply(all_classifiers, function(lbl) {
  v <- ivm_auc(lbl)
  data.frame(
    Classifier      = lbl,
    `UKB AUC (95% CI)`    = fmt_per_cohort(ukb_m, lbl),
    `AoU AUC (95% CI)`    = fmt_per_cohort(aou_m, lbl),
    `Pooled AUC (95% CI)` = fmt_auc_ci(v),
    Q       = fmt_q(unname(v["Q"])),
    df      = if (is.na(v["df"])) "--" else as.character(as.integer(v["df"])),
    `I^2`   = fmt_i2(unname(v["I2"])),
    `tau^2` = fmt_t2(unname(v["tau2"])),
    `p_Q`   = fmt_p_q(unname(v["p_Q"])),
    check.names = FALSE,
    stringsAsFactors = FALSE
  )
}))

kbl(het_rows, format = "latex", booktabs = TRUE, escape = FALSE,
    longtable = FALSE,                       # landscape page → single table OK
    align = c("l", rep("c", 8)),
    col.names = c("Classifier",
                  "UKB AUC (95\\% CI)", "AoU AUC (95\\% CI)",
                  "Pooled AUC (95\\% CI)",
                  "$Q$", "df", "$I^2$", "$\\tau^2$", "$p_Q$")) %>%
  kable_styling(latex_options = c("hold_position"),
                font_size = 8,
                position = "center") %>%
  column_spec(1, width = "5.0cm") %>%
  column_spec(2, width = "2.6cm") %>%
  column_spec(3, width = "2.6cm") %>%
  column_spec(4, width = "2.6cm") %>%
  column_spec(5, width = "1.2cm") %>%
  column_spec(6, width = "0.7cm") %>%
  column_spec(7, width = "1.2cm") %>%
  column_spec(8, width = "1.5cm") %>%
  column_spec(9, width = "1.2cm")
```

\end{landscape}

\newpage

## Supplementary Table 6. Discrimination of EAU stratification alone vs EAU combined with a recurrent-disease (2/more events) threshold

Per-cohort cluster-bootstrap estimates (B = 1000 iterations resampling participants) and DerSimonian–Laird random-effects pooled estimates for two classifiers of high-risk status applied to the entire transitions sample:

* **EAU only** — flags participants as high-risk on EAU criteria alone.
* **EAU + ≥2 events** — flags participants as high-risk if they are EAU high-risk OR have reached ≥2 stone events at the index transition.

AUC is pooled on the AUC scale (linear DL); sensitivity and specificity are pooled on the logit scale and back-transformed.

```{r supp-table-6-eau-only-sens-spec, results='asis'}
suppressMessages({ library(kableExtra) })

ukb_m_t6 <- read.csv("UKB Recurrence paper results/recurrent_disease_whole_dataset_metrics.csv",
                     check.names = FALSE, stringsAsFactors = FALSE)
aou_m_t6 <- read.csv("AoU Recurrence paper results/recurrent_disease_whole_dataset_metrics_aou.csv",
                     check.names = FALSE, stringsAsFactors = FALSE)

# DL random-effects pool on logit scale (proportions: Sens, Spec).
re_meta_proportion <- function(p_vec, lo_vec, hi_vec) {
  ok <- is.finite(p_vec) & is.finite(lo_vec) & is.finite(hi_vec) &
        p_vec > 0 & p_vec < 1 & lo_vec > 0 & hi_vec < 1
  p_vec <- p_vec[ok]; lo_vec <- lo_vec[ok]; hi_vec <- hi_vec[ok]
  k <- length(p_vec)
  if (k == 0) return(c(est = NA_real_, lo = NA_real_, hi = NA_real_, tau2 = NA_real_))
  theta <- log(p_vec / (1 - p_vec))
  theta_lo <- log(lo_vec / (1 - lo_vec))
  theta_hi <- log(hi_vec / (1 - hi_vec))
  se   <- (theta_hi - theta_lo) / (2 * 1.96)
  vi   <- se^2
  if (k == 1) return(c(est = p_vec, lo = lo_vec, hi = hi_vec, tau2 = 0))
  w_fe  <- 1 / vi
  fe_pe <- sum(w_fe * theta) / sum(w_fe)
  Q     <- sum(w_fe * (theta - fe_pe)^2)
  C     <- sum(w_fe) - sum(w_fe^2) / sum(w_fe)
  tau2  <- max(0, (Q - (k - 1)) / C)
  w_re  <- 1 / (vi + tau2)
  pe    <- sum(w_re * theta) / sum(w_re)
  pse   <- sqrt(1 / sum(w_re))
  c(est  = 1 / (1 + exp(-pe)),
    lo   = 1 / (1 + exp(-(pe - 1.96 * pse))),
    hi   = 1 / (1 + exp(-(pe + 1.96 * pse))),
    tau2 = tau2)
}

# DL random-effects pool on the linear (AUC) scale.
re_meta_auc <- function(est, lo, hi) {
  se <- (hi - lo) / (2 * 1.96)
  ok <- is.finite(se) & se > 0 & is.finite(est)
  est <- est[ok]; se <- se[ok]; vi <- se^2
  k <- length(est)
  if (k == 0) return(c(est = NA_real_, lo = NA_real_, hi = NA_real_, tau2 = NA_real_))
  if (k == 1) return(c(est = est, lo = est - 1.96 * se, hi = est + 1.96 * se, tau2 = 0))
  w_fe <- 1 / vi
  fe_pe <- sum(w_fe * est) / sum(w_fe)
  Q  <- sum(w_fe * (est - fe_pe)^2)
  C  <- sum(w_fe) - sum(w_fe^2) / sum(w_fe)
  tau2 <- max(0, (Q - (k - 1)) / C)
  w_re <- 1 / (vi + tau2)
  pe   <- sum(w_re * est) / sum(w_re)
  pse  <- sqrt(1 / sum(w_re))
  c(est = pe, lo = pe - 1.96 * pse, hi = pe + 1.96 * pse, tau2 = tau2)
}

fmt_pct_ci <- function(est, lo, hi) {
  if (any(is.na(c(est, lo, hi)))) return("--")
  sprintf("%.1f\\%% (%.1f--%.1f\\%%)", est * 100, lo * 100, hi * 100)
}
fmt_auc_ci <- function(est, lo, hi) {
  if (any(is.na(c(est, lo, hi)))) return("--")
  sprintf("%.3f (%.3f--%.3f)", est, lo, hi)
}

# Helper: produce the three formatted strings (AUC, Sens, Spec) for one classifier
# across UKB / AoU / Pooled rows.
build_metric_column <- function(comparison_label) {
  ukb_row <- ukb_m_t6[ukb_m_t6$Comparison == comparison_label, , drop = FALSE]
  aou_row <- aou_m_t6[aou_m_t6$Comparison == comparison_label, , drop = FALSE]

  auc_pool  <- re_meta_auc(
    c(ukb_row$AUC_val, aou_row$AUC_val),
    c(ukb_row$AUC_lo,  aou_row$AUC_lo),
    c(ukb_row$AUC_hi,  aou_row$AUC_hi)
  )
  sens_pool <- re_meta_proportion(
    c(ukb_row$Sensitivity_val, aou_row$Sensitivity_val),
    c(ukb_row$Sensitivity_lo,  aou_row$Sensitivity_lo),
    c(ukb_row$Sensitivity_hi,  aou_row$Sensitivity_hi)
  )
  spec_pool <- re_meta_proportion(
    c(ukb_row$Specificity_val, aou_row$Specificity_val),
    c(ukb_row$Specificity_lo,  aou_row$Specificity_lo),
    c(ukb_row$Specificity_hi,  aou_row$Specificity_hi)
  )

  list(
    cells = c(
      # AUC: UKB, AoU, Pooled
      fmt_auc_ci(ukb_row$AUC_val, ukb_row$AUC_lo, ukb_row$AUC_hi),
      fmt_auc_ci(aou_row$AUC_val, aou_row$AUC_lo, aou_row$AUC_hi),
      fmt_auc_ci(auc_pool["est"], auc_pool["lo"], auc_pool["hi"]),
      # Sens
      fmt_pct_ci(ukb_row$Sensitivity_val, ukb_row$Sensitivity_lo, ukb_row$Sensitivity_hi),
      fmt_pct_ci(aou_row$Sensitivity_val, aou_row$Sensitivity_lo, aou_row$Sensitivity_hi),
      fmt_pct_ci(sens_pool["est"], sens_pool["lo"], sens_pool["hi"]),
      # Spec
      fmt_pct_ci(ukb_row$Specificity_val, ukb_row$Specificity_lo, ukb_row$Specificity_hi),
      fmt_pct_ci(aou_row$Specificity_val, aou_row$Specificity_lo, aou_row$Specificity_hi),
      fmt_pct_ci(spec_pool["est"], spec_pool["lo"], spec_pool["hi"])
    ),
    tau2 = c(AUC = auc_pool["tau2"],
             Sensitivity = sens_pool["tau2"],
             Specificity = spec_pool["tau2"])
  )
}

col_eau   <- build_metric_column("EAU only")
col_2plus <- build_metric_column("EAU + ≥2 events")

t6 <- tibble::tibble(
  Metric    = c("AUC", "", "",
                "Sensitivity", "", "",
                "Specificity", "", ""),
  Cohort    = rep(c("UK Biobank", "All of Us", "Pooled (DL random-effects)"), 3),
  `EAU only`         = col_eau$cells,
  `EAU + ≥2 events`  = col_2plus$cells
)

t6_footnote <- sprintf(
  paste("DerSimonian-Laird $\\tau^2$ --- ",
        "EAU only: AUC $= %.4f$ (linear), sensitivity $= %.4f$, specificity $= %.4f$ (logit); ",
        "EAU + ≥2 events: AUC $= %.4f$ (linear), sensitivity $= %.4f$, specificity $= %.4f$ (logit). ",
        sep = ""),
  col_eau$tau2["AUC"],   col_eau$tau2["Sensitivity"],   col_eau$tau2["Specificity"],
  col_2plus$tau2["AUC"], col_2plus$tau2["Sensitivity"], col_2plus$tau2["Specificity"]
)

kbl(t6, format = "latex", booktabs = TRUE, escape = FALSE,
    align = c("l", "l", "c", "c"),
    col.names = c("Metric", "Cohort",
                  "EAU only (95\\% CI)",
                  "EAU + recurrent disease = ≥2 events (95\\% CI)")) %>%
  kable_styling(latex_options = c("hold_position"),
                font_size = 9, position = "center") %>%
  column_spec(1, width = "2.6cm") %>%
  column_spec(2, width = "3.6cm") %>%
  column_spec(3, width = "4.2cm") %>%
  column_spec(4, width = "4.4cm") %>%
  row_spec(3, hline_after = TRUE) %>%
  row_spec(6, hline_after = TRUE)
```

`r t6_footnote` Per-cohort 95% CIs are from the cluster-bootstrap (B = 1000 iterations resampling participants). The pooled estimate weights each cohort by $1/(v_i + \tau^2)$ --- on the AUC scale for AUC, and on the logit scale (back-transformed for display) for sensitivity and specificity. The "EAU only" classifier flags participants as high-risk solely on EAU criteria; the "EAU + ≥2 events" classifier additionally flags any participant who has reached ≥2 stone events at the index transition, regardless of EAU status.

\newpage

# Figures

## Figure 1
```{r fig1-forest-plot-data, fig.width=10, fig.height=14, out.width="100%"}
# --- Load data ---
ukb <- read.csv("UKB Recurrence paper results/prognostic_accuracy_grid_search_results.csv")
aou <- read.csv("AoU Recurrence paper results/prognostic_accuracy_grid_search_results_aou.csv")

# Remove duplicate rows in AoU
aou <- aou[!duplicated(aou[, c("Starting_Point", "Time_Cutoff_Months", "Recurrence_Definition")]), ]

# --- Build labels ---
event_map <- c("Index Date"   = "First",
               "Second Event" = "Second",
               "Third Event"  = "Third",
               "Fourth Event" = "Fourth")

make_label <- function(starting_point, cutoff) {
  event <- event_map[starting_point]
  if (is.na(cutoff) | cutoff == "NA") {
    event
  } else {
    paste0(event, " (", cutoff, "mo)")
  }
}

# --- Prepare UKB ---
ukb$Biobank <- "UK Biobank"
ukb$label <- mapply(make_label, ukb$Starting_Point,
                    as.character(ukb$Time_Cutoff_Months))

# --- Prepare AoU ---
aou$Biobank <- "All of Us"
aou$label <- mapply(make_label, aou$Starting_Point,
                    as.character(aou$Time_Cutoff_Months))

# --- Combine ---
cols <- c("label", "Starting_Point", "Time_Cutoff_Months", "Recurrence_Definition",
          "AUC_val", "AUC_lo", "AUC_hi", "Biobank")
df <- rbind(ukb[, cols], aou[, cols])

# Ensure numeric
df$AUC_val <- as.numeric(df$AUC_val)
df$AUC_lo <- as.numeric(df$AUC_lo)
df$AUC_hi <- as.numeric(df$AUC_hi)

# --- DerSimonian-Laird random-effects meta-analysis on AUC ---
# SE derived from 95% CI bounds (normal approximation). With only 2 cohorts
# the between-study variance estimate (tau^2) is unstable, but RE pooling
# is the methodologically appropriate choice when between-cohort
# heterogeneity is plausible. tau^2 = 0 collapses to fixed-effect IVM.
re_meta_auc <- function(est, lo, hi) {
  se <- (hi - lo) / (2 * 1.96)
  ok <- is.finite(se) & se > 0 & is.finite(est)
  est <- est[ok]; se <- se[ok]; vi <- se^2
  k <- length(est)
  if (k < 1) return(c(est = NA_real_, lo = NA_real_, hi = NA_real_))
  if (k == 1) return(c(est = est, lo = est - 1.96*se, hi = est + 1.96*se))
  w_fe <- 1 / vi
  fe_pe <- sum(w_fe * est) / sum(w_fe)
  Q  <- sum(w_fe * (est - fe_pe)^2)
  C  <- sum(w_fe) - sum(w_fe^2) / sum(w_fe)
  tau2 <- max(0, (Q - (k - 1)) / C)
  w_re <- 1 / (vi + tau2)
  pe   <- sum(w_re * est) / sum(w_re)
  pse  <- sqrt(1 / sum(w_re))
  c(est = pe, lo = pe - 1.96 * pse, hi = pe + 1.96 * pse)
}

meta_auc <- df %>%
  mutate(SE = (AUC_hi - AUC_lo) / (2 * 1.96)) %>%
  filter(is.finite(SE) & SE > 0) %>%
  group_by(label, Starting_Point, Time_Cutoff_Months, Recurrence_Definition) %>%
  summarise(
    pe = list(re_meta_auc(AUC_val, AUC_lo, AUC_hi)),
    .groups  = "drop"
  ) %>%
  mutate(
    AUC_val = sapply(pe, `[`, "est"),
    AUC_lo  = sapply(pe, `[`, "lo"),
    AUC_hi  = sapply(pe, `[`, "hi"),
    Biobank = "Meta-analysis"
  ) %>%
  dplyr::select(all_of(cols))

df <- rbind(df, meta_auc)

# --- Order labels by event then cutoff ---
event_order <- c("First", "Second", "Third", "Fourth")
df$event_label <- event_map[df$Starting_Point]
df$event_order <- match(df$event_label, event_order)
df$cutoff_num <- ifelse(is.na(df$Time_Cutoff_Months), 0,
                        as.numeric(df$Time_Cutoff_Months))

df <- df[order(df$event_order, df$cutoff_num), ]

# --- Y-axis: cutoff-only labels (event is in the row facet strip) ---
# For Index Date and the no-cutoff variant of 2nd/3rd/4th events we use a
# single shared label "Baseline" — there is no short-time modifier in
# either case (Index Date has no prior gap; the no-cutoff non-Index variant
# explicitly omits the short-time rule). The 6- and 24-month short-time rows
# sit below it in each non-Index facet.
df$cutoff_label <- dplyr::case_when(
  df$Starting_Point == "Index Date"                                ~ "Baseline",
  is.na(df$Time_Cutoff_Months) | df$Time_Cutoff_Months == "NA"     ~ "Baseline",
  TRUE                                                             ~ paste0("+ ≤", df$Time_Cutoff_Months, "mo")
)
# ---  Order cutoff labels (top→bottom: Baseline, + ≤6mo, + ≤24mo) ---
# In ggplot, factor level 1 is at the bottom. To put "Baseline"
# on top we place it last in the factor levels.
cutoff_levels <- c("+ ≤24mo", "+ ≤6mo", "Baseline")
df$cutoff_label <- factor(df$cutoff_label, levels = cutoff_levels)

# ---  Condense information ---
df <- df %>%
  filter(Recurrence_Definition == "≥1 subsequent stone events") %>%
  filter(
    Starting_Point == "Index Date" |
    (Starting_Point != "Index Date" &
       (is.na(Time_Cutoff_Months) | Time_Cutoff_Months %in% c(6, 24)))
  )

# --- Cohort factor order: UKB, AoU, Meta-analysis ---
df$Biobank <- factor(df$Biobank,
                     levels = c("UK Biobank", "All of Us", "Meta-analysis"))

# --- Row facet: event group ---
df$event_label <- factor(df$event_label, levels = event_order)

# --- Column facet: recurrence definition ---
rec_labels <- c("\u22651 subsequent stone events" = "\u2265 1 Subsequent Stone Events")
df$rec_facet <- rec_labels[df$Recurrence_Definition]
df$rec_facet <- factor(df$rec_facet, levels = rec_labels)

# --- Manual dodge offset (so 3 groups stay aligned regardless of layer) ---
dodge_w <- 0.7
df$y_offset <- dplyr::case_when(
  df$Biobank == "UK Biobank"    ~ +dodge_w / 3,
  df$Biobank == "All of Us"     ~  0,
  df$Biobank == "Meta-analysis" ~ -dodge_w / 3
)
df$y_num <- as.numeric(df$cutoff_label) + df$y_offset

# --- Ensure ONLY desired cutoff levels exist ---
df <- df %>% dplyr::filter(cutoff_num %in% c(0, 6, 24))
df$cutoff_label <- factor(df$cutoff_label, levels = cutoff_levels)

# --- Studies + meta-analysis split ---
df_studies <- df %>% dplyr::filter(Biobank != "Meta-analysis")
df_meta    <- df %>% dplyr::filter(Biobank == "Meta-analysis")

# --- Pairwise Wald-test p-values on pooled meta-analytic AUCs ---
# For each non-Index event (Second/Third/Fourth) we compute three comparisons:
#   (i)   Baseline  vs ≤6mo
#   (ii)  Baseline  vs ≤24mo
#   (iii) ≤6mo      vs ≤24mo
# Each p uses z = (AUC_a - AUC_b) / sqrt(SE_a^2 + SE_b^2), where SE comes
# from the pooled meta-analytic CI: SE = (AUC_hi - AUC_lo) / (2 * 1.96).
# Treats the pooled estimates as independent (conservative — paired
# discrimination tests on the same subjects have negative covariance that
# would shrink the SE of the difference).
fmt_pp <- function(p) {
  if (is.na(p)) return("NA")
  if (p < 0.001) return("<0.001")
  formatC(p, digits = 3, format = "f")
}
wald_p <- function(a, b) {
  if (nrow(a) == 0 || nrow(b) == 0) return(NA_real_)
  se_a <- (a$AUC_hi - a$AUC_lo) / (2 * 1.96)
  se_b <- (b$AUC_hi - b$AUC_lo) / (2 * 1.96)
  z    <- (a$AUC_val - b$AUC_val) / sqrt(se_a^2 + se_b^2)
  2 * pnorm(-abs(z))
}

pair_events <- df_meta %>%
  dplyr::filter(Starting_Point != "Index Date") %>%
  dplyr::distinct(event_label) %>%
  dplyr::pull(event_label)

pval_df <- do.call(rbind, lapply(pair_events, function(ev) {
  rows  <- df_meta %>% dplyr::filter(event_label == ev)
  nst   <- rows %>% dplyr::filter(cutoff_label == "Baseline")
  six   <- rows %>% dplyr::filter(cutoff_label == "+ ≤6mo")
  twf   <- rows %>% dplyr::filter(cutoff_label == "+ ≤24mo")
  if (nrow(nst) == 0 && nrow(six) == 0 && nrow(twf) == 0) return(NULL)

  p1 <- wald_p(nst, six)   # Baseline vs ≤6mo
  p2 <- wald_p(nst, twf)   # Baseline vs ≤24mo
  p3 <- wald_p(six, twf)   # ≤6mo vs ≤24mo

  # Inset-table label content: header, separator and three pairwise rows,
  # rendered in a monospaced font so the columns align inside the box.
  col1 <- 23  # width of the "Comparison" column (chars)
  col2 <- 7   # width of the "p" column (chars)
  table_text <- paste(
    sprintf(paste0("%-", col1, "s  %-", col2, "s"), "Comparison",        "p-value"),
    sprintf(paste0("%-", col1, "s  %-", col2, "s"),
            strrep("-", col1), strrep("-", col2)),
    sprintf(paste0("%-", col1, "s  %-", col2, "s"), "Baseline vs <=6mo",     fmt_pp(p1)),
    sprintf(paste0("%-", col1, "s  %-", col2, "s"), "Baseline vs <=24mo",    fmt_pp(p2)),
    sprintf(paste0("%-", col1, "s  %-", col2, "s"), "<=6mo vs <=24mo",       fmt_pp(p3)),
    sep = "\n"
  )

  # Place block centred on the middle row ("Short Time ≤6mo") of this event,
  # just to the right of the diamond region.
  # Anchor the p-value box on the middle row of each event facet (the "+ ≤6mo"
  # row). Must reference the current cutoff_levels label exactly — if the
  # label is renamed, this lookup returns NA and the boxes silently vanish.
  y_anchor <- as.numeric(factor("+ ≤6mo", levels = cutoff_levels)) -
                (dodge_w / 3)

  data.frame(event_label = as.character(ev),
             rec_facet   = unique(rows$rec_facet),
             x_text      = 0.71,
             y_num       = y_anchor,
             p_label     = table_text,
             stringsAsFactors = FALSE)
}))

if (is.null(pval_df) || nrow(pval_df) == 0) {
  pval_df <- data.frame(event_label = factor(character(0), levels = event_order),
                        rec_facet   = factor(character(0), levels = rec_labels),
                        x_text = numeric(0), y_num = numeric(0),
                        p_label = character(0))
} else {
  pval_df$event_label <- factor(pval_df$event_label, levels = event_order)
}

# --- Manual dodge offsets ---
dodge_w <- 0.7
df_studies$y_num <- as.numeric(df_studies$cutoff_label) +
  dplyr::case_when(
    df_studies$Biobank == "UK Biobank" ~ +dodge_w / 3,
    df_studies$Biobank == "All of Us"  ~  0
  )
df_meta$y_num <- as.numeric(df_meta$cutoff_label) - (dodge_w / 3)

# --- Diamond polygon vertices ---
diamond_h <- 0.13
diamond_df <- df_meta %>%
  dplyr::rowwise() %>%
  dplyr::do(data.frame(
    label       = .$label,
    event_label = .$event_label,
    rec_facet   = .$rec_facet,
    Biobank     = "Meta-analysis",
    x = c(.$AUC_lo, .$AUC_val, .$AUC_hi, .$AUC_val),
    y = .$y_num + c(0, diamond_h, 0, -diamond_h)
  )) %>%
  dplyr::ungroup()

# --- Axis breaks ---
y_breaks <- seq_along(levels(df$cutoff_label))
y_labels <- levels(df$cutoff_label)

# --- Plot ---
p_fig1 <- ggplot() +

  annotate("rect", xmin = -Inf, xmax = 0.5, ymin = -Inf, ymax = Inf,
           fill = "#F4A3A3", alpha = 0.2) +
  annotate("rect", xmin = 0.5, xmax = 0.7, ymin = -Inf, ymax = Inf,
           fill = "#F6D186", alpha = 0.2) +
  annotate("rect", xmin = 0.7, xmax = Inf, ymin = -Inf, ymax = Inf,
           fill = "#A6D96A", alpha = 0.2) +

  geom_vline(xintercept = 0.5, linetype = "dashed", colour = "grey40", linewidth = 0.7) +
  geom_vline(xintercept = 0.7, linetype = "dotdash", colour = "darkgreen", linewidth = 0.7) +

  geom_errorbarh(data = df_studies,
                 aes(xmin = AUC_lo, xmax = AUC_hi, y = y_num, colour = Biobank),
                 height = 0.18, linewidth = 0.9) +

  geom_point(data = df_studies,
             aes(x = AUC_val, y = y_num, colour = Biobank, shape = Biobank),
             size = 3.5, stroke = 0.6) +

  # NOTE: map colour = Biobank (not a fixed "black") so the "Meta-analysis"
  # level actually enters the colour aesthetic's data. Otherwise the colour
  # legend key for "Meta-analysis" has no underlying data row, and the
  # override.aes diamond glyph is silently dropped (only the label is shown).
  # `key_glyph = draw_key_point` overrides the default polygon-key (which is
  # a filled square and ignores `shape`) so override.aes(shape = 23) is
  # honoured for the meta-analysis key, rendering a filled diamond.
  geom_polygon(data = diamond_df,
               aes(x = x, y = y, group = label,
                   colour = Biobank, fill = Biobank),
               linewidth = 0.3,
               key_glyph = draw_key_point) +

  geom_label(data = pval_df,
             aes(x = x_text, y = y_num, label = p_label),
             hjust = 0, vjust = 0.5,
             size = 4.2, lineheight = 1.05,
             family = "mono", colour = "black",
             fill = "white",
             label.size = 0.5,
             label.padding = unit(7, "pt"),
             label.r = unit(2, "pt")) +

  facet_grid(event_label ~ rec_facet,
             scales = "free_y", space = "free_y", switch = "y") +

  scale_y_continuous(breaks = y_breaks,
                     labels = y_labels,
                     expand = expansion(add = 0.6)) +

  # Unified single legend: UK Biobank → All of Us → Meta-analysis, with the
  # meta-analysis key shown as a filled diamond to match its geom_polygon.
  scale_colour_manual(
    name   = NULL,
    values = c("UK Biobank"    = "#1b9e77",
               "All of Us"     = "#d95f02",
               "Meta-analysis" = "#7570b3"),
    breaks = c("UK Biobank", "All of Us", "Meta-analysis"),
    drop   = FALSE
  ) +
  scale_shape_manual(
    name   = NULL,
    values = c("UK Biobank"    = 16,
               "All of Us"     = 17,
               "Meta-analysis" = 23),
    breaks = c("UK Biobank", "All of Us", "Meta-analysis"),
    drop   = FALSE
  ) +
  scale_fill_manual(
    name   = NULL,
    values = c("UK Biobank"    = NA,
               "All of Us"     = NA,
               "Meta-analysis" = "#7570b3"),
    breaks = c("UK Biobank", "All of Us", "Meta-analysis"),
    drop   = FALSE,
    guide  = "none"
  ) +
  guides(
    shape  = "none",
    colour = guide_legend(
      override.aes = list(
        shape = c(16, 17, 23),
        size  = c(3.5, 3.5, 4),
        fill  = c("#1b9e77", "#d95f02", "#7570b3")
      )
    )
  ) +

  # `clip = "off"` lets the p-value comparison boxes render even when their
  # right edge extends past xlim — at size = 4.2 in monospace, a 23-char-wide
  # box is ~0.21 data units, so starting at x_text = 0.71 it lands on / past
  # the panel edge. Without clip="off" the boxes vanish entirely.
  coord_cartesian(xlim = c(0.45, 0.95), clip = "off") +
  scale_x_continuous(breaks = seq(0.45, 0.75, 0.05)) +

  labs(x = "Area Under Receiver-Operator-Characteristic Curve (95% CI)",
       y = "Risk Stratification Definition",
       title = "Per-Event Analyses Summary",
       subtitle = "Outcome = Recurrence within 5 years (defined as at least 1 subsequent event)") +

  theme_bw(base_size = 12) +
  theme(
    strip.text.x      = element_text(face = "bold", size = 14),
    # `angle = 90` rotates the left-side row strip text to vertical (reads
    # bottom-to-top) per supervisor request. Strip labels are now bare
    # ordinals ("First"/"Second"/...) so they fit even in the short 1-row
    # "First" facet at size 11; the "Kidney Stone Presentation Number" outer
    # label (added in the gtable step below) explains what they denote.
    strip.text.y.left = element_text(angle = 90, face = "bold", size = 11),
    strip.background  = element_rect(fill = "grey95"),
    strip.placement   = "outside",
    panel.spacing     = unit(0.8, "lines"),
    legend.position   = "bottom",
    legend.text       = element_text(size = 12),
    axis.text.x       = element_text(size = 11),
    axis.text.y       = element_text(size = 11),
    axis.title.x      = element_text(size = 13),
    # After the gtable swap, the y-axis title sits between the strip column
    # and the axis-text column. `margin(l = ...)` adds whitespace to the LEFT
    # of the rotated title (i.e. between the strip and the title), shifting
    # the title rightward within its column.
    axis.title.y      = element_text(size = 13, margin = margin(l = 12, r = 4)),
    plot.title        = element_text(face = "bold", size = 16),
    plot.subtitle     = element_text(size = 11, colour = "grey30")
  )

# -----------------------------------------------------------------------------
# Post-hoc layout: place the y-axis title BETWEEN the strip labels (outermost)
# and the y-tick labels — a configuration ggplot doesn't natively support
# (ggplot always puts the axis title outermost). We do this by converting the
# plot to a gtable, finding the `ylab-l` column (axis title) and the `strip-l`
# columns (facet strips), and swapping their column positions + widths so the
# strip is outermost and the title sits inside it but outside the axis text.
# -----------------------------------------------------------------------------
suppressMessages({ library(grid); library(gtable) })

g_fig1 <- ggplotGrob(p_fig1)

ylab_idx  <- which(g_fig1$layout$name == "ylab-l")
strip_idx <- grep("^strip-l", g_fig1$layout$name)

if (length(ylab_idx) == 1 && length(strip_idx) >= 1) {
  ylab_col  <- g_fig1$layout$l[ylab_idx]
  strip_col <- g_fig1$layout$l[strip_idx][1]   # all strip-l share one column

  # Swap column indices in the layout table.
  g_fig1$layout$l[ylab_idx]  <- strip_col
  g_fig1$layout$r[ylab_idx]  <- strip_col
  g_fig1$layout$l[strip_idx] <- ylab_col
  g_fig1$layout$r[strip_idx] <- ylab_col

  # Swap widths so the strip column gets the strip's natural width and the
  # title column gets the title's narrower width.
  w_ylab  <- g_fig1$widths[ylab_col]
  w_strip <- g_fig1$widths[strip_col]
  g_fig1$widths[ylab_col]  <- w_strip
  g_fig1$widths[strip_col] <- w_ylab
}

# -----------------------------------------------------------------------------
# Add an OUTER y-axis label ("Kidney Stone Presentation Number") to the LEFT of
# the (now-outermost) strip column, describing what the First/Second/Third/
# Fourth strip labels denote. Insert a new gtable column just left of the strip
# and place a rotated textGrob spanning all panel rows.
# -----------------------------------------------------------------------------
strip_now_col <- g_fig1$layout$l[strip_idx][1]   # strip column AFTER the swap
# Faceted ggplots name panels "panel-<row>-<col>", NOT "panel" — use a prefix
# match so panel_t/panel_b span all facet rows.
panel_idx     <- grep("^panel", g_fig1$layout$name)
panel_t       <- min(g_fig1$layout$t[panel_idx])
panel_b       <- max(g_fig1$layout$b[panel_idx])

g_fig1 <- gtable::gtable_add_cols(g_fig1,
                                  widths = unit(1.3, "lines"),
                                  pos    = strip_now_col - 1)
outer_col <- strip_now_col   # freshly-added column sits where strip was; strip shifts right

g_fig1 <- gtable::gtable_add_grob(
  g_fig1,
  grobs = grid::textGrob(
    "Kidney Stone Presentation Number",
    rot = 90,
    gp  = grid::gpar(fontsize = 13, fontface = "bold", col = "grey20")
  ),
  t = panel_t, b = panel_b,
  l = outer_col, r = outer_col,
  z = Inf, name = "outer-ylab", clip = "off"
)

grid.newpage()
grid.draw(g_fig1)
```

**Figure 1:** Forest plot of area under the receiver-operator-characteristic curve (AUC-ROC) for various definitions of European Association of Urology (EAU) risk stratification's predictive ability for 5-year recurrence in the 'Per-Event analyses', stratified by kidney stone presentation number. The y-axis denotes the *Short Time Between Events*: Baseline = no 'recurrent disease' or 'short time' definition, and 6/24 mo = Baseline + 'short time' definition of 6 or 24 months. Dashed line indicates AUC = 0.5 i.e. no difference between high/low risk, Dot/Dash line indicates AUC = 0.7 (generally accepted threshold for meaningful clinical difference). Green circle = UK Biobank, Orange triangle = All of Us, Purple diamond = DerSimonian-Laird random-effects meta-analysis of UK Biobank (UKB) + All of Us (AoU). The diamond's horizontal extent indicates the pooled 95% confidence interval (CI). The boxed inset tables reports three pairwise Wald-test *p*-values comparing the pooled meta-analytic AUCs.

\newpage

## Figure 2

```{r fig2-eau-vs-recurrent-disease, fig.width=11, fig.height=11, out.width="100%"}
# --- Load per-cohort whole-dataset analysis results ---
# These come from the whole-dataset analysis (every participant contributes
# one row per transition they reach, using per-event re-ascertained EAU risk),
# saved by `prognostic_accuracy_grid_search.Rmd` and `symptomatic_occurences.ipynb`.
ukb_p <- read.csv("UKB Recurrence paper results/recurrent_disease_whole_dataset_metrics.csv",
                  check.names = FALSE)
aou_p <- read.csv("AoU Recurrence paper results/recurrent_disease_whole_dataset_metrics_aou.csv",
                  check.names = FALSE)

# Figure 2 is strictly a forest of EAU stratification \u00b1 "Short Time" \u00b1 "Recurrent"
# modifiers. The whole-dataset CSVs additionally contain the non-EAU
# "\u22652 prior events (no EAU)" classifier used in Sup Fig 17 / Sup Table 6 \u2014
# that row does not belong in any of Figure 2's EAU + modifier families and is
# excluded here. Without this filter the row falls through classify_row() into
# the "EAU only (baseline)" facet because its label says "prior events" rather
# than "events", silently inflating the EAU-only meta-analysis.
ukb_p <- ukb_p[!grepl("no EAU", ukb_p$Comparison, fixed = TRUE), , drop = FALSE]
aou_p <- aou_p[!grepl("no EAU", aou_p$Comparison, fixed = TRUE), , drop = FALSE]

# Relabel each classifier definition. We detect three orthogonal features
# in each Comparison string:
#   - rec_def: "\u22652", "\u22653", "\u22654", or "none"
#   - st_cut : 6, 24, or NA (no short-time modifier)
# and combine them into a Group label and a Risk_Family for facetting.
classify_row <- function(rd) {
  has_2  <- grepl("\u22652 events", rd)
  has_3  <- grepl("\u22653 events", rd)
  has_4  <- grepl("\u22654 events", rd)
  has_st6  <- grepl("Short Time \u22646mo|Short Time <=6mo|Short Time \\u22646mo", rd)
  has_st24 <- grepl("Short Time \u226424mo|Short Time <=24mo|Short Time \\u226424mo", rd)
  rec <- dplyr::case_when(
    has_2 ~ "\u22652 events",
    has_3 ~ "\u22653 events",
    has_4 ~ "\u22654 events",
    TRUE  ~ "none"
  )
  st <- dplyr::case_when(
    has_st6  ~ "Short Time \u22646mo",
    has_st24 ~ "Short Time \u226424mo",
    TRUE     ~ "no short time"
  )
  list(rec = rec, st = st)
}
classified_ukb <- lapply(ukb_p$Comparison, classify_row)
ukb_p$rec_def <- vapply(classified_ukb, function(x) x$rec, character(1))
ukb_p$st_def  <- vapply(classified_ukb, function(x) x$st,  character(1))
classified_aou <- lapply(aou_p$Comparison, classify_row)
aou_p$rec_def <- vapply(classified_aou, function(x) x$rec, character(1))
aou_p$st_def  <- vapply(classified_aou, function(x) x$st,  character(1))

# Build human-readable Group label (per-row) and a Risk_Family (facet).
# "EAU" / "EAU only (baseline)" are now rendered as "Baseline" per supervisor
# request — the underlying classifier is still the EAU urolithiasis risk
# stratification, the relabeling is purely cosmetic.
make_group <- function(rec, st) {
  if (rec == "none" && st == "no short time") return("Baseline")
  base <- if (rec == "none") "Baseline" else paste0("Baseline + ", rec)
  if (st == "no short time") base else paste0(base, " + ", st)
}
make_family <- function(rec, st) {
  # Classifiers without a recurrent-disease (≥N events) modifier are pooled
  # into a single "Nil" facet — covers both the plain Baseline and the
  # Short Time ≤6mo / ≤24mo variants. Within that facet, sub_label()
  # differentiates the three rows on the y-axis.
  if (rec == "none") return("Nil")
  rec
}

ukb_p$Group        <- mapply(make_group,  ukb_p$rec_def, ukb_p$st_def)
ukb_p$Risk_Family  <- mapply(make_family, ukb_p$rec_def, ukb_p$st_def)
aou_p$Group        <- mapply(make_group,  aou_p$rec_def, aou_p$st_def)
aou_p$Risk_Family  <- mapply(make_family, aou_p$rec_def, aou_p$st_def)
ukb_p$Cohort <- "UKB"; aou_p$Cohort <- "AoU"

# Standardise the DeLong p-value column name across the two CSVs
ukb_p$delong_p <- ukb_p$delong_p_vs_EAU_only
aou_p$delong_p <- aou_p$delong_p_vs_EAU_only

studies <- rbind(
  ukb_p[, c("Group","Risk_Family","AUC_val","AUC_lo","AUC_hi","delong_p","Cohort")],
  aou_p[, c("Group","Risk_Family","AUC_val","AUC_lo","AUC_hi","delong_p","Cohort")]
)

group_levels <- c(
  "Baseline",
  "Baseline + Short Time \u22646mo",
  "Baseline + Short Time \u226424mo",
  "Baseline + \u22652 events",
  "Baseline + \u22652 events + Short Time \u22646mo",
  "Baseline + \u22652 events + Short Time \u226424mo",
  "Baseline + \u22653 events",
  "Baseline + \u22653 events + Short Time \u22646mo",
  "Baseline + \u22653 events + Short Time \u226424mo",
  "Baseline + \u22654 events",
  "Baseline + \u22654 events + Short Time \u22646mo",
  "Baseline + \u22654 events + Short Time \u226424mo"
)
family_levels <- c("Nil",
                   "\u22652 events", "\u22653 events", "\u22654 events")

studies$Group       <- factor(studies$Group,       levels = group_levels)
studies$Risk_Family <- factor(studies$Risk_Family, levels = family_levels)

# --- DerSimonian-Laird random-effects meta-analysis on AUC ---
# With only 2 cohorts the between-study variance estimate (tau^2) is
# unstable, but the user explicitly requested random-effects pooling so
# between-cohort heterogeneity is acknowledged in the SE. When tau^2 = 0
# (no detectable heterogeneity) the pool collapses to fixed-effect IVM.
re_meta <- function(est, lo, hi) {
  se <- (hi - lo) / (2 * 1.96)
  ok <- is.finite(se) & se > 0 & is.finite(est)
  est <- est[ok]; se <- se[ok]; vi <- se^2
  k <- length(est)
  if (k < 1) return(c(est = NA_real_, lo = NA_real_, hi = NA_real_, tau2 = NA_real_))
  if (k == 1) return(c(est = est, lo = est - 1.96*se, hi = est + 1.96*se, tau2 = 0))
  w_fe <- 1 / vi
  fe_pe <- sum(w_fe * est) / sum(w_fe)
  Q  <- sum(w_fe * (est - fe_pe)^2)
  C  <- sum(w_fe) - sum(w_fe^2) / sum(w_fe)
  tau2 <- max(0, (Q - (k - 1)) / C)
  w_re <- 1 / (vi + tau2)
  pe   <- sum(w_re * est) / sum(w_re)
  pse  <- sqrt(1 / sum(w_re))
  c(est = pe, lo = pe - 1.96 * pse, hi = pe + 1.96 * pse, tau2 = tau2)
}

# --- Fisher's combined p-value across cohorts (treats two as independent tests) ---
fisher_combine <- function(ps) {
  ps <- ps[is.finite(ps) & ps > 0 & ps <= 1]
  if (length(ps) < 1) return(NA_real_)
  if (length(ps) == 1) return(ps)
  X <- -2 * sum(log(ps))
  1 - pchisq(X, df = 2 * length(ps))
}

pooled <- studies %>%
  group_by(Group, Risk_Family) %>%
  summarise(
    UKB_p    = first(delong_p[Cohort == "UKB"]),
    AoU_p    = first(delong_p[Cohort == "AoU"]),
    fisher_p = fisher_combine(c(first(delong_p[Cohort == "UKB"]),
                                 first(delong_p[Cohort == "AoU"]))),
    pe = list(re_meta(AUC_val, AUC_lo, AUC_hi)),
    .groups = "drop"
  ) %>%
  mutate(
    AUC_val = sapply(pe, `[`, "est"),
    AUC_lo  = sapply(pe, `[`, "lo"),
    AUC_hi  = sapply(pe, `[`, "hi")
  ) %>%
  dplyr::select(-pe) %>%
  mutate(Cohort = "Meta-analysis")

# --- Build long row_id factor for plotting ---
all_rows <- bind_rows(
  studies %>% dplyr::select(Group, Risk_Family, Cohort, AUC_val, AUC_lo, AUC_hi),
  pooled  %>% dplyr::select(Group, Risk_Family, Cohort, AUC_val, AUC_lo, AUC_hi)
) %>%
  mutate(Cohort = factor(Cohort, levels = c("UKB","AoU","Meta-analysis")))

all_rows$row_id <- factor(
  paste(as.character(all_rows$Group), all_rows$Cohort, sep = " | "),
  levels = unlist(lapply(group_levels, function(g)
    paste(g, c("UKB","AoU","Meta-analysis"), sep = " | ")))
)
all_rows$row_id <- forcats::fct_rev(all_rows$row_id)
all_rows$y_num  <- as.integer(all_rows$row_id)

# Within-family sub-label shown on the y-axis (the family itself sits in the
# strip on the left, so we only need the differentiator within the family).
sub_label <- function(g) dplyr::case_when(
  g == "Baseline"                              ~ "Baseline",
  g == "Baseline + Short Time ≤6mo"            ~ "+ Short Time ≤6mo",
  g == "Baseline + Short Time ≤24mo"           ~ "+ Short Time ≤24mo",
  grepl("Short Time ≤6mo$",  g)                ~ "+ Short Time ≤6mo",
  grepl("Short Time ≤24mo$", g)                ~ "+ Short Time ≤24mo",
  grepl("≥[234] events$", g)                   ~ "Baseline",
  TRUE                                          ~ as.character(g)
)
all_rows$sub_label <- sub_label(as.character(all_rows$Group))

studies_plot <- all_rows %>% filter(Cohort != "Meta-analysis")
pooled_plot  <- all_rows %>% filter(Cohort == "Meta-analysis" & is.finite(AUC_val))

diamond_h <- 0.30
diamond_df <- pooled_plot %>%
  rowwise() %>%
  do(data.frame(
    Group       = .$Group,
    Risk_Family = .$Risk_Family,
    Cohort = factor("Meta-analysis", levels = c("UKB","AoU","Meta-analysis")),
    x = c(.$AUC_lo, .$AUC_val, .$AUC_hi, .$AUC_val),
    y = .$y_num + c(0, diamond_h, 0, -diamond_h)
  )) %>%
  ungroup()

# NOTE: per-classifier Fisher-combined DeLong p-values used to be annotated
# on this plot; they have been moved to Supplementary Table 4 to allow ALL
# pairwise comparisons (not just vs EAU only) to be reported.

# Y-axis labels: show the within-family differentiator at every row position.
# Each Group has 3 rows (UKB top, AoU middle, Pooled bottom). Anchoring to
# the AoU row centres the label vertically on the 3-row block.
y_label_lookup <- all_rows %>%
  dplyr::distinct(y_num, sub_label, Cohort) %>%
  dplyr::filter(Cohort == "AoU") %>%   # middle row → label is centred on the block
  dplyr::arrange(y_num)
# Build a label vector indexed by integer y position
y_labels <- rep("", length(levels(all_rows$row_id)))
y_labels[y_label_lookup$y_num] <- y_label_lookup$sub_label

# --- Within-facet group dividers ---
# Each Group occupies 3 consecutive y_num values (UKB / AoU / Pooled). To
# make the boundary between consecutive Groups within a Risk_Family clearer,
# draw a faint horizontal line at y = (top of group below) + 0.5 — i.e. just
# above each non-bottom Group within each facet.
group_dividers <- all_rows %>%
  dplyr::distinct(Risk_Family, Group, y_num) %>%
  dplyr::group_by(Risk_Family, Group) %>%
  dplyr::summarise(y_max = max(y_num), .groups = "drop") %>%
  dplyr::group_by(Risk_Family) %>%
  dplyr::arrange(desc(y_max), .by_group = TRUE) %>%
  dplyr::slice(-1) %>%        # drop the topmost group in each facet (no divider above it)
  dplyr::ungroup() %>%
  dplyr::mutate(y_div = y_max + 0.5)

p_fig2 <- ggplot() +
  annotate("rect", xmin = -Inf, xmax = 0.5, ymin = -Inf, ymax = Inf,
           fill = "#F4A3A3", alpha = 0.2) +
  annotate("rect", xmin = 0.5, xmax = 0.7, ymin = -Inf, ymax = Inf,
           fill = "#F6D186", alpha = 0.2) +
  annotate("rect", xmin = 0.7, xmax = Inf, ymin = -Inf, ymax = Inf,
           fill = "#A6D96A", alpha = 0.2) +

  geom_vline(xintercept = 0.5, linetype = "dashed", colour = "grey40", linewidth = 0.7) +
  geom_vline(xintercept = 0.7, linetype = "dotdash", colour = "darkgreen", linewidth = 0.7) +

  # Faint horizontal dividers between Groups within each Risk_Family facet.
  geom_hline(data = group_dividers,
             aes(yintercept = y_div),
             colour = "grey40", linewidth = 0.4, alpha = 1) +

  geom_errorbarh(data = studies_plot,
                 aes(xmin = AUC_lo, xmax = AUC_hi, y = y_num, colour = Cohort),
                 height = 0.25, linewidth = 0.9) +
  facet_grid(Risk_Family ~ .,
             scales = "free_y", space = "free_y", switch = "y") +
  geom_point(data = studies_plot,
             aes(x = AUC_val, y = y_num, colour = Cohort, shape = Cohort),
             size = 3, na.rm = TRUE) +
  # NOTE: map colour = Cohort (not a fixed "black") so the "Meta-analysis"
  # level actually enters the colour aesthetic's data. Otherwise the colour
  # legend key for "Meta-analysis" has no underlying data row, and the
  # override.aes diamond glyph is silently dropped (only the label is shown).
  # `key_glyph = draw_key_point` overrides the default polygon-key (which is
  # a filled square and ignores `shape`) so override.aes(shape = 23) is
  # honoured for the meta-analysis key, rendering a filled diamond.
  geom_polygon(data = diamond_df,
               aes(x = x, y = y, group = Group,
                   colour = Cohort, fill = Cohort),
               linewidth = 0.3,
               key_glyph = draw_key_point) +

  scale_y_continuous(breaks = seq_along(y_labels),
                     labels = y_labels,
                     expand = expansion(add = 0.6)) +
  # Unified single legend: UKB → AoU → Meta-analysis, with the
  # meta-analysis key shown as a filled diamond to match the polygon.
  scale_colour_manual(
    name   = NULL,
    values = c("UKB" = "#1b9e77",
               "AoU" = "#d95f02",
               "Meta-analysis" = "#7570b3"),
    breaks = c("UKB", "AoU", "Meta-analysis"),
    drop   = FALSE
  ) +
  scale_shape_manual(
    name   = NULL,
    values = c("UKB" = 16, "AoU" = 17, "Meta-analysis" = 23),
    breaks = c("UKB", "AoU", "Meta-analysis"),
    drop   = FALSE
  ) +
  scale_fill_manual(
    name   = NULL,
    values = c("UKB" = NA, "AoU" = NA, "Meta-analysis" = "#7570b3"),
    drop   = FALSE,
    guide  = "none"
  ) +
  guides(
    shape  = "none",
    colour = guide_legend(
      override.aes = list(
        shape = c(16, 17, 23),
        size  = c(3, 3, 4),
        fill  = c("#1b9e77", "#d95f02", "#7570b3")
      )
    )
  ) +

  coord_cartesian(xlim = c(0.49, 0.72)) +
  labs(x = "AUC (95% CI)",
       y = "Recurrent Disease Definition",
       title = "Any Event Analyses Summary",
       subtitle = "Outcome = Recurrence within 5 years (defined as at least 1 subsequent event)") +
  theme_bw(base_size = 10) +
  theme(strip.text.x = element_text(face = "bold", size = 11),
        # `angle = 90` rotates the left-side row strip text to vertical (reads
        # bottom-to-top) — matches Figure 1's strip orientation.
        strip.text.y.left = element_text(angle = 90, face = "bold", size = 9),
        strip.background = element_rect(fill = "grey95"),
        strip.placement = "outside",
        panel.spacing = unit(0.8, "lines"),
        legend.position = "bottom",
        axis.text.y = element_text(size = 8),
        axis.title.y = element_text(size = 12),
        plot.title = element_text(face = "bold", size = 13))

# -----------------------------------------------------------------------------
# Layout: keep the standard outside y-axis title ("Recurrent Disease Definition")
# AND insert a second rotated label INSIDE the grid, between the facet strip
# and the y-tick labels. ggplot has only one axis-title slot, so we open a
# new gtable column at that position and add a textGrob into it.
# -----------------------------------------------------------------------------
suppressMessages({ library(grid); library(gtable) })

g_fig2 <- ggplotGrob(p_fig2)

# Locate the leftmost axis-text column (this is where the y-tick labels live).
axis_l_col <- min(g_fig2$layout$l[grep("^axis-l", g_fig2$layout$name)])

# Cache the panel rows BEFORE the column insertion — rows don't shift.
# Faceted ggplots name panels "panel-<row>-<col>", NOT "panel" — use a prefix
# match so panel_t/panel_b span all facet rows.
panel_idx <- grep("^panel", g_fig2$layout$name)
panel_t   <- min(g_fig2$layout$t[panel_idx])
panel_b   <- max(g_fig2$layout$b[panel_idx])

# Insert a new column immediately to the LEFT of axis-l (i.e. between the
# strip column and the y-tick column). gtable_add_cols(pos = K) adds the new
# column at position K+1 and shifts existing cols ≥ K+1 right by one. So
# pos = axis_l_col - 1 places the new column at axis_l_col, and axis-l/panels
# shift right by one.
g_fig2 <- gtable::gtable_add_cols(g_fig2,
                                  widths = unit(0.9, "lines"),
                                  pos    = axis_l_col - 1)
new_col <- axis_l_col   # column index of the freshly-added column

# The textGrob for the inside title — same orientation as the outside y-axis
# title (rotated 90° CCW, reads bottom-to-top).
inside_label <- grid::textGrob(
  "Baseline only or Including 'Short Time' Definition",
  rot = 90,
  gp  = grid::gpar(fontsize = 10, fontface = "plain", col = "grey20")
)

g_fig2 <- gtable::gtable_add_grob(
  g_fig2,
  grobs = inside_label,
  t = panel_t, b = panel_b,
  l = new_col, r = new_col,
  z = Inf,
  name = "inside-ylab",
  clip = "off"
)

grid.newpage()
grid.draw(g_fig2)
```

**Figure 2:** Forest plot of area under the receiver-operator-characteristic curve (AUC-ROC) for predictive accuracy of various definitions of risk stratification for 5-year recurrence within the 'Any-Event' analyses. The Y-Axis details how the risk stratification is defined: Baseline = no 'recurrent disease' or 'short time' definition; Short time = Baseline + short time between stone events definitions of 6/24 months; >/= X events = recurrent disease definition, these are also stratified by Baseline only (e.g Risk definition = Baseline + recurrent disease >/= 2 events) and 'Short time' between events (as above). Vertical dashed line indicates AUC = 0.5 (no difference between high/low risk); vertical dot-dash line indicates AUC = 0.7 (the generally accepted threshold for meaningful clinical difference); horizontal grey lines within each block indicate a single analysis trio (UK Biobank (UKB)/All of Us (AoU)/Meta-analysis). Green circle = UK Biobank, Orange triangle = All of Us, Purple diamond = DerSimonian-Laird random-effects meta-analysis of UKB + AoU. The diamond's horizontal extent indicates the pooled 95% confidence interval (CI). Pairwise statistical comparisons across all classifiers are reported in **Supplementary Table 4**.

\newpage

## Figure 3

```{r fig3-km-likelihood, fig.width=10, fig.height=6, out.width="100%"}
# --- Panel A: 2-cell heatmap (1 vs ≥2 events only, no EAU stratification) ---
ukb_km <- read.csv("UKB Recurrence paper results/km_5y_recurrence_by_event_count.csv",
                   check.names = FALSE)
aou_km <- read.csv("AoU Recurrence paper results/km_5y_recurrence_by_event_count_aou.csv",
                   check.names = FALSE)

km_df <- rbind(ukb_km, aou_km)

# --- Relabel Group: "Low Risk (1 event)" → "1st Event"; "High Risk (≥2 events)" → "≥2 Events" ---
km_df$risk_group <- dplyr::case_when(
  grepl("1 event",  km_df$Group, ignore.case = TRUE) &
    !grepl("≥2", km_df$Group)                          ~ "1st Event",
  grepl("≥2",  km_df$Group)                            ~ "≥2 Events",
  TRUE                                                       ~ km_df$Group
)

km_df <- km_df %>%
  dplyr::select(Cohort, risk_group,
                pct = rec_5y_pct,
                lo  = rec_5y_lo_pct,
                hi  = rec_5y_hi_pct)

km_df$risk_group <- factor(km_df$risk_group, levels = c("1st Event", "≥2 Events"))
km_df$Biobank    <- factor(km_df$Cohort,     levels = c("UKB", "AoU"))

# --- Annotation text ---
km_df$label_text <- paste0(
  sprintf("%.1f%%", km_df$pct),
  "\n(",
  sprintf("%.1f", km_df$lo), "–",
  sprintf("%.1f", km_df$hi),
  "%)"
)

# --- Relative likelihood within each cohort (rescale 0-100) ---
km_df_scaled <- km_df %>%
  group_by(Biobank) %>%
  mutate(pct_scaled = scales::rescale(pct, to = c(0, 100))) %>%
  ungroup()

# --- DerSimonian-Laird random-effects meta-analysis on the LOGIT scale ---
re_meta_logit <- function(theta, vi) {
  theta <- unname(theta); vi <- unname(vi)
  k <- length(theta)
  if (k < 1) return(c(theta = NA_real_, se = NA_real_))
  if (k == 1) return(c(theta = theta[1], se = sqrt(vi[1])))
  w_fe <- 1 / vi
  fe_pe <- sum(w_fe * theta) / sum(w_fe)
  Q  <- sum(w_fe * (theta - fe_pe)^2)
  C  <- sum(w_fe) - sum(w_fe^2) / sum(w_fe)
  tau2 <- max(0, (Q - (k - 1)) / C)
  w_re <- 1 / (vi + tau2)
  pe   <- sum(w_re * theta) / sum(w_re)
  pse  <- sqrt(1 / sum(w_re))
  c(theta = pe, se = pse)
}

meta_df <- km_df %>%
  mutate(p    = pct / 100,
         lo_p = lo  / 100,
         hi_p = hi  / 100,
         theta    = log(p    / (1 - p)),
         theta_lo = log(lo_p / (1 - lo_p)),
         theta_hi = log(hi_p / (1 - hi_p)),
         se = (theta_hi - theta_lo) / (2 * 1.96),
         vi = se^2) %>%
  group_by(risk_group) %>%
  summarise(
    pe = list(re_meta_logit(theta, vi)),
    .groups = "drop"
  ) %>%
  mutate(
    theta_meta = sapply(pe, `[`, "theta"),
    se_meta    = sapply(pe, `[`, "se"),
    p_meta     = 1 / (1 + exp(-theta_meta)),
    lo_meta    = 1 / (1 + exp(-(theta_meta - 1.96 * se_meta))),
    hi_meta    = 1 / (1 + exp(-(theta_meta + 1.96 * se_meta))),
    Biobank    = factor("Meta-analysis", levels = c("UKB","AoU","Meta-analysis")),
    pct        = p_meta * 100,
    lo         = lo_meta * 100,
    hi         = hi_meta * 100,
    pct_scaled = scales::rescale(pct, to = c(0, 100)),
    label_text = paste0(
      sprintf("%.1f%%", pct), "\n(",
      sprintf("%.1f", lo), "–", sprintf("%.1f", hi), "%)"
    )
  ) %>%
  dplyr::select(risk_group, Biobank, pct, lo, hi, pct_scaled, label_text)

df_plot <- bind_rows(
  km_df_scaled %>% dplyr::select(risk_group, Biobank, pct, lo, hi, pct_scaled, label_text),
  meta_df
)
df_plot$Biobank <- factor(df_plot$Biobank, levels = c("UKB", "AoU", "Meta-analysis"))

# --- Plot ---
ggplot(df_plot, aes(x = risk_group, y = "5-year recurrence", fill = pct_scaled)) +
  geom_tile(colour = "black", linewidth = 0.4) +
  geom_text(aes(label = label_text), size = 6, lineheight = 0.85, colour = "black") +
  facet_grid2(Biobank ~ .,
              strip = strip_themed(background_y = elem_list_rect(
                fill = c("#FFFFFF","#FFFFFF","#D6EAF8"),
                colour = "black", linewidth = 0.6))) +
  scale_x_discrete(position = "top") +
  scale_fill_gradient2(low = "#A6D96A", mid = "#FFFFF0", high = "#E34A33",
                       midpoint = 50, limits = c(0, 100),
                       name = "Relative likelihood\nwithin Each Biobank (%)") +
  labs(x = NULL, y = NULL,
       title = "(A) 5-Year Cumulative Recurrence Likelihood") +
  theme_minimal(base_size = 11) +
  theme(
    axis.text.x  = element_text(face = "bold", colour = "black", size = 12),
    axis.text.y  = element_blank(),
    axis.ticks.x = element_line(colour = "black"),
    axis.line.x  = element_line(colour = "black"),
    panel.spacing = unit(1.4, "lines"),
    strip.text.y = element_text(face = "bold", size = 12),
    plot.title   = element_text(face = "bold")
  )
```

\begin{center}

\vspace{0.4em}
\textbf{(B) Kaplan-Meier survival curves: ≥2 vs 1 prior event}\\[0.3em]
\begin{minipage}{0.48\textwidth}
\centering
\textbf{(B1) UK Biobank}\\[0.2em]
\includegraphics[width=\textwidth]{UKB Recurrence paper results/recurrent_disease_km_2plus.pdf}
\end{minipage}
\hfill
\begin{minipage}{0.48\textwidth}
\centering
\textbf{(B2) All of Us}\\[0.2em]
\includegraphics[width=\textwidth]{AoU Recurrence paper results/recurrent_disease_km_2plus_aou.pdf}
\end{minipage}

\end{center}

**Figure 3:** **(A)** Heatmap of likelihood of recurrence within 5 years stratified by number of prior events. This excludes any European Association of Urology (EAU) risk stratification. *1st Event* = participants at their first stone event. *≥2 Events* = participants at any subsequent transition. Cells are coloured by relative likelihood within each cohort (rescaled 0-100), and the Meta-analysis row is the DerSimonian-Laird random-effects pool of UKB and AoU on a logit scale. **(B)** Kaplan-Meier 5-year event-free survival curves stratified by event-count group, for UK Biobank (C1) and All of Us (C2); log-rank *p*-value annotated on each panel.

\newpage

# Supplementary Figures

### Supplementary Figure 1: Consort Flow Diagram

\begin{center}
\includegraphics[width=\textwidth]{Supplementary Figure 1.pdf}
\end{center}

**Supplementary Figure 1:** Consolidated Standards of Reporting Trials (CONSORT)-style flow diagram of cohort construction in UK Biobank and All of Us, showing the number of participants identified with a symptomatic kidney-stone event and the exclusions applied at each step to arrive at the final cohorts.

\newpage

## Sensitivity-analysis Forest Plot (Full Grid)

#### Supplementary Figure 2: Sensitivity-analysis forest plot

```{r supfig55-forest, fig.width=11, fig.height=16, fig.align="center", out.width="100%"}
# Sensitivity-analysis forest plot \u2014 same idiom as main-text Figure 1 but
# without the filters that restricted Figure 1 to the \u22651 subsequent-event
# definition and the 6-/24-month cutoffs only. Shows every (event \u00d7 cutoff \u00d7
# recurrence-definition) combination.

# --- Load + combine ---
ukb <- read.csv("UKB Recurrence paper results/prognostic_accuracy_grid_search_results.csv")
aou <- read.csv("AoU Recurrence paper results/prognostic_accuracy_grid_search_results_aou.csv")
aou <- aou[!duplicated(aou[, c("Starting_Point","Time_Cutoff_Months","Recurrence_Definition")]), ]

event_map <- c("Index Date"   = "First",
               "Second Event" = "Second",
               "Third Event"  = "Third",
               "Fourth Event" = "Fourth")

make_label <- function(sp, c) {
  e <- event_map[sp]
  if (is.na(c) | c == "NA") e else paste0(e, " (", c, "mo)")
}

ukb$Biobank <- "UK Biobank"
ukb$label   <- mapply(make_label, ukb$Starting_Point, as.character(ukb$Time_Cutoff_Months))
aou$Biobank <- "All of Us"
aou$label   <- mapply(make_label, aou$Starting_Point, as.character(aou$Time_Cutoff_Months))

cols <- c("label","Starting_Point","Time_Cutoff_Months","Recurrence_Definition",
          "AUC_val","AUC_lo","AUC_hi","Biobank")
df <- rbind(ukb[, cols], aou[, cols])
df$AUC_val <- as.numeric(df$AUC_val); df$AUC_lo <- as.numeric(df$AUC_lo); df$AUC_hi <- as.numeric(df$AUC_hi)

# Keep only 6-month-interval cutoffs (drop 9 / 15 / 21 mo) plus the index
# event (NA cutoff). Leaves Baseline + 6 / 12 / 18 / 24 mo.
.cut <- suppressWarnings(as.numeric(df$Time_Cutoff_Months))
df <- df[is.na(.cut) | .cut %in% c(6, 12, 18, 24), , drop = FALSE]

# --- DerSimonian-Laird random-effects meta-analysis on AUC ---
re_meta_auc <- function(est, lo, hi) {
  se <- (hi - lo) / (2 * 1.96)
  ok <- is.finite(se) & se > 0 & is.finite(est)
  est <- est[ok]; se <- se[ok]; vi <- se^2
  k <- length(est)
  if (k < 1) return(c(est = NA_real_, lo = NA_real_, hi = NA_real_))
  if (k == 1) return(c(est = est, lo = est - 1.96*se, hi = est + 1.96*se))
  w_fe <- 1 / vi
  fe_pe <- sum(w_fe * est) / sum(w_fe)
  Q  <- sum(w_fe * (est - fe_pe)^2)
  C  <- sum(w_fe) - sum(w_fe^2) / sum(w_fe)
  tau2 <- max(0, (Q - (k - 1)) / C)
  w_re <- 1 / (vi + tau2)
  pe   <- sum(w_re * est) / sum(w_re)
  pse  <- sqrt(1 / sum(w_re))
  c(est = pe, lo = pe - 1.96 * pse, hi = pe + 1.96 * pse)
}

meta_auc <- df %>%
  mutate(SE = (AUC_hi - AUC_lo) / (2 * 1.96)) %>%
  filter(is.finite(SE) & SE > 0) %>%
  group_by(label, Starting_Point, Time_Cutoff_Months, Recurrence_Definition) %>%
  summarise(pe = list(re_meta_auc(AUC_val, AUC_lo, AUC_hi)), .groups = "drop") %>%
  mutate(
    AUC_val = sapply(pe, `[`, "est"),
    AUC_lo  = sapply(pe, `[`, "lo"),
    AUC_hi  = sapply(pe, `[`, "hi"),
    Biobank = "Meta-analysis"
  ) %>%
  dplyr::select(all_of(cols))
df <- rbind(df, meta_auc)

# --- Order ---
event_order <- c("First","Second","Third","Fourth")
df$event_label <- event_map[df$Starting_Point]
df$event_label <- factor(df$event_label, levels = event_order)
df$cutoff_num  <- ifelse(is.na(df$Time_Cutoff_Months), 0, as.numeric(df$Time_Cutoff_Months))
df$cutoff_label <- ifelse(df$cutoff_num == 0, "Baseline",
                          paste0("+ \u2264", df$Time_Cutoff_Months, "mo"))
# Place Baseline on top \u2192 make it the LAST factor level (level 1 sits at the
# bottom). Ordering top\u2192bottom: Baseline, + \u22646mo, + \u226412mo, + \u226418mo, + \u226424mo.
cutoff_levels <- c("+ \u226424mo", "+ \u226418mo", "+ \u226412mo", "+ \u22646mo", "Baseline")
df$cutoff_label <- factor(df$cutoff_label, levels = cutoff_levels)

df$Biobank <- factor(df$Biobank, levels = c("UK Biobank","All of Us","Meta-analysis"))

rec_labels <- c("\u22651 subsequent stone events" = "\u2265 1 Subsequent Stone Events",
                "\u22652 subsequent stone events" = "\u2265 2 Subsequent Stone Events",
                "\u22653 subsequent stone events" = "\u2265 3 Subsequent Stone Events")
df$rec_facet <- rec_labels[df$Recurrence_Definition]
df$rec_facet <- factor(df$rec_facet, levels = rec_labels)

# --- Studies + meta-analysis split + manual dodge ---
df_studies <- df %>% dplyr::filter(Biobank != "Meta-analysis")
df_meta    <- df %>% dplyr::filter(Biobank == "Meta-analysis")

dodge_w <- 0.7
df_studies$y_num <- as.numeric(df_studies$cutoff_label) +
  dplyr::case_when(
    df_studies$Biobank == "UK Biobank" ~ +dodge_w / 3,
    df_studies$Biobank == "All of Us"  ~  0
  )
df_meta$y_num <- as.numeric(df_meta$cutoff_label) - (dodge_w / 3)

# --- Diamond polygon vertices for meta-analysis ---
diamond_h <- 0.13
diamond_df <- df_meta %>%
  dplyr::rowwise() %>%
  dplyr::do(data.frame(
    label       = .$label,
    event_label = .$event_label,
    rec_facet   = .$rec_facet,
    Biobank     = "Meta-analysis",
    x = c(.$AUC_lo, .$AUC_val, .$AUC_hi, .$AUC_val),
    y = .$y_num + c(0, diamond_h, 0, -diamond_h)
  )) %>%
  dplyr::ungroup()

y_breaks <- seq_along(levels(df$cutoff_label))
y_labels <- levels(df$cutoff_label)

p_supfig2 <- ggplot() +

  annotate("rect", xmin = -Inf, xmax = 0.5, ymin = -Inf, ymax = Inf,
           fill = "#F4A3A3", alpha = 0.2) +
  annotate("rect", xmin = 0.5, xmax = 0.7, ymin = -Inf, ymax = Inf,
           fill = "#F6D186", alpha = 0.2) +
  annotate("rect", xmin = 0.7, xmax = Inf, ymin = -Inf, ymax = Inf,
           fill = "#A6D96A", alpha = 0.2) +

  geom_vline(xintercept = 0.5, linetype = "dashed",  colour = "grey40",   linewidth = 0.7) +
  geom_vline(xintercept = 0.7, linetype = "dotdash", colour = "darkgreen", linewidth = 0.7) +

  geom_errorbarh(data = df_studies,
                 aes(xmin = AUC_lo, xmax = AUC_hi, y = y_num, colour = Biobank),
                 height = 0.18, linewidth = 0.9) +
  geom_point(data = df_studies,
             aes(x = AUC_val, y = y_num, colour = Biobank, shape = Biobank),
             size = 3.5, stroke = 0.6) +
  # NOTE: map colour = Biobank (not a fixed "black") so the "Meta-analysis"
  # level actually enters the colour aesthetic's data. Otherwise the colour
  # legend key for "Meta-analysis" has no underlying data row, and the
  # override.aes diamond glyph is silently dropped (only the label is shown).
  # `key_glyph = draw_key_point` overrides the default polygon-key (which is
  # a filled square and ignores `shape`) so override.aes(shape = 23) is
  # honoured for the meta-analysis key, rendering a filled diamond.
  geom_polygon(data = diamond_df,
               aes(x = x, y = y, group = label,
                   colour = Biobank, fill = Biobank),
               linewidth = 0.3,
               key_glyph = draw_key_point) +

  facet_grid(event_label ~ rec_facet,
             scales = "free_y", space = "free_y", switch = "y") +

  scale_y_continuous(breaks = y_breaks, labels = y_labels,
                     expand = expansion(add = 0.6)) +
  # Unified single legend: UK Biobank → All of Us → Meta-analysis.
  scale_colour_manual(
    name   = NULL,
    values = c("UK Biobank"    = "#1b9e77",
               "All of Us"     = "#d95f02",
               "Meta-analysis" = "#7570b3"),
    breaks = c("UK Biobank", "All of Us", "Meta-analysis"),
    drop   = FALSE
  ) +
  scale_shape_manual(
    name   = NULL,
    values = c("UK Biobank" = 16, "All of Us" = 17, "Meta-analysis" = 23),
    breaks = c("UK Biobank", "All of Us", "Meta-analysis"),
    drop   = FALSE
  ) +
  scale_fill_manual(
    name   = NULL,
    values = c("UK Biobank" = NA, "All of Us" = NA,
               "Meta-analysis" = "#7570b3"),
    drop   = FALSE,
    guide  = "none"
  ) +
  guides(
    shape  = "none",
    colour = guide_legend(
      override.aes = list(
        shape = c(16, 17, 23),
        size  = c(3, 3, 4),
        fill  = c("#1b9e77", "#d95f02", "#7570b3")
      )
    )
  ) +

  coord_cartesian(xlim = c(0.45, 0.75), clip = "off") +
  scale_x_continuous(breaks = seq(0.45, 0.75, 0.05)) +

  labs(x = "Area Under Receiver-Operator-Characteristic Curve (95% CI)",
       y = "'Short Time Between Events' Definition (months)",
       title = "Per-Event Analyses Summary \u2014 Full Sensitivity Analysis",
       subtitle = "Outcome = Recurrence within 5 years, defined as:") +

  theme_bw(base_size = 12) +
  theme(
    # Column-facet (recurrence-definition) headers \u2014 reduced so the long
    # "\u2265 N Subsequent Stone Events" strings fit cleanly.
    strip.text.x      = element_text(face = "bold", size = 10),
    # `angle = 90` rotates the left-side row strip text to vertical \u2014 matches
    # Figure 1.
    strip.text.y.left = element_text(angle = 90, face = "bold", size = 11),
    strip.background  = element_rect(fill = "grey95"),
    strip.placement   = "outside",
    panel.spacing     = unit(0.8, "lines"),
    legend.position   = "bottom",
    legend.text       = element_text(size = 12),
    axis.text.x       = element_text(size = 11),
    axis.text.y       = element_text(size = 11),
    axis.title.x      = element_text(size = 13),
    # After the gtable swap, the y-axis title sits between the strip column and
    # the y-tick column; margin(l=...) shifts it rightward off the strip.
    axis.title.y      = element_text(size = 13, margin = margin(l = 12, r = 4)),
    plot.title        = element_text(face = "bold", size = 16),
    plot.subtitle     = element_text(size = 11, colour = "grey30")
  )

# -----------------------------------------------------------------------------
# Same post-hoc layout as Figure 1: (1) swap ylab-l with strip-l so the y-axis
# title sits BETWEEN the event strips and the y-tick labels; (2) add an OUTER
# column to the left of the strips with a rotated "Kidney Stone Presentation
# Number" label.
# -----------------------------------------------------------------------------
suppressMessages({ library(grid); library(gtable) })

g_supfig2 <- ggplotGrob(p_supfig2)

ylab_idx  <- which(g_supfig2$layout$name == "ylab-l")
strip_idx <- grep("^strip-l", g_supfig2$layout$name)

if (length(ylab_idx) == 1 && length(strip_idx) >= 1) {
  ylab_col  <- g_supfig2$layout$l[ylab_idx]
  strip_col <- g_supfig2$layout$l[strip_idx][1]

  g_supfig2$layout$l[ylab_idx]  <- strip_col
  g_supfig2$layout$r[ylab_idx]  <- strip_col
  g_supfig2$layout$l[strip_idx] <- ylab_col
  g_supfig2$layout$r[strip_idx] <- ylab_col

  w_ylab  <- g_supfig2$widths[ylab_col]
  w_strip <- g_supfig2$widths[strip_col]
  g_supfig2$widths[ylab_col]  <- w_strip
  g_supfig2$widths[strip_col] <- w_ylab
}

# Outer label to the LEFT of the (now-outermost) strip column.
strip_now_col <- g_supfig2$layout$l[strip_idx][1]
panel_idx     <- grep("^panel", g_supfig2$layout$name)
panel_t       <- min(g_supfig2$layout$t[panel_idx])
panel_b       <- max(g_supfig2$layout$b[panel_idx])

g_supfig2 <- gtable::gtable_add_cols(g_supfig2,
                                     widths = unit(1.3, "lines"),
                                     pos    = strip_now_col - 1)
outer_col <- strip_now_col

g_supfig2 <- gtable::gtable_add_grob(
  g_supfig2,
  grobs = grid::textGrob(
    "Kidney Stone Presentation Number",
    rot = 90,
    gp  = grid::gpar(fontsize = 13, fontface = "bold", col = "grey20")
  ),
  t = panel_t, b = panel_b,
  l = outer_col, r = outer_col,
  z = Inf, name = "outer-ylab", clip = "off"
)

grid.newpage()
grid.draw(g_supfig2)
```

**Supplementary Figure 2:** Forest plot of predictive value of risk stratification in the per-event analyses. This is an extension of Figure 1 and demonstrates the sensitivity analyses expanding the definition of 'recurrence' (i.e the outcome of interest) to 2/more or 3/more subsequent events. Background bands shade area under the curve (AUC) < 0.5 (red), 0.5–0.7 (amber) and ≥ 0.7 (green); dashed line at 0.5 = chance discrimination, dot-dash line at 0.7 = generally accepted clinical-usefulness threshold. Green circle = UK Biobank, orange triangle = All of Us, purple diamond = DerSimonian-Laird random-effects meta-analysis (the diamond's horizontal extent is the pooled 95% confidence interval (CI)).

\newpage

## Heatmaps

\blandscape

#### Supplementary Figure 3: Grid Search Heatmap – AUC

\begin{center}
\textbf{(A) UK Biobank}\\[0.4em]
\includegraphics[width=\textheight,height=0.86\textwidth,keepaspectratio]{UKB Recurrence paper results/grid_search_heatmap_auc.pdf}
\end{center}

\newpage

\begin{center}
\textbf{(B) All of Us}\\[0.4em]
\includegraphics[width=\textheight,height=0.86\textwidth,keepaspectratio]{AoU Recurrence paper results/grid_search_heatmap_auc_aou.pdf}
\end{center}

**Supplementary Figure 3:** Heatmap of area under the receiver-operating-characteristic (ROC) curve (AUC) for European Association of Urology (EAU) risk stratification across starting stone event (rows) and inter-event-time cutoff (columns: Baseline / ≤6 / ≤12 / ≤18 / ≤24 months), faceted by recurrence definition (≥1 / ≥2 / ≥3 subsequent symptomatic events). (A) UK Biobank (preceding page), (B) All of Us. Cell text shows the area under the ROC curve (AUC) value.

\newpage

#### Supplementary Figure 4: Grid Search Heatmap – Sensitivity

\begin{center}
\textbf{(A) UK Biobank}\\[0.4em]
\includegraphics[width=\textheight,height=0.86\textwidth,keepaspectratio]{UKB Recurrence paper results/grid_search_heatmap_sensitivity.pdf}
\end{center}

\newpage

\begin{center}
\textbf{(B) All of Us}\\[0.4em]
\includegraphics[width=\textheight,height=0.86\textwidth,keepaspectratio]{AoU Recurrence paper results/grid_search_heatmap_sensitivity_aou.pdf}
\end{center}

**Supplementary Figure 4:** Heatmap of sensitivity for European Association of Urology (EAU) risk stratification across starting stone event (rows) and inter-event-time cutoff (columns: Baseline / ≤6 / ≤12 / ≤18 / ≤24 months), faceted by recurrence definition (≥1 / ≥2 / ≥3 subsequent symptomatic events). (A) UK Biobank (preceding page), (B) All of Us. Cell text shows the sensitivity value.

\newpage

#### Supplementary Figure 5: Grid Search Heatmap – Specificity

\begin{center}
\textbf{(A) UK Biobank}\\[0.4em]
\includegraphics[width=\textheight,height=0.86\textwidth,keepaspectratio]{UKB Recurrence paper results/grid_search_heatmap_specificity.pdf}
\end{center}

\newpage

\begin{center}
\textbf{(B) All of Us}\\[0.4em]
\includegraphics[width=\textheight,height=0.86\textwidth,keepaspectratio]{AoU Recurrence paper results/grid_search_heatmap_specificity_aou.pdf}
\end{center}

**Supplementary Figure 5:** Heatmap of specificity for European Association of Urology (EAU) risk stratification across starting stone event (rows) and inter-event-time cutoff (columns: Baseline / ≤6 / ≤12 / ≤18 / ≤24 months), faceted by recurrence definition (≥1 / ≥2 / ≥3 subsequent symptomatic events). (A) UK Biobank (preceding page), (B) All of Us. Cell text shows the specificity value.

\newpage

#### Supplementary Figure 6: Grid Search Heatmap – PPV

\begin{center}
\textbf{(A) UK Biobank}\\[0.4em]
\includegraphics[width=\textheight,height=0.86\textwidth,keepaspectratio]{UKB Recurrence paper results/grid_search_heatmap_ppv.pdf}
\end{center}

\newpage

\begin{center}
\textbf{(B) All of Us}\\[0.4em]
\includegraphics[width=\textheight,height=0.86\textwidth,keepaspectratio]{AoU Recurrence paper results/grid_search_heatmap_ppv_aou.pdf}
\end{center}

**Supplementary Figure 6:** Heatmap of positive predictive value (PPV) for European Association of Urology (EAU) risk stratification across starting stone event (rows) and inter-event-time cutoff (columns: Baseline / ≤6 / ≤12 / ≤18 / ≤24 months), faceted by recurrence definition (≥1 / ≥2 / ≥3 subsequent symptomatic events). (A) UK Biobank (preceding page), (B) All of Us. Cell text shows the positive predictive value (PPV) value.

\newpage

#### Supplementary Figure 7: Grid Search Heatmap – NPV

\begin{center}
\textbf{(A) UK Biobank}\\[0.4em]
\includegraphics[width=\textheight,height=0.86\textwidth,keepaspectratio]{UKB Recurrence paper results/grid_search_heatmap_npv.pdf}
\end{center}

\newpage

\begin{center}
\textbf{(B) All of Us}\\[0.4em]
\includegraphics[width=\textheight,height=0.86\textwidth,keepaspectratio]{AoU Recurrence paper results/grid_search_heatmap_npv_aou.pdf}
\end{center}

**Supplementary Figure 7:** Heatmap of negative predictive value (NPV) for European Association of Urology (EAU) risk stratification across starting stone event (rows) and inter-event-time cutoff (columns: Baseline / ≤6 / ≤12 / ≤18 / ≤24 months), faceted by recurrence definition (≥1 / ≥2 / ≥3 subsequent symptomatic events). (A) UK Biobank (preceding page), (B) All of Us. Cell text shows the negative predictive value (NPV) value.

\newpage

#### Supplementary Figure 8: Grid Search Heatmap – 5-Year Recurrence Likelihood (Risk Status × Cohort)

\begin{center}
\begin{minipage}{0.49\textheight}\centering
\textbf{(A) UK Biobank – High Risk}\\[0.3em]
\includegraphics[width=\linewidth,height=0.40\textwidth,keepaspectratio]{UKB Recurrence paper results/grid_search_heatmap_likelihood_high_risk.pdf}
\end{minipage}\hfill
\begin{minipage}{0.49\textheight}\centering
\textbf{(B) All of Us – High Risk}\\[0.3em]
\includegraphics[width=\linewidth,height=0.40\textwidth,keepaspectratio]{AoU Recurrence paper results/grid_search_heatmap_likelihood_high_risk_aou.pdf}
\end{minipage}

\vspace{0.6em}

\begin{minipage}{0.49\textheight}\centering
\textbf{(C) UK Biobank – Low Risk}\\[0.3em]
\includegraphics[width=\linewidth,height=0.40\textwidth,keepaspectratio]{UKB Recurrence paper results/grid_search_heatmap_likelihood_low_risk.pdf}
\end{minipage}\hfill
\begin{minipage}{0.49\textheight}\centering
\textbf{(D) All of Us – Low Risk}\\[0.3em]
\includegraphics[width=\linewidth,height=0.40\textwidth,keepaspectratio]{AoU Recurrence paper results/grid_search_heatmap_likelihood_low_risk_aou.pdf}
\end{minipage}
\end{center}

**Supplementary Figure 8:** Heatmaps of 5-year cumulative recurrence likelihood (%) across starting stone event (rows) and inter-event-time cutoff (columns), faceted by recurrence definition (≥1 / ≥2 / ≥3 subsequent events), arranged as a 2×2 grid of risk status × cohort. Top row = high-risk participants: (A) UK Biobank, (B) All of Us. Bottom row = low-risk participants: (C) UK Biobank, (D) All of Us.

\elandscape

\newpage

## Recurrent Disease Definition

### Stratified by Time to Next Stone Event

#### Supplementary Figure 9: Time to Next Stone Event by Transition Type

\begin{center}
\begin{minipage}{0.48\textwidth}
\centering
\textbf{(A) UK Biobank}\\[0.5em]
\includegraphics[width=\textwidth]{UKB Recurrence paper results/recurrent_disease_km_by_transition.pdf}
\end{minipage}
\hfill
\begin{minipage}{0.48\textwidth}
\centering
\textbf{(B) All of Us}\\[0.5em]
\includegraphics[width=\textwidth]{AoU Recurrence paper results/recurrent_disease_km_by_transition_aou.pdf}
\end{minipage}
\end{center}

**Supplementary Figure 9:** Kaplan-Meier curves of time to the next symptomatic stone event, stratified by transition number (1→2, 2→3, 3→4, 4→5). (A) UK Biobank, (B) All of Us.

\newpage

### Heatmaps - Current Event to Next Event

\blandscape

#### Supplementary Figure 10: Heatmap – AUC, Baseline vs Baseline + Recurrent Disease

\begin{center}
\begin{minipage}{0.49\textheight}
\centering
\textbf{(A) UK Biobank}\\[0.5em]
\includegraphics[width=\linewidth]{UKB Recurrence paper results/recurrent_disease_heatmap_auc.pdf}
\end{minipage}
\hfill
\begin{minipage}{0.49\textheight}
\centering
\textbf{(B) All of Us}\\[0.5em]
\includegraphics[width=\linewidth]{AoU Recurrence paper results/recurrent_disease_heatmap_auc_aou.pdf}
\end{minipage}
\end{center}

**Supplementary Figure 10:** Heatmap of area under the receiver-operating-characteristic (ROC) curve (AUC) comparing the European Association of Urology (EAU)-only classifier with the EAU + recurrent-disease classifier across stone-event transitions. (A) UK Biobank, (B) All of Us. Cell text shows the area under the ROC curve (AUC) value.

\newpage

#### Supplementary Figure 11: Heatmap – Sensitivity, Baseline vs Baseline + Recurrent Disease

\begin{center}
\begin{minipage}{0.49\textheight}
\centering
\textbf{(A) UK Biobank}\\[0.5em]
\includegraphics[width=\linewidth]{UKB Recurrence paper results/recurrent_disease_heatmap_sensitivity.pdf}
\end{minipage}
\hfill
\begin{minipage}{0.49\textheight}
\centering
\textbf{(B) All of Us}\\[0.5em]
\includegraphics[width=\linewidth]{AoU Recurrence paper results/recurrent_disease_heatmap_sensitivity_aou.pdf}
\end{minipage}
\end{center}

**Supplementary Figure 11:** Heatmap of sensitivity comparing the European Association of Urology (EAU)-only classifier with the EAU + recurrent-disease classifier across stone-event transitions. (A) UK Biobank, (B) All of Us. Cell text shows the sensitivity value.

\newpage

#### Supplementary Figure 12: Heatmap – Specificity, Baseline vs Baseline + Recurrent Disease

\begin{center}
\begin{minipage}{0.49\textheight}
\centering
\textbf{(A) UK Biobank}\\[0.5em]
\includegraphics[width=\linewidth]{UKB Recurrence paper results/recurrent_disease_heatmap_specificity.pdf}
\end{minipage}
\hfill
\begin{minipage}{0.49\textheight}
\centering
\textbf{(B) All of Us}\\[0.5em]
\includegraphics[width=\linewidth]{AoU Recurrence paper results/recurrent_disease_heatmap_specificity_aou.pdf}
\end{minipage}
\end{center}

**Supplementary Figure 12:** Heatmap of specificity comparing the European Association of Urology (EAU)-only classifier with the EAU + recurrent-disease classifier across stone-event transitions. (A) UK Biobank, (B) All of Us. Cell text shows the specificity value.

\newpage

#### Supplementary Figure 13: Heatmap – PPV, Baseline vs Baseline + Recurrent Disease

\begin{center}
\begin{minipage}{0.49\textheight}
\centering
\textbf{(A) UK Biobank}\\[0.5em]
\includegraphics[width=\linewidth]{UKB Recurrence paper results/recurrent_disease_heatmap_ppv.pdf}
\end{minipage}
\hfill
\begin{minipage}{0.49\textheight}
\centering
\textbf{(B) All of Us}\\[0.5em]
\includegraphics[width=\linewidth]{AoU Recurrence paper results/recurrent_disease_heatmap_ppv_aou.pdf}
\end{minipage}
\end{center}

**Supplementary Figure 13:** Heatmap of positive predictive value (PPV) comparing the European Association of Urology (EAU)-only classifier with the EAU + recurrent-disease classifier across stone-event transitions. (A) UK Biobank, (B) All of Us. Cell text shows the positive predictive value (PPV) value.

\newpage

#### Supplementary Figure 14: Heatmap – NPV, Baseline vs Baseline + Recurrent Disease

\begin{center}
\begin{minipage}{0.49\textheight}
\centering
\textbf{(A) UK Biobank}\\[0.5em]
\includegraphics[width=\linewidth]{UKB Recurrence paper results/recurrent_disease_heatmap_npv.pdf}
\end{minipage}
\hfill
\begin{minipage}{0.49\textheight}
\centering
\textbf{(B) All of Us}\\[0.5em]
\includegraphics[width=\linewidth]{AoU Recurrence paper results/recurrent_disease_heatmap_npv_aou.pdf}
\end{minipage}
\end{center}

**Supplementary Figure 14:** Heatmap of negative predictive value (NPV) comparing the European Association of Urology (EAU)-only classifier with the EAU + recurrent-disease classifier across stone-event transitions. (A) UK Biobank, (B) All of Us. Cell text shows the negative predictive value (NPV) value.

\elandscape

\newpage

### Number of Prior Events + Time Gaps - KM

#### Supplementary Figure 15: Three-Group Risk — First Event vs Recurrent (Long Gap) vs Recurrent (Short Gap)

Three-group KMs at each inter-event-gap cutoff (rows = 12 / 18 / 24 month gap definitions). (A) = UK Biobank, (B) = All of Us in each row.

\begin{center}
\begin{minipage}{0.48\textwidth}
\centering
\textbf{(A) UK Biobank — 12-month gap}\\[0.3em]
\includegraphics[width=\textwidth]{UKB Recurrence paper results/recurrent_disease_km_three_group_12mo.pdf}
\end{minipage}
\hfill
\begin{minipage}{0.48\textwidth}
\centering
\textbf{(B) All of Us — 12-month gap}\\[0.3em]
\includegraphics[width=\textwidth]{AoU Recurrence paper results/recurrent_disease_km_three_group_12mo_aou.pdf}
\end{minipage}

\vspace{0.5em}

\begin{minipage}{0.48\textwidth}
\centering
\textbf{(A) UK Biobank — 18-month gap}\\[0.3em]
\includegraphics[width=\textwidth]{UKB Recurrence paper results/recurrent_disease_km_three_group_18mo.pdf}
\end{minipage}
\hfill
\begin{minipage}{0.48\textwidth}
\centering
\textbf{(B) All of Us — 18-month gap}\\[0.3em]
\includegraphics[width=\textwidth]{AoU Recurrence paper results/recurrent_disease_km_three_group_18mo_aou.pdf}
\end{minipage}

\vspace{0.5em}

\begin{minipage}{0.48\textwidth}
\centering
\textbf{(A) UK Biobank — 24-month gap}\\[0.3em]
\includegraphics[width=\textwidth]{UKB Recurrence paper results/recurrent_disease_km_three_group_24mo.pdf}
\end{minipage}
\hfill
\begin{minipage}{0.48\textwidth}
\centering
\textbf{(B) All of Us — 24-month gap}\\[0.3em]
\includegraphics[width=\textwidth]{AoU Recurrence paper results/recurrent_disease_km_three_group_24mo_aou.pdf}
\end{minipage}

\vspace{0.5em}

\end{center}

**Supplementary Figure 15:** Kaplan-Meier event-free survival for a three-group stratification — 1 event, ≥2 events with a long inter-event gap, and ≥2 events with a short inter-event gap — at inter-event-gap cutoffs of 12 (top row), 18 (middle row) and 24 (bottom row) months. (A) UK Biobank and (B) All of Us in each row.

\newpage

#### Supplementary Figure 16: Pooled Transitions — EAU Risk Only vs Combined EAU + Recurrent Disease

Pooled across all transitions. Top row: EAU risk only. Bottom row: combined classifier (EAU OR ≥2 prior events with ≤12-month inter-event gap). (A) = UK Biobank, (B) = All of Us.

\begin{center}
\begin{minipage}{0.48\textwidth}
\centering
\textbf{(A) UK Biobank — EAU risk only}\\[0.3em]
\includegraphics[width=\textwidth]{UKB Recurrence paper results/recurrent_disease_km_eau_only_pooled.pdf}
\end{minipage}
\hfill
\begin{minipage}{0.48\textwidth}
\centering
\textbf{(B) All of Us — EAU risk only}\\[0.3em]
\includegraphics[width=\textwidth]{AoU Recurrence paper results/recurrent_disease_km_eau_only_pooled_aou.pdf}
\end{minipage}

\vspace{0.5em}

\begin{minipage}{0.48\textwidth}
\centering
\textbf{(A) UK Biobank — EAU + recurrent disease}\\[0.3em]
\includegraphics[width=\textwidth]{UKB Recurrence paper results/recurrent_disease_km_combined_eau_recurrent.pdf}
\end{minipage}
\hfill
\begin{minipage}{0.48\textwidth}
\centering
\textbf{(B) All of Us — EAU + recurrent disease}\\[0.3em]
\includegraphics[width=\textwidth]{AoU Recurrence paper results/recurrent_disease_km_combined_eau_recurrent_aou.pdf}
\end{minipage}

\vspace{0.5em}

\end{center}

**Supplementary Figure 16:** Kaplan-Meier event-free survival pooled across all transitions, comparing European Association of Urology (EAU) risk stratification alone (top row) with a combined classifier (EAU high-risk OR ≥2 prior events with a ≤12-month inter-event gap; bottom row). (A) UK Biobank, (B) All of Us.

\newpage

#### Supplementary Figure 17: Decision Curve Analysis on the entire transitions_long dataset

\begin{center}
\begin{minipage}{0.48\textwidth}
\centering
\textbf{(A) UK Biobank}\\[0.5em]
\includegraphics[width=\textwidth]{UKB Recurrence paper results/recurrent_disease_whole_dataset_dca.pdf}
\end{minipage}
\hfill
\begin{minipage}{0.48\textwidth}
\centering
\textbf{(B) All of Us}\\[0.5em]
\includegraphics[width=\textwidth]{AoU Recurrence paper results/recurrent_disease_whole_dataset_dca_aou.pdf}
\end{minipage}
\end{center}

**Supplementary Figure 17:** Decision curve analysis (DCA) on the same whole-dataset sample used in main-text Figure 2 — every participant contributes one row per transition they reach (1→2, 2→3, 3→4, 4→5), with European Association of Urology (EAU) risk re-ascertained at each transition's starting event. Each panel overlays five classifiers — *Baseline*, *EAU + ≥2 events*, *EAU + ≥3 events*, *EAU + ≥4 events*, and *≥2 events (no EAU)* (the same event-count-only classifier shown in main-text Figure 3 Panel C, included here to let the reader see what EAU stratification adds on top of the pure event-count rule) — alongside the standard "Follow-up all" / "Follow-up none" reference lines. Net Benefit is plotted against threshold probability. (A) UK Biobank, (B) All of Us. DCA is reported per cohort because Net Benefit depends on cohort-specific outcome prevalence and is not amenable to a simple meta-analytic pool.

\newpage

### Summary Plots
#### Supplementary Figure 18: Sensitivity-analysis 5-year recurrence likelihood heatmap

```{r supfig56-heatmap-likelihood, fig.width=14, fig.height=9, out.width="100%"}
# Sensitivity-analysis heatmap — same visual idiom as main-text Figure 3
# (theme_minimal, traffic-light gradient, Biobank rows including a
# Meta-analysis row, strip_themed) but extended over the full grid of
# starting-event × recurrence-definition × risk-group combinations.

ukb <- read.csv("UKB Recurrence paper results/prognostic_accuracy_grid_search_results.csv")
aou <- read.csv("AoU Recurrence paper results/prognostic_accuracy_grid_search_results_aou.csv")
aou <- aou[!duplicated(aou[, c("Starting_Point","Time_Cutoff_Months","Recurrence_Definition")]), ]

# The CSVs have multiple rows per (Starting_Point, Recurrence_Definition) —
# one row per Time_Cutoff_Months grid point, PLUS a no-cutoff baseline row
# (Time_Cutoff_Months == NA) for the non-index events (used by Figure 1's
# "No Short time" comparator). The heatmap groups by
# event × risk-group × recurrence-def, so we must keep EXACTLY ONE row per
# cell or the labels overlap. Pick a single representative cutoff:
#   • Index Date    → the NA row (no inter-event cutoff applies)
#   • all others    → the 12-month row ONLY (drop their NA baseline row, which
#                     would otherwise stack a second label in the same cell)
keep_one <- function(dat) {
  dat[(dat$Starting_Point == "Index Date" & is.na(dat$Time_Cutoff_Months)) |
      (dat$Starting_Point != "Index Date" & dat$Time_Cutoff_Months %in% 12), ]
}
ukb <- keep_one(ukb)
aou <- keep_one(aou)

event_map <- c("Index Date"   = "First Stone Event",
               "Second Event" = "Second Stone Event",
               "Third Event"  = "Third Stone Event",
               "Fourth Event" = "Fourth Stone Event")
event_order <- c("First Stone Event","Second Stone Event","Third Stone Event","Fourth Stone Event")

make_heatmap_df <- function(dat, biobank_name) {
  dat$event_label <- event_map[dat$Starting_Point]
  dat$Biobank <- biobank_name
  high <- data.frame(
    event_label = dat$event_label,
    Recurrence_Definition = dat$Recurrence_Definition,
    Biobank    = dat$Biobank,
    risk_group = "High Risk",
    pct = as.numeric(dat$Likelihood_Recurrence_High_Risk_pct),
    lo  = as.numeric(dat$Likelihood_Recurrence_High_Risk_lo),
    hi  = as.numeric(dat$Likelihood_Recurrence_High_Risk_hi),
    stringsAsFactors = FALSE
  )
  low <- data.frame(
    event_label = dat$event_label,
    Recurrence_Definition = dat$Recurrence_Definition,
    Biobank    = dat$Biobank,
    risk_group = "Low Risk",
    pct = as.numeric(dat$Likelihood_Recurrence_Low_Risk_pct),
    lo  = as.numeric(dat$Likelihood_Recurrence_Low_Risk_lo),
    hi  = as.numeric(dat$Likelihood_Recurrence_Low_Risk_hi),
    stringsAsFactors = FALSE
  )
  rbind(high, low)
}

df <- rbind(make_heatmap_df(ukb, "UKB"), make_heatmap_df(aou, "AoU"))
df$event_label <- factor(df$event_label, levels = rev(event_order))
df$Biobank    <- factor(df$Biobank, levels = c("UKB","AoU"))
df$risk_group <- factor(df$risk_group, levels = c("Low Risk","High Risk"))

rec_labels <- c("≥1 subsequent stone events" = "≥ 1 Subsequent Stone Events",
                "≥2 subsequent stone events" = "≥ 2 Subsequent Stone Events",
                "≥3 subsequent stone events" = "≥ 3 Subsequent Stone Events")
df$rec_facet <- rec_labels[df$Recurrence_Definition]
df$rec_facet <- factor(df$rec_facet, levels = rec_labels)

df$label_text <- paste0(
  sprintf("%.1f%%", df$pct), "\n(",
  sprintf("%.1f", df$lo), "–", sprintf("%.1f", df$hi), "%)"
)

df_scaled <- df %>%
  group_by(Biobank) %>%
  mutate(pct_scaled = scales::rescale(pct, to = c(0, 100))) %>%
  ungroup()

# DerSimonian-Laird random-effects meta-analysis on the LOGIT scale (matches Figure 3)
re_meta_logit <- function(theta, vi) {
  theta <- unname(theta); vi <- unname(vi)
  k <- length(theta)
  if (k < 1) return(c(theta = NA_real_, se = NA_real_))
  if (k == 1) return(c(theta = theta[1], se = sqrt(vi[1])))
  w_fe <- 1 / vi
  fe_pe <- sum(w_fe * theta) / sum(w_fe)
  Q  <- sum(w_fe * (theta - fe_pe)^2)
  C  <- sum(w_fe) - sum(w_fe^2) / sum(w_fe)
  tau2 <- max(0, (Q - (k - 1)) / C)
  w_re <- 1 / (vi + tau2)
  pe   <- sum(w_re * theta) / sum(w_re)
  pse  <- sqrt(1 / sum(w_re))
  c(theta = pe, se = pse)
}

meta_df <- df %>%
  mutate(p = pct / 100, lo_p = lo / 100, hi_p = hi / 100,
         theta    = log(p    / (1 - p)),
         theta_lo = log(lo_p / (1 - lo_p)),
         theta_hi = log(hi_p / (1 - hi_p)),
         se = (theta_hi - theta_lo) / (2 * 1.96),
         vi = se^2) %>%
  group_by(event_label, risk_group, rec_facet) %>%
  summarise(pe = list(re_meta_logit(theta, vi)), .groups = "drop") %>%
  mutate(theta_meta = sapply(pe, `[`, "theta"),
         se_meta    = sapply(pe, `[`, "se"),
         p_meta     = 1 / (1 + exp(-theta_meta)),
         lo_meta    = 1 / (1 + exp(-(theta_meta - 1.96 * se_meta))),
         hi_meta    = 1 / (1 + exp(-(theta_meta + 1.96 * se_meta)))) %>%
  dplyr::select(-pe) %>%
  mutate(
    Biobank    = factor("Meta-analysis", levels = c("UKB","AoU","Meta-analysis")),
    pct        = p_meta  * 100,
    lo         = lo_meta * 100,
    hi         = hi_meta * 100,
    pct_scaled = scales::rescale(pct, to = c(0, 100)),
    label_text = paste0(
      sprintf("%.1f%%", pct), "\n(",
      sprintf("%.1f", lo), "–", sprintf("%.1f", hi), "%)"
    )
  ) %>%
  dplyr::select(event_label, risk_group, rec_facet, Biobank,
                pct, lo, hi, pct_scaled, label_text)

df_plot <- bind_rows(
  df_scaled %>% dplyr::select(event_label, risk_group, rec_facet, Biobank,
                               pct, lo, hi, pct_scaled, label_text),
  meta_df
)
df_plot$Biobank <- factor(df_plot$Biobank, levels = c("UKB","AoU","Meta-analysis"))

# --- Plot (same idiom as Figure 3) ---
ggplot(df_plot, aes(x = risk_group, y = event_label, fill = pct_scaled)) +
  geom_tile(colour = "black", linewidth = 0.4) +
  geom_text(aes(label = label_text), size = 3, lineheight = 0.85, colour = "black") +
  facet_grid2(Biobank ~ rec_facet,
              strip = strip_themed(background_y = elem_list_rect(
                fill = c("#FFFFFF","#FFFFFF","#D6EAF8"),
                colour = "black", linewidth = 0.6))) +
  scale_x_discrete(position = "top") +
  scale_fill_gradient2(low = "#A6D96A", mid = "#FFFFF0", high = "#E34A33",
                       midpoint = 50, limits = c(0, 100),
                       name = "Relative likelihood\nwithin Each Biobank (%)") +
  labs(x = NULL, y = NULL,
       title = "5-Year Cumulative Recurrence Likelihood — Sensitivity Analysis",
       subtitle = "Same idiom as Figure 3, extended over the full grid of recurrence definitions and event-count strata.") +
  theme_minimal(base_size = 11) +
  theme(
    axis.text.x   = element_text(face = "bold", colour = "black", size = 11),
    axis.text.y   = element_text(face = "bold", colour = "black", size = 9),
    axis.ticks.x  = element_line(colour = "black"),
    axis.line.x   = element_line(colour = "black"),
    panel.spacing = unit(1.4, "lines"),
    strip.text.x  = element_text(face = "bold", size = 11),
    strip.text.y  = element_text(face = "bold", size = 11),
    plot.title    = element_text(face = "bold"),
    plot.subtitle = element_text(size = 9, colour = "grey30")
  )
```

**Supplementary Figure 18:** Sensitivity-analysis heatmap of 5-year cumulative recurrence likelihood, in the same visual idiom as main-text Figure 3. Rows = Biobank (UK Biobank (UKB) / All of Us (AoU) / DerSimonian-Laird random-effects meta-analysis on the logit scale); columns = recurrence definition (≥1, ≥2, ≥3 subsequent stone events). Within each panel, cells show the proportion of high-risk vs low-risk participants who recurred within 5 years, stratified by their starting stone event (1st / 2nd / 3rd / 4th). For non-index transitions a 12-month inter-event cutoff is used to define the high-risk-by-recent-recurrence component; for the index transition no inter-event cutoff applies. Cells are coloured by likelihood rescaled within each cohort (0–100); cell text shows the absolute percentage and 95% confidence interval (CI).

