---
title: "Clinical Utility of EAU Risk Stratification for 1st time stone formers"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    code_folding: show
---

# Libraries

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(forcats)
library(anytime)
library(pROC)
library(gt)
library(gtExtras)
library(grid)
library(gridExtra)
library(survminer)
library(survival)
library(MatchIt)
```

# Data Loading

## DoB data

```{r load-diet}
diet_data_participant <- read.csv("diet_data_updated__participant.csv",
                                  na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()
```

## Clinical coding data

### Read codes

```{r load-clinical}
recurrence_gp_data <- read.csv("gp_data_gp_clinical.csv",
                               na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

recurrence_data_hesin <- read.csv("data_hesin.csv", na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

recurrence_data_hesin_diag <- read.csv("data_hesin_diag.csv",
                                       na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

recurrence_data_hesin_critical <- read.csv("data_hesin_critical.csv",
                                           na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()
```

### OPCS

```{r}
recurrence_data_hesin_oper <- read.csv("data_hesin_oper.csv",
                                       na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()
```


### ICD codes

```{r load-icd}
icd10_upto196 <- read.csv("icd10_upto196_participant.csv",
                           na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

icd10_morethan196 <- read.csv("icd10_morethan196_participant.csv",
                               na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

icd10_dates2 <- cbind(icd10_upto196,
                      subset(icd10_morethan196, select = -participant_id)) %>%
  drop_na(diagnoses_icd10)

icd10_data_extra <- read.csv("icd10_extra_participant.csv",
                              na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names() %>%
  subset(select = -c(age_at_recruitment, diagnoses_icd10))

icd9_data <- read.csv("icd9_participant.csv",
                       na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()
```

# Data Processing

## Identify recurrence events

Creates: `time_to_first_recurrence1`, `overall_data_cut_off_5`, `overall_follow_up`

```{r identify-recurrence}
source("recurrence_identification_colic_to_colic_multiple_occurrences.R")
```

## Ascertain past medical history

Creates: `pmhx_cleaned` (including UTI flag)

```{r ascertain-pmhx}
source("pmhx_ascertainment_with_dates.R")
```

# Derived Variables

## Create time-to-recurrence dataset

```{r time-to-recurrence}
time_to_recurrence_2 <- time_to_first_recurrence1 %>%
  mutate(
    time_0 = first_date,
    recurrence = ifelse(pheno > 0, "rsf", "ssf"),
    time_to_recurrence_1 = time_diff_years
  )
```

## Create high-risk classification (with initial presentation)

```{r high-risk-classification}
high_risk <- time_to_recurrence_2 %>%
  subset(select = c(participant_id, recurrence, time_to_recurrence_1, initial_presentation)) %>%
  left_join(pmhx_cleaned, by = "participant_id") %>%
  left_join(diet_data_participant %>%
              mutate(dob = as.Date(paste("1", month_of_birth, year_of_birth, sep = " - "),
                                   format = "%d - %m - %Y")) %>%
              dplyr::select(participant_id, dob),
            by = "participant_id") %>%
  left_join(time_to_first_recurrence1 %>% dplyr::select(participant_id, date_of_first_code),
            by = "participant_id") %>%
  mutate(
    age_at_first_stone = (date_of_first_code - dob) / 365.25,
    high_risk = case_when(
      age_at_first_stone < 25 ~ "high_risk",
      (metabolic_disorder + hyperpth + transplant_immunosuppression + pkd + msk +
         bowel_surgery + ibd + malabsorption + sarcoidosis + spinal_injury + cf +
         pujo + metabolic_syndrome + horshoe_kidney + eating_disorder + ileal_conduit +
         single_kidney + vur + ureteric_stricture + metabolic_syndrome) > 1 ~ "high_risk",
      TRUE ~ "low_risk"
    )
  ) %>%
  dplyr::select(participant_id, initial_presentation, high_risk)
```

# Overall Recurrence Rates

## Kaplan Meier
```{r}
demographics_km1 <- time_to_recurrence_2 %>% subset(select = c(recurrence, time_to_recurrence_1)) %>% drop_na(recurrence) %>% drop_na(time_to_recurrence_1)
demographics_km1$recurrence <- ifelse(demographics_km1$recurrence == "rsf", 1, 0)
demographics_km1$recurrence <- as.integer(demographics_km1$recurrence)
km_fit <- surv_fit(Surv(time_to_recurrence_1, as.integer(recurrence)) ~ 1, data =
                     demographics_km1) 
ggsurvplot(km_fit,
           data = demographics_km1,
           risk.table = TRUE,
           surv.median.line = "hv",
           conf.int = TRUE,
           tables.theme = theme_cleantable(),
           break.time.by = 1,
           xlab = "Time (years)",
           xlim = c(0,10),
           title = "Time to First Recurrence",
           censor = FALSE)
```

## Yearly Cut-offs Recurrence Rates
```{r}
as_tibble(cbind(
  "Yearly Recurrence" =  c(2, 5, 10),
  "Recurrence Rates" = 1-round(summary(km_fit, times = c(2, 5, 10))$surv, digits = 2),
  "95% CI" = paste0(
    1 - round(summary(km_fit, times = c(2, 5, 10))$upper, digits = 2),
    "-",
    1- round(summary(km_fit, times = c(2, 5, 10))$lower, digits = 2)
  )
)) %>%
  gt() %>%
  gt_theme_espn()
```


# With vs Without UTI - Data Preparation

## Age at first stone

```{r age-first-stone}
age_at_first_stone_df_2 <- time_to_recurrence_2 %>%
  subset(select = c(participant_id, recurrence, time_to_recurrence_1)) %>%
  left_join(pmhx_cleaned, by = "participant_id") %>%
  left_join(diet_data_participant %>%
              mutate(dob = as.Date(paste("1", month_of_birth, year_of_birth, sep = " - "),
                                   format = "%d - %m - %Y")) %>%
              dplyr::select(participant_id, dob),
            by = "participant_id") %>%
  left_join(time_to_first_recurrence1 %>% dplyr::select(participant_id, date_of_first_code),
            by = "participant_id") %>%
  mutate(age_at_first_stone = (date_of_first_code - dob) / 365.25) %>%
  dplyr::select(participant_id, age_at_first_stone)
```

## Risk stratification without UTI

```{r risk-without-uti}
high_risk_without_uti <- time_to_first_recurrence1 %>%
  select(participant_id) %>%
  distinct(participant_id) %>%
  left_join(pmhx_cleaned, by = "participant_id") %>%
  dplyr::select(-uti) %>%
  mutate(across(c(metabolic_disorder, metabolic_syndrome, hyperpth, immunosuppression,
                  transplant_immunosuppression, pkd, msk,
                  bowel_surgery, ibd, malabsorption, sarcoidosis, spinal_injury,
                  cf, pujo, diverticulum, ureteric_stricture, vur, single_kidney,
                  ileal_conduit, eating_disorder, horshoe_kidney),
                ~replace_na(., 0))) %>%
  mutate(
    high_risk = if_else(
      (metabolic_disorder + metabolic_syndrome +
         hyperpth + immunosuppression + transplant_immunosuppression +
         pkd + msk + bowel_surgery + ibd + malabsorption +
         sarcoidosis + spinal_injury + cf + pujo + diverticulum + ureteric_stricture +
         vur + single_kidney + ileal_conduit + eating_disorder + horshoe_kidney) < 1,
      "low_risk",
      "high_risk")) %>%
  select(participant_id, high_risk) %>%
  left_join(age_at_first_stone_df_2 %>% dplyr::select(participant_id, age_at_first_stone),
            by = "participant_id") %>%
  mutate(high_risk = case_when(age_at_first_stone < 25 ~ "high_risk", TRUE ~ high_risk)) %>%
  group_by(participant_id) %>%
  summarise(high_risk = if_else(any(high_risk == "high_risk"), "high_risk", "low_risk"),
            .groups = "drop")

table(high_risk_without_uti$high_risk)
```

## Risk stratification with UTI

```{r risk-with-uti}
high_risk_with_uti <- time_to_first_recurrence1 %>%
  select(participant_id) %>%
  distinct(participant_id) %>%
  left_join(pmhx_cleaned, by = "participant_id") %>%
  mutate(across(c(metabolic_disorder, metabolic_syndrome, hyperpth, uti, immunosuppression,
                  transplant_immunosuppression, pkd, msk,
                  bowel_surgery, ibd, malabsorption, sarcoidosis, spinal_injury,
                  cf, pujo, diverticulum, ureteric_stricture, vur, single_kidney,
                  ileal_conduit, eating_disorder, horshoe_kidney),
                ~replace_na(., 0))) %>%
  mutate(
    high_risk = if_else(
      (metabolic_disorder + metabolic_syndrome + uti +
         hyperpth + immunosuppression + transplant_immunosuppression +
         pkd + msk + bowel_surgery + ibd + malabsorption +
         sarcoidosis + spinal_injury + cf + pujo + diverticulum + ureteric_stricture +
         vur + single_kidney + ileal_conduit + eating_disorder + horshoe_kidney) < 1,
      "low_risk",
      "high_risk")) %>%
  select(participant_id, high_risk) %>%
  left_join(age_at_first_stone_df_2 %>% dplyr::select(participant_id, age_at_first_stone),
            by = "participant_id") %>%
  mutate(high_risk = case_when(age_at_first_stone < 25 ~ "high_risk", TRUE ~ high_risk)) %>%
  group_by(participant_id) %>%
  summarise(high_risk = if_else(any(high_risk == "high_risk"), "high_risk", "low_risk"),
            .groups = "drop")

table(high_risk_with_uti$high_risk)
```

## Assemble base datasets

```{r assemble-datasets}
### Unmatched: Without UTI
base_data_without_uti <- overall_data_cut_off_5 %>%
  left_join(high_risk_without_uti, by = "participant_id") %>%
  left_join(high_risk %>% dplyr::select(participant_id, initial_presentation), by = "participant_id") %>%
  left_join(age_at_first_stone_df_2 %>% dplyr::select(participant_id, age_at_first_stone), by = "participant_id") %>%
  dplyr::select(participant_id, count_diff, first_date, last_date, high_risk, initial_presentation, age_at_first_stone) %>%
  mutate(recurrence = if_else(count_diff == 0, 0, 1), .keep = "all")

### Unmatched: With UTI
base_data_with_uti <- overall_data_cut_off_5 %>%
  left_join(high_risk_with_uti, by = "participant_id") %>%
  left_join(high_risk %>% dplyr::select(participant_id, initial_presentation), by = "participant_id") %>%
  left_join(age_at_first_stone_df_2 %>% dplyr::select(participant_id, age_at_first_stone), by = "participant_id") %>%
  dplyr::select(participant_id, count_diff, first_date, last_date, high_risk, initial_presentation, age_at_first_stone) %>%
  mutate(recurrence = if_else(count_diff == 0, 0, 1), .keep = "all")

### KM datasets
base_data_without_uti_for_km <- time_to_first_recurrence1 %>%
  left_join(high_risk_without_uti, by = "participant_id") %>%
  left_join(age_at_first_stone_df_2 %>% dplyr::select(participant_id, age_at_first_stone),
            by = "participant_id") %>%
  dplyr::select(participant_id, pheno, high_risk, initial_presentation, age_at_first_stone, time_diff_years) %>%
  mutate(recurrence = pheno,
         age_at_first_stone = as.numeric(age_at_first_stone),
         time_to_recurrence_1 = time_diff_years,
         .keep = "unused") %>%
  drop_na(time_to_recurrence_1)

base_data_with_uti_for_km <- time_to_first_recurrence1 %>%
  left_join(high_risk_with_uti, by = "participant_id") %>%
  left_join(age_at_first_stone_df_2 %>% dplyr::select(participant_id, age_at_first_stone),
            by = "participant_id") %>%
  dplyr::select(participant_id, pheno, high_risk, initial_presentation, age_at_first_stone, time_diff_years) %>%
  mutate(recurrence = pheno,
         age_at_first_stone = as.numeric(age_at_first_stone),
         time_to_recurrence_1 = time_diff_years,
         .keep = "unused") %>%
  drop_na(time_to_recurrence_1)
```

## Tabulate data 

### Without UTI
```{r}
base_data_without_uti_for_km_summary <- base_data_without_uti_for_km %>%
    left_join(pmhx_cleaned, by = "participant_id") %>%
  dplyr::select(-c(time_to_recurrence_1, participant_id)) %>%
  mutate(
    early_onset = case_when(
      age_at_first_stone <25 ~ "Yes",
      TRUE ~ "No"
    ),
    .keep = "all"
  ) %>%
  tbl_summary(statistic = list(
    all_continuous() ~ "{mean} ± {sd}",
    all_categorical() ~
      "{n} ({p}%)"
  ))

base_data_without_uti_for_km_summary
```


### With UTI
```{r}
base_data_with_uti_for_km_summary <- base_data_with_uti_for_km %>%
  dplyr::select(high_risk) %>%
  tbl_summary(statistic = list(
    all_continuous() ~ "{mean} ± {sd}",
    all_categorical() ~
      "{n} ({p}%)"
  ))

base_data_with_uti_for_km_summary
```


# Analysis Parameters and Matched Datasets

```{r analysis-params}
thresholds <- c(1, 2, 3)
labels <- c("0 vs \u22651 events", "0 vs \u22652 events", "0 vs \u22653 events")
colors <- c("#1b9e77", "#d95f02", "#7570b3")
```

## Propensity-score matched datasets

```{r matched-datasets}
### Matched: Without UTI
base_data_match_without_uti <- base_data_without_uti %>%
  mutate(
    high_risk_binary = if_else(high_risk == "high_risk", 1L, 0L),
    age_at_first_stone = as.numeric(age_at_first_stone),
    initial_presentation = as.factor(initial_presentation)
  ) %>%
  drop_na(high_risk_binary, age_at_first_stone, initial_presentation)

m <- matchit(high_risk_binary ~ age_at_first_stone + initial_presentation,
             data = base_data_match_without_uti,
             method = "nearest")
base_data_match_without_uti <- match.data(m)

### Matched: With UTI
base_data_match_with_uti <- base_data_with_uti %>%
  mutate(
    high_risk_binary = if_else(high_risk == "high_risk", 1L, 0L),
    age_at_first_stone = as.numeric(age_at_first_stone),
    initial_presentation = as.factor(initial_presentation)
  ) %>%
  drop_na(high_risk_binary, age_at_first_stone, initial_presentation)

m <- matchit(high_risk_binary ~ age_at_first_stone + initial_presentation,
             data = base_data_match_with_uti,
             method = "nearest")
base_data_match_with_uti <- match.data(m)
```

# Helper Functions

```{r helper-functions}
prep_roc <- function(base_data, thresh) {
  base_data %>%
    mutate(
      actual = case_when(
        count_diff >= thresh ~ 1,
        count_diff == 0 ~ 0,
        TRUE ~ NA_integer_
      ),
      predicted = if_else(high_risk == "high_risk", 1, 0)
    ) %>%
    drop_na()
}

extract_metrics <- function(roc_obj, dataset_name, label, p_text) {
  auc_val <- as.numeric(auc(roc_obj))
  auc_ci  <- ci.auc(roc_obj)

  coords_best <- coords(roc_obj, "best", ret = c("sensitivity", "specificity"),
                        best.method = "youden")

  sens_ci <- ci.se(roc_obj, specificities = coords_best$specificity)
  spec_ci <- ci.sp(roc_obj, sensitivities = coords_best$sensitivity)

  data.frame(
    Dataset = dataset_name,
    Comparison = label,
    AUC_CI = sprintf("%.2f (%.2f\u2013%.2f)", auc_val, auc_ci[1], auc_ci[3]),
    Sensitivity = sprintf("%.2f (%.2f\u2013%.2f)",
                          coords_best$sensitivity, sens_ci[, 1], sens_ci[, 3]),
    Specificity = sprintf("%.2f (%.2f\u2013%.2f)",
                          coords_best$specificity, spec_ci[, 1], spec_ci[, 3]),
    DeLong_p = p_text
  )
}

generate_roc_plot <- function(base_data, plot_title) {
  roc_list <- list()
  auc_table_df <- data.frame(Comparison = character(), AUC_CI = character())
  ci_combined_df <- data.frame()

  for (i in seq_along(thresholds)) {
    thresh <- thresholds[i]
    label <- labels[i]

    roc_data <- prep_roc(base_data, thresh)
    roc_obj <- roc(roc_data$actual, roc_data$predicted, quiet = TRUE)

    roc_list[[i]] <- list(roc_obj = roc_obj, color = colors[i], label = label)

    auc_val <- as.numeric(auc(roc_obj))
    auc_ci  <- ci.auc(roc_obj)

    auc_table_df <- rbind(
      auc_table_df,
      data.frame(
        Comparison = label,
        AUC_CI = sprintf("%.2f (%.2f\u2013%.2f)", auc_val, auc_ci[1], auc_ci[3])
      )
    )

    ci_se <- ci.se(roc_obj, specificities = seq(0, 1, length.out = 100))
    ci_combined_df <- rbind(ci_combined_df, data.frame(
      fpr = 1 - as.numeric(rownames(ci_se)),
      tpr_lower = ci_se[, 1],
      tpr_upper = ci_se[, 3],
      Comparison = label
    ))
  }

  roc_combined_df <- do.call(rbind, lapply(seq_along(roc_list), function(i) {
    roc_obj <- roc_list[[i]]$roc_obj
    data.frame(
      fpr = 1 - roc_obj$specificities,
      tpr = roc_obj$sensitivities,
      Comparison = roc_list[[i]]$label
    )
  }))

  auc_table <- tableGrob(auc_table_df, rows = NULL, theme = ttheme_minimal(base_size = 9))
  auc_table_boxed <- grobTree(
    rectGrob(gp = gpar(col = "black", fill = "white", lwd = 1)),
    auc_table
  )

  ggplot() +
    geom_ribbon(
      data = ci_combined_df,
      aes(x = fpr, ymin = tpr_lower, ymax = tpr_upper, fill = Comparison),
      alpha = 0.2
    ) +
    geom_line(
      data = roc_combined_df,
      aes(x = fpr, y = tpr, color = Comparison),
      linewidth = 1
    ) +
    geom_abline(linetype = "dashed", alpha = 0.6) +
    labs(x = "False Positive Rate", y = "True Positive Rate", title = plot_title) +
    scale_color_manual(values = colors) +
    scale_fill_manual(values = colors) +
    coord_equal() +
    theme_minimal(base_size = 12) +
    annotation_custom(
      grob = auc_table_boxed,
      xmin = 0.55, xmax = 1,
      ymin = 0.05, ymax = 0.3
    ) + theme_bw()
}

generate_faceted_roc_plot <- function(base_data, plot_title) {
  presentations <- unique(base_data$initial_presentation)

  roc_combined_df <- data.frame()
  ci_combined_df  <- data.frame()
  auc_table_df    <- data.frame()

  for (pres in presentations) {
    pres_data <- base_data %>% filter(initial_presentation == pres)

    for (i in seq_along(thresholds)) {
      thresh <- thresholds[i]
      label  <- labels[i]

      roc_data <- pres_data %>%
        mutate(
          actual = case_when(
            count_diff >= thresh ~ 1,
            count_diff == 0      ~ 0,
            TRUE                 ~ NA_integer_
          ),
          predicted = if_else(high_risk == "high_risk", 1, 0)
        ) %>%
        drop_na()

      if (nrow(roc_data) < 10 || length(unique(roc_data$actual)) < 2) next

      roc_obj <- roc(roc_data$actual, roc_data$predicted, quiet = TRUE)

      roc_combined_df <- rbind(roc_combined_df, data.frame(
        fpr = 1 - roc_obj$specificities,
        tpr = roc_obj$sensitivities,
        Comparison = label,
        initial_presentation = pres
      ))

      ci_se <- ci.se(roc_obj, specificities = seq(0, 1, length.out = 100))
      ci_combined_df <- rbind(ci_combined_df, data.frame(
        fpr = 1 - as.numeric(rownames(ci_se)),
        tpr_lower = ci_se[, 1],
        tpr_upper = ci_se[, 3],
        Comparison = label,
        initial_presentation = pres
      ))

      auc_val <- as.numeric(auc(roc_obj))
      auc_ci  <- ci.auc(roc_obj)
      auc_table_df <- rbind(auc_table_df, data.frame(
        initial_presentation = pres,
        Comparison = label,
        AUC = sprintf("%.2f (%.2f\u2013%.2f)", auc_val, auc_ci[1], auc_ci[3])
      ))
    }
  }

  ggplot() +
    geom_ribbon(
      data = ci_combined_df,
      aes(x = fpr, ymin = tpr_lower, ymax = tpr_upper, fill = Comparison),
      alpha = 0.2
    ) +
    geom_line(
      data = roc_combined_df,
      aes(x = fpr, y = tpr, color = Comparison),
      linewidth = 1
    ) +
    geom_abline(linetype = "dashed", alpha = 0.6) +
    geom_label(
      data = auc_table_df,
      aes(label = paste0(Comparison, ": ", AUC), color = Comparison),
      x = 0.95, y = seq(0.25, 0.05, length.out = length(labels))[
        match(auc_table_df$Comparison, labels)
      ],
      hjust = 1, size = 2.8, fill = "white", label.size = 0.3, show.legend = FALSE
    ) +
    scale_color_manual(values = setNames(colors, labels)) +
    scale_fill_manual(values = setNames(colors, labels)) +
    facet_wrap(~ initial_presentation) +
    coord_equal() +
    labs(x = "False Positive Rate", y = "True Positive Rate",
         title = plot_title, color = NULL, fill = NULL) +
    theme_bw(base_size = 11) +
    theme(legend.position = "bottom", strip.text = element_text(face = "bold"))
}
```

# DeLong's Tests - Summary Tables

## Unmatched: Without UTI vs With UTI

```{r delong-unmatched}
results_unmatched_df <- data.frame(
  Dataset = character(), Comparison = character(),
  AUC_CI = character(), Sensitivity = character(),
  Specificity = character(), DeLong_p = character(),
  stringsAsFactors = FALSE
)

for (i in seq_along(thresholds)) {
  thresh <- thresholds[i]

  roc_with    <- prep_roc(base_data_with_uti, thresh)
  roc_without <- prep_roc(base_data_without_uti, thresh)

  roc_obj1 <- roc(roc_with$actual, roc_with$predicted, quiet = TRUE)
  roc_obj2 <- roc(roc_without$actual, roc_without$predicted, quiet = TRUE)

  test_result <- roc.test(roc_obj1, roc_obj2, method = "delong")
  p_val <- test_result$p.value
  p_label <- if_else(p_val < 0.001, "<0.001", sprintf("%.3f", p_val))

  results_unmatched_df <- rbind(
    results_unmatched_df,
    extract_metrics(roc_obj2, "Without UTI", labels[i], p_label),
    extract_metrics(roc_obj1, "With UTI", labels[i], "")
  )
}

results_unmatched_df %>%
  gt() %>%
  tab_header(title = "Unmatched: Without UTI vs With UTI") %>%
  gt_theme_espn()
```

## Matched: Without UTI vs With UTI

```{r delong-matched}
results_matched_df <- data.frame(
  Dataset = character(), Comparison = character(),
  AUC_CI = character(), Sensitivity = character(),
  Specificity = character(), DeLong_p = character(),
  stringsAsFactors = FALSE
)

for (i in seq_along(thresholds)) {
  thresh <- thresholds[i]

  roc_with    <- prep_roc(base_data_match_with_uti, thresh)
  roc_without <- prep_roc(base_data_match_without_uti, thresh)

  roc_obj1 <- roc(roc_with$actual, roc_with$predicted, quiet = TRUE)
  roc_obj2 <- roc(roc_without$actual, roc_without$predicted, quiet = TRUE)

  test_result <- roc.test(roc_obj1, roc_obj2, method = "delong")
  p_val <- test_result$p.value
  p_label <- if_else(p_val < 0.001, "<0.001", sprintf("%.3f", p_val))

  results_matched_df <- rbind(
    results_matched_df,
    extract_metrics(roc_obj2, "Without UTI", labels[i], p_label),
    extract_metrics(roc_obj1, "With UTI", labels[i], "")
    
  )
}

results_matched_df %>%
  gt() %>%
  tab_header(title = "Matched: Without UTI vs With UTI") %>%
  gt_theme_espn()
```

# ROC Curve Plots

## Without UTI

### Unmatched

```{r roc-without-uti-unmatched, fig.width=8, fig.height=6}
roc_plot_without_uti_unmatched <- generate_roc_plot(base_data_without_uti, "ROC Curves: EAU Risk Stratification")
roc_plot_without_uti_unmatched
```

### Matched

```{r roc-without-uti-matched, fig.width=8, fig.height=6}
roc_plot_without_uti_matched <- generate_roc_plot(base_data_match_without_uti, "ROC Curves: EAU Risk Stratification")
roc_plot_without_uti_matched
```

### Split by Initial Presentation

```{r roc-without-uti-faceted, fig.width=10, fig.height=8}
roc_plot_facet_by_any_procedure_without_uti <- generate_faceted_roc_plot(
  base_data_without_uti, "ROC Curves: EAU Risk Stratification by Initial Presentation")
roc_plot_facet_by_any_procedure_without_uti
```

## With UTI

### Unmatched

```{r roc-with-uti-unmatched, fig.width=8, fig.height=6}
roc_plot_with_uti_unmatched <- generate_roc_plot(base_data_with_uti, "ROC Curves: EAU Risk Stratification")
roc_plot_with_uti_unmatched
```

### Matched

```{r roc-with-uti-matched, fig.width=8, fig.height=6}
roc_plot_with_uti_matched <- generate_roc_plot(base_data_match_with_uti, "ROC Curves: EAU Risk Stratification")
roc_plot_with_uti_matched
```

### Split by Initial Presentation

```{r roc-with-uti-faceted, fig.width=10, fig.height=8}
roc_plot_facet_by_any_procedure_with_uti <- generate_faceted_roc_plot(
  base_data_with_uti, "ROC Curves: EAU Risk Stratification by Initial Presentation")
roc_plot_facet_by_any_procedure_with_uti
```

# Kaplan-Meier Plots

## Without UTI

### KM matched dataset

```{r km-match-without-uti}
base_data_without_uti_for_km1 <- base_data_without_uti_for_km %>%
  mutate(
    high_risk_binary = if_else(high_risk == "high_risk", 1L, 0L),
    age_at_first_stone = as.numeric(age_at_first_stone),
    initial_presentation = as.factor(initial_presentation)
  ) %>%
  drop_na(high_risk_binary, age_at_first_stone, initial_presentation)

m <- matchit(high_risk_binary ~ age_at_first_stone + initial_presentation,
             data = base_data_without_uti_for_km1,
             method = "nearest")
base_data_match_without_uti_match <- match.data(m)
```

### Unmatched KM

```{r km-without-uti-unmatched, fig.width=10, fig.height=7}
km_fit <- surv_fit(Surv(time_to_recurrence_1, recurrence) ~ high_risk,
                   data = base_data_without_uti_for_km)

first_to_second_event_by_risk_without_uti_unmatched <- ggsurvplot(
  km_fit,
  data = base_data_without_uti_for_km,
  censor = FALSE, risk.table = TRUE, surv.median.line = "hv",
  conf.int = TRUE, tables.theme = theme_cleantable(),
  break.time.by = 1, xlab = "Time (years)", xlim = c(0, 10),
  title = "Time to First Recurrence", pval = TRUE,
  legend.title = "Risk Status", legend.labs = c("High Risk", "Low Risk"),
  ggtheme = theme_bw()
)
first_to_second_event_by_risk_without_uti_unmatched
```

### Matched KM

```{r km-without-uti-matched, fig.width=10, fig.height=7}
km_fit <- surv_fit(Surv(time_to_recurrence_1, recurrence) ~ high_risk,
                   data = base_data_match_without_uti_match)

first_to_second_event_by_risk_without_uti_matched <- ggsurvplot(
  km_fit,
  data = base_data_match_without_uti_match,
  censor = FALSE, risk.table = TRUE, surv.median.line = "hv",
  conf.int = TRUE, tables.theme = theme_cleantable(),
  break.time.by = 1, xlab = "Time (years)", xlim = c(0, 10),
  title = "Time to First Recurrence", pval = TRUE,
  legend.title = "Risk Status", legend.labs = c("High Risk", "Low Risk"),
  ggtheme = theme_bw()
)
first_to_second_event_by_risk_without_uti_matched
```

### Faceted by Initial Presentation

```{r km-without-uti-faceted, fig.width=10, fig.height=7}
km_fit <- surv_fit(Surv(time_to_recurrence_1, recurrence) ~ high_risk,
                   data = as.data.frame(base_data_without_uti_for_km))

first_to_second_event_by_risk_facet_without_uti <- ggsurvplot_facet(
  km_fit,
  data = as.data.frame(base_data_without_uti_for_km),
  facet.by = "initial_presentation",
  censor = FALSE, conf.int = TRUE, surv.median.line = "hv",
  pval = TRUE, break.time.by = 1, xlim = c(0, 10),
  xlab = "Time (years)", ylab = "Recurrence-free probability",
  legend.title = "Risk Status", legend.labs = c("High Risk", "Low Risk"),
  ggtheme = theme_bw(), panel.labs.font = list(face = "bold")
)
first_to_second_event_by_risk_facet_without_uti
```



## With UTI

### KM matched dataset

```{r km-match-with-uti}
base_data_with_uti_for_km1 <- base_data_with_uti_for_km %>%
  mutate(
    high_risk_binary = if_else(high_risk == "high_risk", 1L, 0L),
    age_at_first_stone = as.numeric(age_at_first_stone),
    initial_presentation = as.factor(initial_presentation)
  ) %>%
  drop_na(high_risk_binary, age_at_first_stone, initial_presentation)

m <- matchit(high_risk_binary ~ age_at_first_stone + initial_presentation,
             data = base_data_with_uti_for_km1,
             method = "nearest")
base_data_match_with_uti_match <- match.data(m)
```

### Unmatched KM

```{r km-with-uti-unmatched, fig.width=10, fig.height=7}
km_fit <- surv_fit(Surv(time_to_recurrence_1, recurrence) ~ high_risk,
                   data = base_data_with_uti_for_km)

first_to_second_event_by_risk_with_uti_unmatched <- ggsurvplot(
  km_fit,
  data = base_data_with_uti_for_km,
  censor = FALSE, risk.table = TRUE, surv.median.line = "hv",
  conf.int = TRUE, tables.theme = theme_cleantable(),
  break.time.by = 1, xlab = "Time (years)", xlim = c(0, 10),
  title = "Time to First Recurrence", pval = TRUE,
  legend.title = "Risk Status", legend.labs = c("High Risk", "Low Risk"),
  ggtheme = theme_bw()
)
first_to_second_event_by_risk_with_uti_unmatched
```

### Matched KM

```{r km-with-uti-matched, fig.width=10, fig.height=7}
km_fit <- surv_fit(Surv(time_to_recurrence_1, recurrence) ~ high_risk,
                   data = base_data_match_with_uti_match)

first_to_second_event_by_risk_with_uti_matched <- ggsurvplot(
  km_fit,
  data = base_data_match_with_uti_match,
  censor = FALSE, risk.table = TRUE, surv.median.line = "hv",
  conf.int = TRUE, tables.theme = theme_cleantable(),
  break.time.by = 1, xlab = "Time (years)", xlim = c(0, 10),
  title = "Time to First Recurrence", pval = TRUE,
  legend.title = "Risk Status", legend.labs = c("High Risk", "Low Risk"),
  ggtheme = theme_bw()
)
first_to_second_event_by_risk_with_uti_matched
```

### Faceted by Initial Presentation

```{r km-with-uti-faceted, fig.width=10, fig.height=7}
km_fit <- surv_fit(Surv(time_to_recurrence_1, recurrence) ~ high_risk,
                   data = as.data.frame(base_data_with_uti_for_km))

first_to_second_event_by_risk_facet_with_uti <- ggsurvplot_facet(
  km_fit,
  data = as.data.frame(base_data_with_uti_for_km),
  facet.by = "initial_presentation",
  censor = FALSE, conf.int = TRUE, surv.median.line = "hv",
  pval = TRUE, break.time.by = 1, xlim = c(0, 10),
  xlab = "Time (years)", ylab = "Recurrence-free probability",
  legend.title = "Risk Status", legend.labs = c("High Risk", "Low Risk"),
  ggtheme = theme_bw(), panel.labs.font = list(face = "bold")
)
first_to_second_event_by_risk_facet_with_uti
```

# DCA

## Without UTI

### Unmatched 
```{r}
thresholds <- c(1, 2, 3)
labels <- c("0 vs ≥1", "0 vs ≥2", "0 vs ≥3")

dca_list <- lapply(seq_along(thresholds), function(i) {
  thresh <- thresholds[i]
  
  dca_data <- base_data_without_uti %>%
    mutate(
      actual = case_when(
        count_diff >= thresh ~ 1,
        count_diff == 0 ~ 0,
        TRUE ~ NA_integer_
      ),
      high_risk = case_when(
        high_risk == "low_risk" ~ 0,
        high_risk == "high_risk" ~ 1,
        TRUE ~ NA_integer_) 
    ) %>%
    drop_na(actual, high_risk)
  
  dca(
    actual ~ high_risk,
    data = dca_data,
    thresholds = seq(0, 0.8, by = 0.01)
  )
})

# Extract plot data and combine
combined_df <- lapply(seq_along(dca_list), function(i) {
  p <- plot(dca_list[[i]])
  p$data %>% mutate(comparison = labels[i])
}) %>%
  bind_rows()

dca_without_uti_unmatched <- ggplot(combined_df, aes(x = threshold, y = net_benefit, colour = label)) +
  geom_line(linewidth = 0.8) +
  facet_wrap(~ comparison, ncol = 3) +
  labs(
    x = "Probability of Recurrence Threshold",
    y = "Net Benefit",
    colour = NULL,
    title = "DCA: UKB Unmatched Dataset Without rUTIs"
  ) +
  theme_bw(base_size = 12) +
  theme(legend.position = "bottom") + 
  scale_colour_discrete(
    labels = c("Follow-up All", "Follow-up None", "Risk Status")
  ) + xlim(c(0,0.6)) + ylim(c(-1.5,0.5)) + geom_vline(xintercept = 0.2, linetype = "dashed")

dca_without_uti_unmatched
```

### Matched 
```{r}
thresholds <- c(1, 2, 3)
labels <- c("0 vs ≥1", "0 vs ≥2", "0 vs ≥3")

dca_list <- lapply(seq_along(thresholds), function(i) {
  thresh <- thresholds[i]
  
  dca_data <- base_data_match_without_uti %>%
    mutate(
      actual = case_when(
        count_diff >= thresh ~ 1,
        count_diff == 0 ~ 0,
        TRUE ~ NA_integer_
      ),
      high_risk = case_when(
        high_risk == "low_risk" ~ 0,
        high_risk == "high_risk" ~ 1,
        TRUE ~ NA_integer_) 
    ) %>%
    drop_na(actual, high_risk)
  
  dca(
    actual ~ high_risk,
    data = dca_data,
    thresholds = seq(0, 0.8, by = 0.01)
  )
})

# Extract plot data and combine
combined_df <- lapply(seq_along(dca_list), function(i) {
  p <- plot(dca_list[[i]])
  p$data %>% mutate(comparison = labels[i])
}) %>%
  bind_rows()

dca_without_uti_matched <- ggplot(combined_df, aes(x = threshold, y = net_benefit, colour = label)) +
  geom_line(linewidth = 0.8) +
  facet_wrap(~ comparison, ncol = 3) +
  labs(
    x = "Probability of Recurrence Threshold",
    y = "Net Benefit",
    colour = NULL,
    title = "DCA: UKB Matched Dataset Without rUTIs"
  ) +
  theme_bw(base_size = 12) +
  theme(legend.position = "bottom") + 
  scale_colour_discrete(
    labels = c("Follow-up All", "Follow-up None", "Risk Status")
  ) + xlim(c(0,0.6)) + ylim(c(-1.5,0.5)) + geom_vline(xintercept = 0.2, linetype = "dashed")

dca_without_uti_matched
```

### By Initial Presentation 
```{r}
thresholds <- c(1, 2, 3)
labels <- c("0 vs ≥1", "0 vs ≥2", "0 vs ≥3")

presentations <- unique(base_data_without_uti$initial_presentation)

combined_df <- lapply(presentations, function(pres) {
  lapply(seq_along(thresholds), function(i) {
    thresh <- thresholds[i]
    
    dca_data <- base_data_without_uti %>%
      filter(initial_presentation == pres) %>%
      mutate(
        actual = case_when(
          count_diff >= thresh ~ 1,
          count_diff == 0 ~ 0,
          TRUE ~ NA_integer_
        ),
        high_risk = case_when(
          high_risk == "low_risk" ~ 0,
          high_risk == "high_risk" ~ 1,
          TRUE ~ NA_integer_
        )
      ) %>%
      drop_na(actual, high_risk)
    
    if (nrow(dca_data) < 10 || length(unique(dca_data$actual)) < 2) return(NULL)
    
    dca_obj <- dca(
      actual ~ high_risk,
      data = dca_data,
      thresholds = seq(0, 0.8, by = 0.01)
    )
    
    p <- plot(dca_obj)
    p$data %>% mutate(comparison = labels[i], initial_presentation = pres)
  }) %>% bind_rows()
}) %>% bind_rows()

dca_initial_presentation_without_uti <- ggplot(combined_df, aes(x = threshold, y = net_benefit, colour = label)) +
  geom_line(linewidth = 0.8) +
  facet_grid(initial_presentation ~ comparison) +
  labs(
    x = "Probability of Recurrence Threshold",
    y = "Net Benefit",
    colour = NULL,
    title = "DCA: UKB Unmatched Dataset Without rUTIs Facetted by Initial Presentation"
  ) +
  theme_bw(base_size = 12) +
  theme(legend.position = "bottom") +
  scale_colour_discrete(
    labels = c("Follow-up All", "Follow-up None", "Risk Status")
  ) +
  xlim(c(0, 0.4)) + ylim(c(-1.0, 0.6)) + geom_vline(xintercept = 0.2, linetype = "dashed")

dca_initial_presentation_without_uti
```

## With UTI

### Unmatched 
```{r}
thresholds <- c(1, 2, 3)
labels <- c("0 vs ≥1", "0 vs ≥2", "0 vs ≥3")

dca_list <- lapply(seq_along(thresholds), function(i) {
  thresh <- thresholds[i]
  
  dca_data <- base_data_with_uti %>%
    mutate(
      actual = case_when(
        count_diff >= thresh ~ 1,
        count_diff == 0 ~ 0,
        TRUE ~ NA_integer_
      ),
      high_risk = case_when(
        high_risk == "low_risk" ~ 0,
        high_risk == "high_risk" ~ 1,
        TRUE ~ NA_integer_) 
    ) %>%
    drop_na(actual, high_risk)
  
  dca(
    actual ~ high_risk,
    data = dca_data,
    thresholds = seq(0, 0.8, by = 0.01)
  )
})

# Extract plot data and combine
combined_df <- lapply(seq_along(dca_list), function(i) {
  p <- plot(dca_list[[i]])
  p$data %>% mutate(comparison = labels[i])
}) %>%
  bind_rows()

dca_with_uti_unmatched <- ggplot(combined_df, aes(x = threshold, y = net_benefit, colour = label)) +
  geom_line(linewidth = 0.8) +
  facet_wrap(~ comparison, ncol = 3) +
  labs(
    x = "Probability of Recurrence Threshold",
    y = "Net Benefit",
    colour = NULL,
    title = "DCA: UKB Unmatched Dataset With rUTIs"
  ) +
  theme_bw(base_size = 12) +
  theme(legend.position = "bottom") + 
  scale_colour_discrete(
    labels = c("Follow-up All", "Follow-up None", "Risk Status")
  ) + xlim(c(0,0.6)) + ylim(c(-1.5,0.5)) + geom_vline(xintercept = 0.2, linetype = "dashed")

dca_with_uti_unmatched
```

### Matched
```{r}
thresholds <- c(1, 2, 3)
labels <- c("0 vs ≥1", "0 vs ≥2", "0 vs ≥3")

dca_list <- lapply(seq_along(thresholds), function(i) {
  thresh <- thresholds[i]
  
  dca_data <- base_data_match_with_uti %>%
    mutate(
      actual = case_when(
        count_diff >= thresh ~ 1,
        count_diff == 0 ~ 0,
        TRUE ~ NA_integer_
      ),
      high_risk = case_when(
        high_risk == "low_risk" ~ 0,
        high_risk == "high_risk" ~ 1,
        TRUE ~ NA_integer_) 
    ) %>%
    drop_na(actual, high_risk)
  
  dca(
    actual ~ high_risk,
    data = dca_data,
    thresholds = seq(0, 0.8, by = 0.01)
  )
})

# Extract plot data and combine
combined_df <- lapply(seq_along(dca_list), function(i) {
  p <- plot(dca_list[[i]])
  p$data %>% mutate(comparison = labels[i])
}) %>%
  bind_rows()

dca_with_uti_matched <- ggplot(combined_df, aes(x = threshold, y = net_benefit, colour = label)) +
  geom_line(linewidth = 0.8) +
  facet_wrap(~ comparison, ncol = 3) +
  labs(
    x = "Probability of Recurrence Threshold",
    y = "Net Benefit",
    colour = NULL,
    title = "DCA: UKB Matched Dataset With rUTIs"
  ) +
  theme_bw(base_size = 12) +
  theme(legend.position = "bottom") + 
  scale_colour_discrete(
    labels = c("Follow-up All", "Follow-up None", "Risk Status")
  ) + xlim(c(0,0.6)) + ylim(c(-1.5,0.5)) + geom_vline(xintercept = 0.2, linetype = "dashed")

dca_with_uti_matched
```

### By Initial Presentation 
```{r}
thresholds <- c(1, 2, 3)
labels <- c("0 vs ≥1", "0 vs ≥2", "0 vs ≥3")

presentations <- unique(base_data_with_uti$initial_presentation)

combined_df <- lapply(presentations, function(pres) {
  lapply(seq_along(thresholds), function(i) {
    thresh <- thresholds[i]
    
    dca_data <- base_data_with_uti %>%
      filter(initial_presentation == pres) %>%
      mutate(
        actual = case_when(
          count_diff >= thresh ~ 1,
          count_diff == 0 ~ 0,
          TRUE ~ NA_integer_
        ),
        high_risk = case_when(
          high_risk == "low_risk" ~ 0,
          high_risk == "high_risk" ~ 1,
          TRUE ~ NA_integer_
        )
      ) %>%
      drop_na(actual, high_risk)
    
    if (nrow(dca_data) < 10 || length(unique(dca_data$actual)) < 2) return(NULL)
    
    dca_obj <- dca(
      actual ~ high_risk,
      data = dca_data,
      thresholds = seq(0, 0.8, by = 0.01)
    )
    
    p <- plot(dca_obj)
    p$data %>% mutate(comparison = labels[i], initial_presentation = pres)
  }) %>% bind_rows()
}) %>% bind_rows()

dca_initial_presentation_with_uti <- ggplot(combined_df, aes(x = threshold, y = net_benefit, colour = label)) +
  geom_line(linewidth = 0.8) +
  facet_grid(initial_presentation ~ comparison) +
  labs(
    x = "Probability of Recurrence Threshold",
    y = "Net Benefit",
    colour = NULL,
    title = "DCA: UKB Unmatched Dataset Without rUTIs"
  ) +
  theme_bw(base_size = 12) +
  theme(legend.position = "bottom") +
  scale_colour_discrete(
    labels = c("Follow-up All", "Follow-up None", "Risk Status")
  ) +
  xlim(c(0, 0.6)) + ylim(c(-1.5, 0.6)) + geom_vline(xintercept = 0.2, linetype = "dashed")

dca_initial_presentation_with_uti
```
# Heatmap

## AUC

```{r}
# Parse AUC values for heatmap
heatmap_data_first_time_only <- all_metrics_combined %>%
  filter(!is.na(Time_Cutoff_Months) | Starting_Point == "Index Date") %>%
  mutate(
    AUC_numeric = as.numeric(str_extract(AUC, "^[0-9.]+")),
    Time_Cutoff_label = if_else(
      is.na(Time_Cutoff_Months) | Starting_Point == "Index Date",
      "EAU Only",
      paste0("\u2264", Time_Cutoff_Months, "mo")
    )
  ) %>% 
  filter(Time_Cutoff_label == "EAU Only") %>%
  mutate(
    UTI = case_when(
      UTI == "With" ~ "With UTI",
      UTI == "Without" ~ "Without UTI"
    ) %>%
      factor(levels = c("With UTI", "Without UTI")),
    Comparison = case_when(
      Comparison == "≥1 subsequent" ~ "≥1 subsequent events",
      Comparison == "≥2 subsequent" ~ "≥2 subsequent events",
      Comparison == "≥3 subsequent" ~ "≥3 subsequent events"
    ) %>% factor(levels = c("≥1 subsequent events", 
                            "≥2 subsequent events", 
                            "≥3 subsequent events"))
  )

median_auc <- median(heatmap_data_first_time_only$AUC_numeric)
min_auc <- min(heatmap_data_first_time_only$AUC_numeric)
max_auc <- max(heatmap_data_first_time_only$AUC_numeric)

if (nrow(heatmap_data_first_time_only) > 0) {
  auc_first_heatmap <- ggplot(heatmap_data_first_time_only,
         aes(x = Comparison, y = UTI, fill = AUC_numeric)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(aes(label = sprintf("%.2f", AUC_numeric)), size = 3) +
    scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                         midpoint = median_auc, name = "AUC", limits = c(min_auc, max_auc)) +
    labs(x = "Subsequent Symptomatic Events needed for 'Recurrence' Definition from First Symptomatic Episode",
         y = "EAU Risk Stratification With / Without UTI",
         title = "AUC") +
    theme_bw(base_size = 11) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "bold"),
          legend.position = "right")
}
auc_first_heatmap
```

## Sensitivity

```{r}
heatmap_data_first_time_only$Sensitivity <- as.numeric(heatmap_data_first_time_only$Sensitivity)
median_sens <- median(heatmap_data_first_time_only$Sensitivity)
min_sens <- min(heatmap_data_first_time_only$Sensitivity)
max_sens <- max(heatmap_data_first_time_only$Sensitivity)

if (nrow(heatmap_data_first_time_only) > 0) {
  sens_first_heatmap <- ggplot(heatmap_data_first_time_only,
         aes(x = Comparison, y = UTI, fill = Sensitivity)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(aes(label = sprintf("%.2f", Sensitivity)), size = 3) +
    scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                         midpoint = median_sens, name = "Sensitivity", limits = c(min_sens, max_sens)) +
    labs(x = "Subsequent Symptomatic Events needed for 'Recurrence' Definition from First Symptomatic Episode",
         y = "EAU Risk Stratification With / Without UTI",
         title = "Sensitivity") +
    theme_bw(base_size = 11) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "bold"),
          legend.position = "right")
}
sens_first_heatmap
```


## Specificity

```{r}
heatmap_data_first_time_only$Specificity <- as.numeric(heatmap_data_first_time_only$Specificity)
median_spec <- median(heatmap_data_first_time_only$Specificity)
min_spec <- min(heatmap_data_first_time_only$Specificity)
max_spec <- max(heatmap_data_first_time_only$Specificity)

if (nrow(heatmap_data_first_time_only) > 0) {
  spec_first_heatmap <- ggplot(heatmap_data_first_time_only,
         aes(x = Comparison, y = UTI, fill = Specificity)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(aes(label = sprintf("%.2f", Specificity)), size = 3) +
    scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                         midpoint = median_spec, name = "Specificity", limits = c(min_spec, max_spec)) +
    labs(x = "Subsequent Symptomatic Events needed for 'Recurrence' Definition from First Symptomatic Episode",
         y = "EAU Risk Stratification With / Without UTI",
         title = "Specificity") +
    theme_bw(base_size = 11) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "bold"),
          legend.position = "right")
}
spec_first_heatmap
```

## Combined plot for 1st time Symptomatic event
```{r}
auc_first_heatmap / sens_first_heatmap / spec_first_heatmap + plot_layout(axes = "collect")
```


# Save Plots

```{r save-plots}
ggsave("roc_plot_without_uti_ukb.pdf", plot = roc_plot_without_uti_unmatched, width = 8, height = 6)
ggsave("roc_plot_with_uti_ukb.pdf", plot = roc_plot_with_uti_unmatched, width = 8, height = 6)
ggsave("roc_plot_matched_without_uti_ukb.pdf", plot = roc_plot_without_uti_matched, width = 8, height = 6)
ggsave("roc_plot_matched_with_uti_ukb.pdf", plot = roc_plot_with_uti_matched, width = 8, height = 6)
ggsave("roc_plot_facet_by_any_procedure_without_uti_ukb.pdf", plot = roc_plot_facet_by_any_procedure_without_uti, width = 10, height = 8)
ggsave("roc_plot_facet_by_any_procedure_with_uti_ukb.pdf", plot = roc_plot_facet_by_any_procedure_with_uti, width = 10, height = 8)

pdf("km_plot_unmatched_without_uti_ukb.pdf", width = 10, height = 7)
print(first_to_second_event_by_risk_without_uti_unmatched)
dev.off()

pdf("km_plot_unmatched_with_uti_ukb.pdf", width = 10, height = 7)
print(first_to_second_event_by_risk_with_uti_unmatched)
dev.off()

pdf("km_plot_matched_without_uti_ukb.pdf", width = 10, height = 7)
print(first_to_second_event_by_risk_without_uti_matched)
dev.off()

pdf("km_plot_matched_with_uti_ukb.pdf", width = 10, height = 7)
print(first_to_second_event_by_risk_with_uti_matched)
dev.off()

pdf("km_plot_facet_without_uti_ukb.pdf", width = 10, height = 7)
print(first_to_second_event_by_risk_facet_without_uti)
dev.off()

pdf("km_plot_facet_with_uti_ukb.pdf", width = 10, height = 7)
print(first_to_second_event_by_risk_facet_with_uti)
dev.off()

ggsave("dca_without_uti_unmatched.pdf", plot = dca_without_uti_unmatched,
       width = 10, height = 8)

ggsave("dca_without_uti_matched.pdf", plot = dca_without_uti_matched,
       width = 10, height = 8)

ggsave("dca_with_uti_unmatched.pdf", plot = dca_with_uti_unmatched,
       width = 10, height = 8)

ggsave("dca_with_uti_matched.pdf", plot = dca_with_uti_matched,
       width = 10, height = 8)

ggsave("dca_initial_presentation_without_uti.pdf", plot = dca_initial_presentation_without_uti,
       width = 10, height = 8)

ggsave("dca_initial_presentation_with_uti.pdf", plot = dca_initial_presentation_with_uti,
       width = 10, height = 8)
```
