---
title: "Prognostic Accuracy Grid Search: Starting Points x Recurrence Definitions"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    code_folding: show
---

# Libraries

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(forcats)
library(anytime)
library(pROC)
library(gt)
library(gtExtras)
library(grid)
library(gridExtra)
library(survminer)
library(survival)
library(MatchIt)
library(dcurves)
library(lubridate)
```

# Data Loading

```{r load-data, message=FALSE, warning=FALSE}
diet_data_participant <- read.csv("diet_data_updated__participant.csv",
                                  na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

recurrence_gp_data <- read.csv("gp_data_gp_clinical.csv",
                               na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

recurrence_data_hesin <- read.csv("data_hesin.csv",
                                  na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

recurrence_data_hesin_diag <- read.csv("data_hesin_diag.csv",
                                       na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

recurrence_data_hesin_critical <- read.csv("data_hesin_critical.csv",
                                           na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

recurrence_data_hesin_oper <- read.csv("data_hesin_oper.csv",
                                       na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

icd10_upto196 <- read.csv("icd10_upto196_participant.csv",
                           na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

icd10_morethan196 <- read.csv("icd10_morethan196_participant.csv",
                               na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

icd10_dates2 <- cbind(icd10_upto196,
                      subset(icd10_morethan196, select = -participant_id)) %>%
  drop_na(diagnoses_icd10)

icd10_data_extra <- read.csv("icd10_extra_participant.csv",
                              na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names() %>%
  subset(select = -c(age_at_recruitment, diagnoses_icd10))

icd9_data <- read.csv("icd9_participant.csv",
                       na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()
```

# Recurrence Identification

```{r identify-recurrence, message=FALSE, warning=FALSE}
source("recurrence_identification_colic_to_colic_multiple_occurrences.R")
```

# Past Medical History

```{r ascertain-pmhx, message=FALSE, warning=FALSE}
source("pmhx_ascertainment_with_dates.R")
```

# Build dates_detailed Object

This uses the episode-based logic from the recurrence identification script.

```{r dates-detailed}
# dates_detailed is already created by the sourced script (line ~1627)
# It contains: participant_id, index_date, first_date, second_date, third_date,
#              fourth_date, fifth_date, n_recurrences, mean_time_between

# Also compute pairwise inter-event times in months
dates_detailed <- dates_detailed %>%
  mutate(
    gap_index_to_first_months  = as.numeric(first_date  - index_date)  / 30.44,
    gap_first_to_second_months = as.numeric(second_date - first_date)  / 30.44,
    gap_second_to_third_months = as.numeric(third_date  - second_date) / 30.44
  )

head(dates_detailed)
```

# Date of Birth Lookup

```{r dob-lookup}
dob_df <- diet_data_participant %>%
  mutate(dob = as.Date(paste("1", month_of_birth, year_of_birth, sep = " - "),
                       format = "%d - %m - %Y")) %>%
  dplyr::select(participant_id, dob)
```

# Age at First Stone (kept for reference / backward compatibility)

```{r age-first-stone}
age_at_first_stone_df <- dates_detailed %>%
  dplyr::select(participant_id, index_date) %>%
  left_join(dob_df, by = "participant_id") %>%
  mutate(age_at_first_stone = as.numeric((index_date - dob) / 365.25)) %>%
  dplyr::select(participant_id, age_at_first_stone)
```

# EAU High-Risk Classification Function

This function creates the high-risk classification for a given starting point.
Age < 25 is evaluated **at the relevant starting date**
Two versions are created: without UTI and with UTI.

```{r high-risk-fn}
# EAU risk factor columns (excluding UTI)
eau_risk_cols <- c("metabolic_disorder", "metabolic_syndrome", "hyperpth",
                   "immunosuppression", "transplant_immunosuppression",
                   "pkd", "msk", "bowel_surgery", "ibd", "malabsorption",
                   "sarcoidosis", "spinal_injury", "cf", "pujo", "diverticulum",
                   "ureteric_stricture", "vur", "single_kidney",
                   "ileal_conduit", "eating_disorder", "horshoe_kidney")

build_high_risk_df <- function(starting_point_col, include_uti = FALSE) {

  # Pick the relevant date column for computing age at start
  ref_dates <- dates_detailed %>%
    dplyr::select(participant_id, ref_date = !!sym(starting_point_col)) %>%
    filter(!is.na(ref_date)) %>%
    distinct(participant_id, .keep_all = TRUE)

  # Compute age at the starting-point date
  age_at_start <- ref_dates %>%
    left_join(dob_df, by = "participant_id") %>%
    mutate(age_at_start = as.numeric((ref_date - dob) / 365.25)) %>%
    dplyr::select(participant_id, age_at_start)

  # Choose which risk factor columns to use
  risk_cols <- if (include_uti) c(eau_risk_cols, "uti") else eau_risk_cols

  hr <- dates_detailed %>%
    dplyr::select(participant_id) %>%
    distinct() %>%
    left_join(pmhx_cleaned, by = "participant_id") %>%
    mutate(across(any_of(risk_cols), ~replace_na(., 0))) %>%
    mutate(
      risk_sum = rowSums(across(any_of(risk_cols)), na.rm = TRUE),
      high_risk = if_else(risk_sum < 1, "low_risk", "high_risk")
    ) %>%
    dplyr::select(participant_id, high_risk) %>%
    left_join(age_at_start, by = "participant_id") %>%
    mutate(high_risk = case_when(age_at_start < 25 ~ "high_risk", TRUE ~ high_risk)) %>%
    group_by(participant_id) %>%
    summarise(high_risk = if_else(any(high_risk == "high_risk"), "high_risk", "low_risk"),
              .groups = "drop")

  return(hr)
}

# Preview: index_date versions
cat("Without UTI (index_date):\n")
table(build_high_risk_df("index_date", include_uti = FALSE)$high_risk)
cat("\nWith UTI (index_date):\n")
table(build_high_risk_df("index_date", include_uti = TRUE)$high_risk)
```

# Grid Search Configuration

```{r grid-config}
# Starting points
starting_points <- c("index_date", "first_date", "second_date", "third_date")

# Recurrence thresholds (subsequent events from starting point)
recurrence_thresholds <- c(1, 2, 3)
recurrence_labels <- c("\u22651 subsequent stone events", "\u22652 subsequent stone events", "\u22653 subsequent stone events")

# Inter-event time cut-offs in months (for first_date onwards analyses)
time_cutoffs_months <- seq(6, 24, by = 3)

# Follow-up horizon (5 years)
follow_up_years <- 5

colors_rec <- c("#1b9e77", "#d95f02", "#7570b3")
```

# Helper: Build Analysis Dataset for a Given Starting Point

```{r build-dataset-fn}
build_analysis_dataset <- function(starting_point_col,
                                   inter_event_cutoff_months = NULL,
                                   include_uti = FALSE) {

  # Get the starting date and count subsequent events
  ds <- dates_detailed %>%
    dplyr::select(participant_id, index_date, first_date, second_date, third_date,
                  fourth_date, fifth_date, n_recurrences, mean_time_between,
                  gap_index_to_first_months, gap_first_to_second_months,
                  gap_second_to_third_months) %>%
    mutate(start_date = !!sym(starting_point_col))

  # Remove participants without a valid starting date

  ds <- ds %>% filter(!is.na(start_date))

  # Count subsequent events (episodes after the starting point, >6 months apart)
  # We already have episode dates in dates_detailed, so count how many fall after start_date
  ds <- ds %>%
    mutate(
      subsequent_events = case_when(
        starting_point_col == "index_date" ~ n_recurrences,
        starting_point_col == "first_date" ~ pmax(n_recurrences - 1L, 0L),
        starting_point_col == "second_date" ~ pmax(n_recurrences - 2L, 0L),
        starting_point_col == "third_date" ~ pmax(n_recurrences - 3L, 0L)
      )
    )

  # Get follow-up info
  last_date_df <- overall_follow_up %>% dplyr::select(participant_id, last_date)

  ds <- ds %>%
    left_join(last_date_df, by = "participant_id") %>%
    drop_na(last_date)

  # Compute time to next event from start_date (for KM)
  ds <- ds %>%
    mutate(
      next_event_date = case_when(
        starting_point_col == "index_date" ~ first_date,
        starting_point_col == "first_date" ~ second_date,
        starting_point_col == "second_date" ~ third_date,
        starting_point_col == "third_date" ~ fourth_date
      ),
      has_next_event = as.integer(!is.na(next_event_date)),
      time_to_next_years = if_else(
        has_next_event == 1L,
        as.numeric(next_event_date - start_date) / 365.25,
        as.numeric(last_date - start_date) / 365.25
      )
    ) %>%
    filter(time_to_next_years > 0)

  # Add high-risk classification (age assessed at this starting point)
  hr_df <- build_high_risk_df(starting_point_col, include_uti = include_uti)
  ds <- ds %>%
    left_join(hr_df, by = "participant_id") %>%
    left_join(age_at_first_stone_df, by = "participant_id")

  # Add initial presentation from first_presentation
  ds <- ds %>%
    left_join(first_presentation %>% dplyr::select(participant_id, initial_presentation),
              by = "participant_id")

  # For first_date onwards: add inter-event time-based high-risk modifier
  if (!is.null(inter_event_cutoff_months) && starting_point_col != "index_date") {
    # Get the gap leading into the starting point
    gap_col <- case_when(
      starting_point_col == "first_date"  ~ "gap_index_to_first_months",
      starting_point_col == "second_date" ~ "gap_first_to_second_months",
      starting_point_col == "third_date"  ~ "gap_second_to_third_months"
    )

    ds <- ds %>%
      mutate(
        prior_gap_months = !!sym(gap_col),
        high_risk_with_time = case_when(
          high_risk == "high_risk" ~ "high_risk",
          !is.na(prior_gap_months) & prior_gap_months <= inter_event_cutoff_months ~ "high_risk",
          TRUE ~ "low_risk"
        )
      )
  } else {
    ds <- ds %>%
      mutate(high_risk_with_time = high_risk)
  }

  return(ds)
}
```

# Helper Functions for Analysis

```{r helper-functions}
prep_roc_grid <- function(ds, thresh, risk_col = "high_risk_with_time") {
  ds %>%
    mutate(
      actual = case_when(
        subsequent_events >= thresh ~ 1L,
        subsequent_events == 0L ~ 0L,
        TRUE ~ NA_integer_
      ),
      predicted = if_else(!!sym(risk_col) == "high_risk", 1, 0)
    ) %>%
    drop_na(actual, predicted)
}

extract_metrics_grid <- function(roc_obj, label, roc_data = NULL) {
  auc_val <- as.numeric(auc(roc_obj))
  auc_ci  <- ci.auc(roc_obj)
  coords_best <- coords(roc_obj, "best", ret = c("sensitivity", "specificity"),
                        best.method = "youden")

  # Contingency table counts & derived metrics with Wilson CIs
  tp <- fp <- tn <- fn <- NA_integer_
  ppv_val <- npv_val <- sens_val <- spec_val <- NA_real_
  ppv_lo <- ppv_hi <- npv_lo <- npv_hi <- NA_real_
  sens_lo <- sens_hi <- spec_lo <- spec_hi <- NA_real_
  n_total <- n_high_risk <- n_low_risk <- NA_integer_
  n_recurred_high <- n_recurred_low <- NA_integer_
  pct_recurred_high <- pct_recurred_low <- NA_real_
  pct_recurred_high_lo <- pct_recurred_high_hi <- NA_real_
  pct_recurred_low_lo  <- pct_recurred_low_hi  <- NA_real_

  sens_val <- coords_best$sensitivity
  spec_val <- coords_best$specificity

  if (!is.null(roc_data)) {
    tp <- sum(roc_data$predicted == 1 & roc_data$actual == 1)
    fp <- sum(roc_data$predicted == 1 & roc_data$actual == 0)
    tn <- sum(roc_data$predicted == 0 & roc_data$actual == 0)
    fn <- sum(roc_data$predicted == 0 & roc_data$actual == 1)
    n_total <- nrow(roc_data)

    ppv_val <- tp / (tp + fp)
    npv_val <- tn / (tn + fn)

    # Wilson score 95% CIs for proportions
    wilson_ci <- function(x, n) {
      if (n == 0) return(c(NA_real_, NA_real_))
      bt <- binom.test(x, n)
      # Use exact Clopper-Pearson from binom.test
      as.numeric(bt$conf.int)
    }

    # Sensitivity CI:  TP / (TP + FN)
    sens_ci <- wilson_ci(tp, tp + fn)
    sens_lo <- sens_ci[1]; sens_hi <- sens_ci[2]

    # Specificity CI:  TN / (TN + FP)
    spec_ci <- wilson_ci(tn, tn + fp)
    spec_lo <- spec_ci[1]; spec_hi <- spec_ci[2]

    # PPV CI:  TP / (TP + FP)
    ppv_ci <- wilson_ci(tp, tp + fp)
    ppv_lo <- ppv_ci[1]; ppv_hi <- ppv_ci[2]

    # NPV CI:  TN / (TN + FN)
    npv_ci <- wilson_ci(tn, tn + fn)
    npv_lo <- npv_ci[1]; npv_hi <- npv_ci[2]

    # Likelihood of recurrence by risk group
    n_high_risk     <- tp + fp
    n_low_risk      <- tn + fn
    n_recurred_high <- tp
    n_recurred_low  <- fn

    pct_recurred_high <- if (n_high_risk > 0) tp / n_high_risk * 100 else NA_real_
    pct_recurred_low  <- if (n_low_risk > 0)  fn / n_low_risk  * 100 else NA_real_

    if (n_high_risk > 0) {
      hr_ci <- wilson_ci(tp, n_high_risk)
      pct_recurred_high_lo <- hr_ci[1] * 100; pct_recurred_high_hi <- hr_ci[2] * 100
    }
    if (n_low_risk > 0) {
      lr_ci <- wilson_ci(fn, n_low_risk)
      pct_recurred_low_lo <- lr_ci[1] * 100; pct_recurred_low_hi <- lr_ci[2] * 100
    }
  }

  # Return both display-formatted and raw numeric columns
  data.frame(
    Comparison = label,
    N = n_total,
    N_High_Risk = n_high_risk,
    N_Low_Risk = n_low_risk,
    AUC = sprintf("%.3f (%.3f\u2013%.3f)", auc_val, auc_ci[1], auc_ci[3]),
    AUC_val = auc_val,
    AUC_lo = as.numeric(auc_ci[1]),
    AUC_hi = as.numeric(auc_ci[3]),
    Sensitivity = sprintf("%.3f (%.3f\u2013%.3f)", sens_val, sens_lo, sens_hi),
    Sensitivity_val = sens_val,
    Sensitivity_lo = sens_lo,
    Sensitivity_hi = sens_hi,
    Specificity = sprintf("%.3f (%.3f\u2013%.3f)", spec_val, spec_lo, spec_hi),
    Specificity_val = spec_val,
    Specificity_lo = spec_lo,
    Specificity_hi = spec_hi,
    PPV = sprintf("%.3f (%.3f\u2013%.3f)", ppv_val, ppv_lo, ppv_hi),
    PPV_val = ppv_val,
    PPV_lo = ppv_lo,
    PPV_hi = ppv_hi,
    NPV = sprintf("%.3f (%.3f\u2013%.3f)", npv_val, npv_lo, npv_hi),
    NPV_val = npv_val,
    NPV_lo = npv_lo,
    NPV_hi = npv_hi,
    Likelihood_Recurrence_High_Risk_pct = pct_recurred_high,
    Likelihood_Recurrence_High_Risk_lo = pct_recurred_high_lo,
    Likelihood_Recurrence_High_Risk_hi = pct_recurred_high_hi,
    N_Recurred_High_Risk = n_recurred_high,
    Likelihood_Recurrence_Low_Risk_pct = pct_recurred_low,
    Likelihood_Recurrence_Low_Risk_lo = pct_recurred_low_lo,
    Likelihood_Recurrence_Low_Risk_hi = pct_recurred_low_hi,
    N_Recurred_Low_Risk = n_recurred_low,
    stringsAsFactors = FALSE
  )
}

generate_roc_plot_grid <- function(ds, plot_title, risk_col = "high_risk_with_time") {
  roc_combined_df <- data.frame()
  ci_combined_df <- data.frame()
  auc_table_df <- data.frame()

  for (i in seq_along(recurrence_thresholds)) {
    thresh <- recurrence_thresholds[i]
    label <- recurrence_labels[i]

    roc_data <- prep_roc_grid(ds, thresh, risk_col)
    if (nrow(roc_data) < 10 || length(unique(roc_data$actual)) < 2) next

    roc_obj <- roc(roc_data$actual, roc_data$predicted, quiet = TRUE)

    roc_combined_df <- rbind(roc_combined_df, data.frame(
      fpr = 1 - roc_obj$specificities,
      tpr = roc_obj$sensitivities,
      Comparison = label
    ))

    ci_se <- ci.se(roc_obj, specificities = seq(0, 1, length.out = 100))
    ci_combined_df <- rbind(ci_combined_df, data.frame(
      fpr = 1 - as.numeric(rownames(ci_se)),
      tpr_lower = ci_se[, 1],
      tpr_upper = ci_se[, 3],
      Comparison = label
    ))

    auc_val <- as.numeric(auc(roc_obj))
    auc_ci <- ci.auc(roc_obj)
    auc_table_df <- rbind(auc_table_df, data.frame(
      Comparison = label,
      AUC_CI = sprintf("%.2f (%.2f\u2013%.2f)", auc_val, auc_ci[1], auc_ci[3])
    ))
  }

  if (nrow(roc_combined_df) == 0) return(NULL)

  auc_table <- tableGrob(auc_table_df, rows = NULL, theme = ttheme_minimal(base_size = 9))
  auc_table_boxed <- grobTree(
    rectGrob(gp = gpar(col = "black", fill = "white", lwd = 1)),
    auc_table
  )

  ggplot() +
    geom_ribbon(data = ci_combined_df,
                aes(x = fpr, ymin = tpr_lower, ymax = tpr_upper, fill = Comparison),
                alpha = 0.2) +
    geom_line(data = roc_combined_df,
              aes(x = fpr, y = tpr, color = Comparison), linewidth = 1) +
    geom_abline(linetype = "dashed", alpha = 0.6) +
    labs(x = "False Positive Rate", y = "True Positive Rate", title = plot_title) +
    scale_color_manual(values = colors_rec) +
    scale_fill_manual(values = colors_rec) +
    coord_equal() +
    theme_bw(base_size = 12) +
    theme(legend.position = "bottom") +
    annotation_custom(grob = auc_table_boxed,
                      xmin = 0.55, xmax = 1, ymin = 0.05, ymax = 0.3)
}

generate_km_plot_grid <- function(ds, plot_title, risk_col = "high_risk_with_time") {
  km_data <- ds %>%
    rename(risk_group = !!sym(risk_col)) %>%
    filter(!is.na(time_to_next_years), !is.na(risk_group)) %>%
    mutate(recurrence = has_next_event)

  if (nrow(km_data) < 10 || length(unique(km_data$risk_group)) < 2) return(NULL)

  km_fit <- surv_fit(Surv(time_to_next_years, recurrence) ~ risk_group, data = km_data)

  ggsurvplot(
    km_fit,
    data = km_data,
    censor = FALSE, risk.table = TRUE, surv.median.line = "hv",
    conf.int = TRUE, tables.theme = theme_cleantable(),
    break.time.by = 1, xlab = "Time (years)", xlim = c(0, 10),
    title = plot_title, pval = TRUE,
    legend.title = "Risk Status", legend.labs = c("High Risk", "Low Risk"),
    ggtheme = theme_bw()
  )
}

generate_dca_plot_grid <- function(ds, plot_title, risk_col = "high_risk_with_time") {
  dca_list <- lapply(seq_along(recurrence_thresholds), function(i) {
    thresh <- recurrence_thresholds[i]

    dca_data <- ds %>%
      mutate(
        actual = case_when(
          subsequent_events >= thresh ~ 1L,
          subsequent_events == 0L ~ 0L,
          TRUE ~ NA_integer_
        ),
        risk_binary = case_when(
          !!sym(risk_col) == "low_risk" ~ 0,
          !!sym(risk_col) == "high_risk" ~ 1,
          TRUE ~ NA_real_)
      ) %>%
      drop_na(actual, risk_binary)

    if (nrow(dca_data) < 10 || length(unique(dca_data$actual)) < 2) return(NULL)

    dca(actual ~ risk_binary, data = dca_data, thresholds = seq(0, 0.8, by = 0.01))
  })

  dca_list <- dca_list[!sapply(dca_list, is.null)]
  if (length(dca_list) == 0) return(NULL)

  labels_used <- recurrence_labels[seq_along(dca_list)]

  combined_df <- lapply(seq_along(dca_list), function(i) {
    p <- plot(dca_list[[i]])
    p$data %>% mutate(comparison = labels_used[i])
  }) %>% bind_rows()

  ggplot(combined_df, aes(x = threshold, y = net_benefit, colour = label)) +
    geom_line(linewidth = 0.8) +
    facet_wrap(~ comparison, ncol = 3) +
    labs(x = "Probability of Recurrence Threshold",
         y = "Net Benefit", colour = NULL, title = plot_title) +
    theme_bw(base_size = 12) +
    theme(legend.position = "bottom") +
    scale_colour_discrete(labels = c("Follow-up All", "Follow-up None", "Risk Status")) +
    xlim(c(0, 0.6)) +
    geom_vline(xintercept = 0.2, linetype = "dashed")
}
```

# Analysis 1: Index Date (EAU Risk Only)

## Without UTI

```{r analysis-index-no-uti, fig.width=10, fig.height=8, warning=FALSE, message=FALSE}
ds_index <- build_analysis_dataset("index_date", include_uti = FALSE)

cat("N participants from index_date (without UTI):", nrow(ds_index), "\n")
table(ds_index$subsequent_events)
```

### ROC Curves
```{r roc-index-no-uti, fig.width=8, fig.height=6, warning=FALSE}
roc_index <- generate_roc_plot_grid(ds_index, "ROC: From Index Date (EAU Risk, Without UTI)")
roc_index
```

### Kaplan-Meier
```{r km-index-no-uti, fig.width=10, fig.height=7, warning=FALSE}
km_index <- generate_km_plot_grid(ds_index, "KM: From Index Date (EAU Risk, Without UTI)")
km_index
```

### Decision Curve Analysis
```{r dca-index-no-uti, fig.width=10, fig.height=6, warning=FALSE}
dca_index <- generate_dca_plot_grid(ds_index, "DCA: From Index Date (EAU Risk, Without UTI)")
dca_index
```

### Metrics Table
```{r metrics-index-no-uti, warning=FALSE}
metrics_index_no_uti <- lapply(seq_along(recurrence_thresholds), function(i) {
  roc_data <- prep_roc_grid(ds_index, recurrence_thresholds[i])
  if (nrow(roc_data) < 10 || length(unique(roc_data$actual)) < 2) return(NULL)
  roc_obj <- roc(roc_data$actual, roc_data$predicted, quiet = TRUE)
  extract_metrics_grid(roc_obj, recurrence_labels[i], roc_data) %>%
    mutate(Starting_Point = "Index Date", Time_Cutoff_Months = NA_real_, UTI = "Without")
}) %>% bind_rows()

metrics_index_no_uti %>% gt() %>% gt_theme_espn()
```

## With UTI

```{r analysis-index-with-uti, fig.width=10, fig.height=8, warning=FALSE, message=FALSE}
ds_index_uti <- build_analysis_dataset("index_date", include_uti = TRUE)

cat("N participants from index_date (with UTI):", nrow(ds_index_uti), "\n")
table(ds_index_uti$subsequent_events)
```

### ROC Curves
```{r roc-index-with-uti, fig.width=8, fig.height=6, warning=FALSE}
roc_index_uti <- generate_roc_plot_grid(ds_index_uti, "ROC: From Index Date (EAU Risk, With UTI)")
roc_index_uti
```

### Kaplan-Meier
```{r km-index-with-uti, fig.width=10, fig.height=7, warning=FALSE}
km_index_uti <- generate_km_plot_grid(ds_index_uti, "KM: From Index Date (EAU Risk, With UTI)")
km_index_uti
```

### Decision Curve Analysis
```{r dca-index-with-uti, fig.width=10, fig.height=6, warning=FALSE}
dca_index_uti <- generate_dca_plot_grid(ds_index_uti, "DCA: From Index Date (EAU Risk, With UTI)")
dca_index_uti
```

### Metrics Table
```{r metrics-index-with-uti, warning=FALSE}
metrics_index_with_uti <- lapply(seq_along(recurrence_thresholds), function(i) {
  roc_data <- prep_roc_grid(ds_index_uti, recurrence_thresholds[i])
  if (nrow(roc_data) < 10 || length(unique(roc_data$actual)) < 2) return(NULL)
  roc_obj <- roc(roc_data$actual, roc_data$predicted, quiet = TRUE)
  extract_metrics_grid(roc_obj, recurrence_labels[i], roc_data) %>%
    mutate(Starting_Point = "Index Date", Time_Cutoff_Months = NA_real_, UTI = "With")
}) %>% bind_rows()

metrics_index_with_uti %>% gt() %>% gt_theme_espn()
```

# Analysis 2-4: First/Second/Third Date with Inter-Event Time Grid Search

For starting points beyond index_date, we add the inter-event time cut-off
(6, 9, 12, 15, 18, 21, 24 months) to the high-risk definition:
participants whose prior gap was <= the cut-off are classified as high-risk
regardless of EAU risk factors.

```{r grid-search-fn, warning=FALSE, message=FALSE}
run_grid_search <- function(starting_point_col, sp_label, include_uti = FALSE) {

  all_metrics <- data.frame()
  all_roc_plots <- list()
  all_km_plots <- list()
  all_dca_plots <- list()

  for (cutoff in time_cutoffs_months) {

    ds <- build_analysis_dataset(starting_point_col,
                                 inter_event_cutoff_months = cutoff,
                                 include_uti = include_uti)

    if (nrow(ds) < 20) next

    uti_tag <- if (include_uti) ", With UTI" else ", Without UTI"
    cutoff_label <- paste0(sp_label, " | Gap \u2264", cutoff, "mo = High Risk", uti_tag)

    # Metrics
    for (i in seq_along(recurrence_thresholds)) {
      roc_data <- prep_roc_grid(ds, recurrence_thresholds[i])
      if (nrow(roc_data) < 10 || length(unique(roc_data$actual)) < 2) next
      roc_obj <- roc(roc_data$actual, roc_data$predicted, quiet = TRUE)
      m <- extract_metrics_grid(roc_obj, recurrence_labels[i], roc_data)
      m$Starting_Point <- sp_label
      m$Time_Cutoff_Months <- cutoff
      m$UTI <- if (include_uti) "With" else "Without"
      all_metrics <- rbind(all_metrics, m)
    }

    # ROC
    roc_p <- generate_roc_plot_grid(ds, paste0("ROC: ", cutoff_label))
    if (!is.null(roc_p)) all_roc_plots[[paste0("cutoff_", cutoff)]] <- roc_p

    # KM
    km_p <- generate_km_plot_grid(ds, paste0("KM: ", cutoff_label))
    if (!is.null(km_p)) all_km_plots[[paste0("cutoff_", cutoff)]] <- km_p

    # DCA
    dca_p <- generate_dca_plot_grid(ds, paste0("DCA: ", cutoff_label))
    if (!is.null(dca_p)) all_dca_plots[[paste0("cutoff_", cutoff)]] <- dca_p
  }

  list(metrics = all_metrics,
       roc_plots = all_roc_plots,
       km_plots = all_km_plots,
       dca_plots = all_dca_plots)
}
```

## From First Date (1st Recurrence) - Without UTI

```{r grid-first-no-uti, fig.width=10, fig.height=8, warning=FALSE, message=FALSE, results='asis'}
results_first_no_uti <- run_grid_search("first_date", "Second Event", include_uti = FALSE)

cat("\n### Metrics Summary\n")
if (nrow(results_first_no_uti$metrics) > 0) {
  print(
    results_first_no_uti$metrics %>%
      gt() %>%
      tab_header(title = "Prognostic Accuracy: From Second Event (Without UTI)") %>%
      gt_theme_espn()
  )
}
```

### ROC Curves - First Date (Without UTI)
```{r roc-first-no-uti, fig.width=8, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_first_no_uti$roc_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_first_no_uti$roc_plots[[nm]])
  cat("\n")
}
```

### Kaplan-Meier - First Date (Without UTI)
```{r km-first-no-uti, fig.width=10, fig.height=7, warning=FALSE, results='asis'}
for (nm in names(results_first_no_uti$km_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_first_no_uti$km_plots[[nm]])
  cat("\n")
}
```

### DCA - First Date (Without UTI)
```{r dca-first-no-uti, fig.width=10, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_first_no_uti$dca_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_first_no_uti$dca_plots[[nm]])
  cat("\n")
}
```

## From First Date (1st Recurrence) - With UTI

```{r grid-first-with-uti, fig.width=10, fig.height=8, warning=FALSE, message=FALSE, results='asis'}
results_first_with_uti <- run_grid_search("first_date", "Second Event", include_uti = TRUE)

cat("\n### Metrics Summary\n")
if (nrow(results_first_with_uti$metrics) > 0) {
  print(
    results_first_with_uti$metrics %>%
      gt() %>%
      tab_header(title = "Prognostic Accuracy: From Second Event (With UTI)") %>%
      gt_theme_espn()
  )
}
```

### ROC Curves - First Date (With UTI)
```{r roc-first-with-uti, fig.width=8, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_first_with_uti$roc_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_first_with_uti$roc_plots[[nm]])
  cat("\n")
}
```

### Kaplan-Meier - First Date (With UTI)
```{r km-first-with-uti, fig.width=10, fig.height=7, warning=FALSE, results='asis'}
for (nm in names(results_first_with_uti$km_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_first_with_uti$km_plots[[nm]])
  cat("\n")
}
```

### DCA - First Date (With UTI)
```{r dca-first-with-uti, fig.width=10, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_first_with_uti$dca_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_first_with_uti$dca_plots[[nm]])
  cat("\n")
}
```

## From Second Date (2nd Recurrence) - Without UTI

```{r grid-second-no-uti, fig.width=10, fig.height=8, warning=FALSE, message=FALSE, results='asis'}
results_second_no_uti <- run_grid_search("second_date", "Third Event", include_uti = FALSE)

cat("\n### Metrics Summary\n")
if (nrow(results_second_no_uti$metrics) > 0) {
  print(
    results_second_no_uti$metrics %>%
      gt() %>%
      tab_header(title = "Prognostic Accuracy: From Third Event (Without UTI)") %>%
      gt_theme_espn()
  )
}
```

### ROC Curves - Second Date (Without UTI)
```{r roc-second-no-uti, fig.width=8, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_second_no_uti$roc_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_second_no_uti$roc_plots[[nm]])
  cat("\n")
}
```

### Kaplan-Meier - Second Date (Without UTI)
```{r km-second-no-uti, fig.width=10, fig.height=7, warning=FALSE, results='asis'}
for (nm in names(results_second_no_uti$km_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_second_no_uti$km_plots[[nm]])
  cat("\n")
}
```

### DCA - Second Date (Without UTI)
```{r dca-second-no-uti, fig.width=10, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_second_no_uti$dca_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_second_no_uti$dca_plots[[nm]])
  cat("\n")
}
```

## From Second Date (2nd Recurrence) - With UTI

```{r grid-second-with-uti, fig.width=10, fig.height=8, warning=FALSE, message=FALSE, results='asis'}
results_second_with_uti <- run_grid_search("second_date", "Third Event", include_uti = TRUE)

cat("\n### Metrics Summary\n")
if (nrow(results_second_with_uti$metrics) > 0) {
  print(
    results_second_with_uti$metrics %>%
      gt() %>%
      tab_header(title = "Prognostic Accuracy: From Third Event (With UTI)") %>%
      gt_theme_espn()
  )
}
```

### ROC Curves - Second Date (With UTI)
```{r roc-second-with-uti, fig.width=8, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_second_with_uti$roc_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_second_with_uti$roc_plots[[nm]])
  cat("\n")
}
```

### Kaplan-Meier - Second Date (With UTI)
```{r km-second-with-uti, fig.width=10, fig.height=7, warning=FALSE, results='asis'}
for (nm in names(results_second_with_uti$km_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_second_with_uti$km_plots[[nm]])
  cat("\n")
}
```

### DCA - Second Date (With UTI)
```{r dca-second-with-uti, fig.width=10, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_second_with_uti$dca_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_second_with_uti$dca_plots[[nm]])
  cat("\n")
}
```

## From Third Date (3rd Recurrence) - Without UTI

```{r grid-third-no-uti, fig.width=10, fig.height=8, warning=FALSE, message=FALSE, results='asis'}
results_third_no_uti <- run_grid_search("third_date", "Fourth Event", include_uti = FALSE)

cat("\n### Metrics Summary\n")
if (nrow(results_third_no_uti$metrics) > 0) {
  print(
    results_third_no_uti$metrics %>%
      gt() %>%
      tab_header(title = "Prognostic Accuracy: From Fourth Event (Without UTI)") %>%
      gt_theme_espn()
  )
}
```

### ROC Curves - Third Date (Without UTI)
```{r roc-third-no-uti, fig.width=8, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_third_no_uti$roc_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_third_no_uti$roc_plots[[nm]])
  cat("\n")
}
```

### Kaplan-Meier - Third Date (Without UTI)
```{r km-third-no-uti, fig.width=10, fig.height=7, warning=FALSE, results='asis'}
for (nm in names(results_third_no_uti$km_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_third_no_uti$km_plots[[nm]])
  cat("\n")
}
```

### DCA - Third Date (Without UTI)
```{r dca-third-no-uti, fig.width=10, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_third_no_uti$dca_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_third_no_uti$dca_plots[[nm]])
  cat("\n")
}
```

## From Third Date (3rd Recurrence) - With UTI

```{r grid-third-with-uti, fig.width=10, fig.height=8, warning=FALSE, message=FALSE, results='asis'}
results_third_with_uti <- run_grid_search("third_date", "Fourth Event", include_uti = TRUE)

cat("\n### Metrics Summary\n")
if (nrow(results_third_with_uti$metrics) > 0) {
  print(
    results_third_with_uti$metrics %>%
      gt() %>%
      tab_header(title = "Prognostic Accuracy: From Fourth Event (With UTI)") %>%
      gt_theme_espn()
  )
}
```

### ROC Curves - Third Date (With UTI)
```{r roc-third-with-uti, fig.width=8, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_third_with_uti$roc_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_third_with_uti$roc_plots[[nm]])
  cat("\n")
}
```

### Kaplan-Meier - Third Date (With UTI)
```{r km-third-with-uti, fig.width=10, fig.height=7, warning=FALSE, results='asis'}
for (nm in names(results_third_with_uti$km_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_third_with_uti$km_plots[[nm]])
  cat("\n")
}
```

### DCA - Third Date (With UTI)
```{r dca-third-with-uti, fig.width=10, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_third_with_uti$dca_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_third_with_uti$dca_plots[[nm]])
  cat("\n")
}
```

# Combined Metrics Summary

```{r combined-metrics, warning=FALSE}
all_metrics_combined <- bind_rows(
  metrics_index_no_uti,
  metrics_index_with_uti,
  results_first_no_uti$metrics,
  results_first_with_uti$metrics,
  results_second_no_uti$metrics,
  results_second_with_uti$metrics,
  results_third_no_uti$metrics,
  results_third_with_uti$metrics
)

all_metrics_combined %>%
  dplyr::select(Starting_Point, Time_Cutoff_Months, UTI, Comparison, N,
                AUC, Sensitivity, Specificity, PPV, NPV) %>%
  gt() %>%
  tab_header(title = "Complete Grid Search: Prognostic Accuracy Summary") %>%
  gt_theme_espn()
```

# Recurrent/Short time Heatmaps:

## AUC

```{r heatmap, fig.width=12, fig.height=8, warning=FALSE}
# Parse AUC values for heatmap
heatmap_data <- all_metrics_combined %>%
  filter(!is.na(Time_Cutoff_Months), Starting_Point != "Index Date") %>%
  mutate(
    AUC_numeric = AUC_val,
    Time_Cutoff_label = paste0("\u2264", Time_Cutoff_Months, "mo")
  ) %>%
  mutate(
    Time_Cutoff_label = factor(Time_Cutoff_label,
                               levels = c(
                                 "≤6mo",
                                  "≤9mo",
                                 "≤12mo",
                                 "≤15mo",
                                 "≤18mo",
                                 "≤21mo",
                                 "≤24mo"
                               )),
    Starting_Point = case_when(
      Starting_Point == "Second Event" ~ "Second Symptomatic Episode",
      Starting_Point == "Third Event" ~ "Third Symptomatic Episode",
      Starting_Point == "Fourth Event" ~ "Fourth Symptomatic Episode"
    ) %>% factor(levels = c("Fourth Symptomatic Episode",
                            "Third Symptomatic Episode",
                            "Second Symptomatic Episode")),
    UTI = case_when(
      UTI == "With" ~ "With UTI",
      UTI == "Without" ~ "Without UTI"
    ) %>%
      factor(levels = c("Without UTI", "With UTI")),
    Comparison = factor(Comparison, levels = c("\u22651 subsequent stone events",
                                               "\u22652 subsequent stone events",
                                               "\u22653 subsequent stone events"))
  )

median_auc <- median(heatmap_data$AUC_numeric)
min_auc <- min(heatmap_data$AUC_numeric)
max_auc <- max(heatmap_data$AUC_numeric)

if (nrow(heatmap_data) > 0) {
  auc_heatmap <- ggplot(heatmap_data,
         aes(x = Time_Cutoff_label, y = Starting_Point, fill = AUC_numeric)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(aes(label = sprintf("%.2f", AUC_numeric)), size = 3) +
    facet_grid(UTI ~ Comparison) +
    scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                         midpoint = median_auc, name = "AUC", limits = c(min_auc, max_auc)) +
    labs(x = "Threshold for 'Short Time' Definition",
         y = "Threshold for 'Recurrent' Definition",
         title = "AUC",
         subtitle = "            Subsequent Symptomatic Events needed for 'Recurrence' Definition") +
    theme_bw(base_size = 11) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "bold"),
          legend.position = "right")
}
auc_heatmap
```

## Sensitivity
```{r}
median_sens <- median(heatmap_data$Sensitivity_val, na.rm = TRUE)
min_sens <- min(heatmap_data$Sensitivity_val, na.rm = TRUE)
max_sens <- max(heatmap_data$Sensitivity_val, na.rm = TRUE)

if (nrow(heatmap_data) > 0) {
  sens_heatmap <- ggplot(heatmap_data,
         aes(x = Time_Cutoff_label, y = Starting_Point, fill = Sensitivity_val)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(aes(label = sprintf("%.2f", Sensitivity_val)), size = 3) +
    facet_grid(UTI ~ Comparison) +
    scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                         midpoint = median_sens, name = "Sensitivity", limits = c(min_sens, max_sens)) +
    labs(x = "Threshold for 'Short Time' Definition",
         y = "Threshold for 'Recurrent' Definition",
         title = "Sensitivity",
         subtitle = "            Subsequent Symptomatic Events needed for 'Recurrence' Definition") +
    theme_bw(base_size = 11) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "bold"),
          legend.position = "right")
}
sens_heatmap
```


## Specificity
```{r}
median_spec <- median(heatmap_data$Specificity_val, na.rm = TRUE)
min_spec <- min(heatmap_data$Specificity_val, na.rm = TRUE)
max_spec <- max(heatmap_data$Specificity_val, na.rm = TRUE)

if (nrow(heatmap_data) > 0) {
  spec_heatmap <- ggplot(heatmap_data,
         aes(x = Time_Cutoff_label, y = Starting_Point, fill = Specificity_val)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(aes(label = sprintf("%.2f", Specificity_val)), size = 3) +
    facet_grid(UTI ~ Comparison) +
    scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                         midpoint = median_spec, name = "Specificity", limits = c(min_spec, max_spec)) +
    labs(x = "Threshold for 'Short Time' Definition",
         y = "Threshold for 'Recurrent' Definition",
         title = "Specificity",
         subtitle = "            Subsequent Symptomatic Events needed for 'Recurrence' Definition") +
    theme_bw(base_size = 11) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "bold"),
          legend.position = "right")
}
spec_heatmap
```

## PPV
```{r heatmap-ppv, fig.width=12, fig.height=8, warning=FALSE}
median_ppv <- median(heatmap_data$PPV_val, na.rm = TRUE)
min_ppv <- min(heatmap_data$PPV_val, na.rm = TRUE)
max_ppv <- max(heatmap_data$PPV_val, na.rm = TRUE)

if (nrow(heatmap_data) > 0) {
  ppv_heatmap <- ggplot(heatmap_data,
         aes(x = Time_Cutoff_label, y = Starting_Point, fill = PPV_val)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(aes(label = sprintf("%.2f", PPV_val)), size = 3) +
    facet_grid(UTI ~ Comparison) +
    scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                         midpoint = median_ppv, name = "PPV", limits = c(min_ppv, max_ppv)) +
    labs(x = "Threshold for 'Short Time' Definition",
         y = "Threshold for 'Recurrent' Definition",
         title = "Positive Predictive Value",
         subtitle = "            Subsequent Symptomatic Events needed for 'Recurrence' Definition") +
    theme_bw(base_size = 11) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "bold"),
          legend.position = "right")
}
ppv_heatmap
```

## NPV
```{r heatmap-npv, fig.width=12, fig.height=8, warning=FALSE}
median_npv <- median(heatmap_data$NPV_val, na.rm = TRUE)
min_npv <- min(heatmap_data$NPV_val, na.rm = TRUE)
max_npv <- max(heatmap_data$NPV_val, na.rm = TRUE)

if (nrow(heatmap_data) > 0) {
  npv_heatmap <- ggplot(heatmap_data,
         aes(x = Time_Cutoff_label, y = Starting_Point, fill = NPV_val)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(aes(label = sprintf("%.2f", NPV_val)), size = 3) +
    facet_grid(UTI ~ Comparison) +
    scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                         midpoint = median_npv, name = "NPV", limits = c(min_npv, max_npv)) +
    labs(x = "Threshold for 'Short Time' Definition",
         y = "Threshold for 'Recurrent' Definition",
         title = "Negative Predictive Value",
         subtitle = "            Subsequent Symptomatic Events needed for 'Recurrence' Definition") +
    theme_bw(base_size = 11) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "bold"),
          legend.position = "right")
}
npv_heatmap
```

## Likelihood of Recurrence by Risk Group

This heatmap shows the proportion of participants in each risk group who
experienced recurrence, across all grid-search combinations.

```{r likelihood-heatmap, fig.width=12, fig.height=10, warning=FALSE, message=FALSE}
# Build likelihood data across all grid-search combinations (excluding index date)
likelihood_rows <- list()

for (sp_col in c("first_date", "second_date", "third_date")) {
  sp_label <- switch(sp_col,
                     first_date  = "Second Event",
                     second_date = "Third Event",
                     third_date  = "Fourth Event")

  for (cutoff in time_cutoffs_months) {
    for (uti_flag in c(FALSE, TRUE)) {
      ds <- build_analysis_dataset(sp_col,
                                   inter_event_cutoff_months = cutoff,
                                   include_uti = uti_flag)
      if (nrow(ds) < 20) next

      for (i in seq_along(recurrence_thresholds)) {
        thresh <- recurrence_thresholds[i]
        label  <- recurrence_labels[i]

        tmp <- ds %>%
          mutate(recurred = as.integer(subsequent_events >= thresh)) %>%
          group_by(high_risk_with_time) %>%
          summarise(n = n(),
                    n_recurred = sum(recurred, na.rm = TRUE),
                    .groups = "drop") %>%
          mutate(
            pct_recurred = n_recurred / n * 100,
            Starting_Point = sp_label,
            Time_Cutoff_Months = cutoff,
            Comparison = label,
            UTI = if (uti_flag) "With" else "Without"
          )
        likelihood_rows <- c(likelihood_rows, list(tmp))
      }
    }
  }
}

likelihood_df <- bind_rows(likelihood_rows) %>%
  mutate(
    Time_Cutoff_label = paste0("\u2264", Time_Cutoff_Months, "mo"),
    Time_Cutoff_label = factor(Time_Cutoff_label,
                               levels = c("\u22646mo", "\u22649mo", "\u226412mo",
                                          "\u226415mo", "\u226418mo", "\u226421mo",
                                          "\u226424mo")),
    Starting_Point = factor(Starting_Point,
                            levels = c("Fourth Event",
                                       "Third Event",
                                       "Second Event")),
    UTI = factor(if_else(UTI == "With", "With UTI", "Without UTI"),
                 levels = c("Without UTI", "With UTI")),
    Comparison = factor(Comparison, levels = recurrence_labels),
    risk_label = case_when(
      high_risk_with_time == "high_risk" ~ "High Risk",
      high_risk_with_time == "low_risk"  ~ "Low Risk"
    )
  )

# High-risk recurrence rate
lr_high <- likelihood_df %>% filter(risk_label == "High Risk")
median_hr <- median(lr_high$pct_recurred, na.rm = TRUE)

high_risk_likelihood <- ggplot(lr_high,
       aes(x = Time_Cutoff_label, y = Starting_Point, fill = pct_recurred)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = sprintf("%.1f%%", pct_recurred)), size = 2.8) +
  facet_grid(UTI ~ Comparison) +
  scale_fill_gradient2(low = "#1a9850", mid = "yellow", high = "red3",
                       midpoint = median_hr, name = "% Recurred") +
  labs(x = "Threshold for 'Short Time' Definition",
       y = "Starting Point",
       title = "Likelihood of Recurrence: High-Risk Group",
       subtitle = "            Subsequent Symptomatic Events needed for 'Recurrence' Definition") +
  theme_bw(base_size = 11) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(face = "bold"),
        legend.position = "right")
high_risk_likelihood

# Low-risk recurrence rate
lr_low <- likelihood_df %>% filter(risk_label == "Low Risk")
median_lr <- median(lr_low$pct_recurred, na.rm = TRUE)

low_risk_likelihood <- ggplot(lr_low,
       aes(x = Time_Cutoff_label, y = Starting_Point, fill = pct_recurred)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = sprintf("%.1f%%", pct_recurred)), size = 2.8) +
  facet_grid(UTI ~ Comparison) +
  scale_fill_gradient2(low = "#1a9850", mid = "yellow", high = "red3",
                       midpoint = median_lr, name = "% Recurred") +
  labs(x = "Threshold for 'Short Time' Definition",
       y = "Starting Point",
       title = "Likelihood of Recurrence: Low-Risk Group",
       subtitle = "            Subsequent Symptomatic Events needed for 'Recurrence' Definition") +
  theme_bw(base_size = 11) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(face = "bold"),
        legend.position = "right")
low_risk_likelihood
```

## Combine Heatmap Plots
```{r combine-heatmaps, fig.width=12, fig.height=30, warning=FALSE}
auc_heatmap / sens_heatmap / spec_heatmap / ppv_heatmap / npv_heatmap + plot_layout(axes = "collect")
```


# Save Outputs

```{r save-outputs, warning=FALSE}
# Build comprehensive results CSV with 95% CIs and likelihood of recurrence
csv_output <- all_metrics_combined %>%
  dplyr::select(
    Starting_Point,
    Time_Cutoff_Months,
    UTI,
    Recurrence_Definition = Comparison,
    N,
    N_High_Risk,
    N_Low_Risk,
    AUC_val, AUC_lo, AUC_hi,
    Sensitivity_val, Sensitivity_lo, Sensitivity_hi,
    Specificity_val, Specificity_lo, Specificity_hi,
    PPV_val, PPV_lo, PPV_hi,
    NPV_val, NPV_lo, NPV_hi,
    Likelihood_Recurrence_High_Risk_pct,
    Likelihood_Recurrence_High_Risk_lo,
    Likelihood_Recurrence_High_Risk_hi,
    N_Recurred_High_Risk,
    Likelihood_Recurrence_Low_Risk_pct,
    Likelihood_Recurrence_Low_Risk_lo,
    Likelihood_Recurrence_Low_Risk_hi,
    N_Recurred_Low_Risk
  ) %>%
  # Add formatted display columns for convenience
  mutate(
    AUC_95CI = sprintf("%.3f (%.3f-%.3f)", AUC_val, AUC_lo, AUC_hi),
    Sensitivity_95CI = sprintf("%.3f (%.3f-%.3f)", Sensitivity_val, Sensitivity_lo, Sensitivity_hi),
    Specificity_95CI = sprintf("%.3f (%.3f-%.3f)", Specificity_val, Specificity_lo, Specificity_hi),
    PPV_95CI = sprintf("%.3f (%.3f-%.3f)", PPV_val, PPV_lo, PPV_hi),
    NPV_95CI = sprintf("%.3f (%.3f-%.3f)", NPV_val, NPV_lo, NPV_hi),
    Likelihood_High_Risk_95CI = sprintf("%.1f%% (%.1f-%.1f%%)",
      Likelihood_Recurrence_High_Risk_pct,
      Likelihood_Recurrence_High_Risk_lo,
      Likelihood_Recurrence_High_Risk_hi),
    Likelihood_Low_Risk_95CI = sprintf("%.1f%% (%.1f-%.1f%%)",
      Likelihood_Recurrence_Low_Risk_pct,
      Likelihood_Recurrence_Low_Risk_lo,
      Likelihood_Recurrence_Low_Risk_hi)
  )

write.csv(csv_output, "prognostic_accuracy_grid_search_results.csv",
          row.names = FALSE)

cat("CSV saved with", nrow(csv_output), "rows\n")
csv_output %>%
  dplyr::select(Starting_Point, Time_Cutoff_Months, UTI, Recurrence_Definition,
                N, N_High_Risk, N_Low_Risk,
                AUC_95CI, Sensitivity_95CI, Specificity_95CI,
                PPV_95CI, NPV_95CI,
                Likelihood_High_Risk_95CI, Likelihood_Low_Risk_95CI) %>%
  gt() %>%
  tab_header(title = "Complete Results with 95% Confidence Intervals") %>%
  gt_theme_espn()

# Save index date plots (without UTI)
if (!is.null(roc_index)) ggsave("grid_search_roc_index_date_no_uti.pdf", plot = roc_index, width = 8, height = 6)
if (!is.null(dca_index)) ggsave("grid_search_dca_index_date_no_uti.pdf", plot = dca_index, width = 10, height = 6)
if (!is.null(km_index)) {
  pdf("grid_search_km_index_date_no_uti.pdf", width = 10, height = 7)
  print(km_index)
  dev.off()
}

# Save index date plots (with UTI)
if (!is.null(roc_index_uti)) ggsave("grid_search_roc_index_date_with_uti.pdf", plot = roc_index_uti, width = 8, height = 6)
if (!is.null(dca_index_uti)) ggsave("grid_search_dca_index_date_with_uti.pdf", plot = dca_index_uti, width = 10, height = 6)
if (!is.null(km_index_uti)) {
  pdf("grid_search_km_index_date_with_uti.pdf", width = 10, height = 7)
  print(km_index_uti)
  dev.off()
}

# Save grid search plots
save_grid_plots <- function(results, prefix) {
  for (nm in names(results$roc_plots)) {
    ggsave(paste0("grid_search_roc_", prefix, "_", nm, ".pdf"),
           plot = results$roc_plots[[nm]], width = 8, height = 6)
  }
  for (nm in names(results$km_plots)) {
    pdf(paste0("grid_search_km_", prefix, "_", nm, ".pdf"), width = 10, height = 7)
    print(results$km_plots[[nm]])
    dev.off()
  }
  for (nm in names(results$dca_plots)) {
    ggsave(paste0("grid_search_dca_", prefix, "_", nm, ".pdf"),
           plot = results$dca_plots[[nm]], width = 10, height = 6)
  }
}

save_grid_plots(results_first_no_uti, "first_date_no_uti")
save_grid_plots(results_first_with_uti, "first_date_with_uti")
save_grid_plots(results_second_no_uti, "second_date_no_uti")
save_grid_plots(results_second_with_uti, "second_date_with_uti")
save_grid_plots(results_third_no_uti, "third_date_no_uti")
save_grid_plots(results_third_with_uti, "third_date_with_uti")

# Save heatmaps
if (nrow(heatmap_data) > 0) {
  ggsave("grid_search_heatmap_auc.pdf", plot = auc_heatmap, width = 12, height = 8)
  ggsave("grid_search_heatmap_sensitivity.pdf", plot = sens_heatmap, width = 12, height = 8)
  ggsave("grid_search_heatmap_specificity.pdf", plot = spec_heatmap, width = 12, height = 8)
  ggsave("grid_search_heatmap_ppv.pdf", plot = ppv_heatmap, width = 12, height = 8)
  ggsave("grid_search_heatmap_npv.pdf", plot = npv_heatmap, width = 12, height = 8)
  ggsave("grid_search_heatmap_likelihood_high_risk.pdf", plot = high_risk_likelihood, width = 12, height = 10)
  ggsave("grid_search_heatmap_likelihood_low_risk.pdf", plot = low_risk_likelihood, width = 12, height = 10)
}

cat("All outputs saved.\n")
```
