---
title: "Prognostic Accuracy Grid Search: Starting Points x Recurrence Definitions"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    code_folding: show
---

# Libraries

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(forcats)
library(anytime)
library(pROC)
library(gt)
library(gtExtras)
library(grid)
library(gridExtra)
library(survminer)
library(survival)
library(MatchIt)
library(dcurves)
library(lubridate)
library(rmda)
library(patchwork)
```

# Data Loading

```{r load-data, message=FALSE, warning=FALSE}
diet_data_participant <- read.csv("diet_data_updated__participant.csv",
                                  na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

recurrence_gp_data <- read.csv("gp_data_gp_clinical.csv",
                               na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

recurrence_data_hesin <- read.csv("data_hesin.csv",
                                  na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

recurrence_data_hesin_diag <- read.csv("data_hesin_diag.csv",
                                       na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

recurrence_data_hesin_critical <- read.csv("data_hesin_critical.csv",
                                           na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

recurrence_data_hesin_oper <- read.csv("data_hesin_oper.csv",
                                       na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

icd10_upto196 <- read.csv("icd10_upto196_participant.csv",
                           na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

icd10_morethan196 <- read.csv("icd10_morethan196_participant.csv",
                               na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()

icd10_dates2 <- cbind(icd10_upto196,
                      subset(icd10_morethan196, select = -participant_id)) %>%
  drop_na(diagnoses_icd10)

icd10_data_extra <- read.csv("icd10_extra_participant.csv",
                              na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names() %>%
  subset(select = -c(age_at_recruitment, diagnoses_icd10))

icd9_data <- read.csv("icd9_participant.csv",
                       na.strings = c("", " ", ".", "NA", "N/A", "NULL")) %>%
  as_tibble() %>% clean_names()
```

# Recurrence Identification

```{r identify-recurrence, message=FALSE, warning=FALSE}
source("recurrence_identification_colic_to_colic_multiple_occurrences.R")
```

# Past Medical History

```{r ascertain-pmhx, message=FALSE, warning=FALSE}
source("pmhx_ascertainment_with_dates.R")
```

# Build dates_detailed Object

This uses the episode-based logic from the recurrence identification script.

```{r dates-detailed}
# dates_detailed is already created by the sourced script (line ~1627)
# It contains: participant_id, index_date, first_date, second_date, third_date,
#              fourth_date, fifth_date, n_recurrences, mean_time_between

# Also compute pairwise inter-event times in months
dates_detailed <- dates_detailed %>%
  mutate(
    gap_index_to_first_months  = as.numeric(first_date  - index_date)  / 30.44,
    gap_first_to_second_months = as.numeric(second_date - first_date)  / 30.44,
    gap_second_to_third_months = as.numeric(third_date  - second_date) / 30.44
  )

head(dates_detailed)
```

# Date of Birth Lookup

```{r dob-lookup}
dob_df <- diet_data_participant %>%
  mutate(dob = as.Date(paste("1", month_of_birth, year_of_birth, sep = " - "),
                       format = "%d - %m - %Y")) %>%
  dplyr::select(participant_id, dob)
```

# Age at First Stone (kept for reference / backward compatibility)

```{r age-first-stone}
age_at_first_stone_df <- dates_detailed %>%
  dplyr::select(participant_id, index_date) %>%
  left_join(dob_df, by = "participant_id") %>%
  mutate(age_at_first_stone = as.numeric((index_date - dob) / 365.25)) %>%
  dplyr::select(participant_id, age_at_first_stone)
```

# EAU High-Risk Classification Function

This function creates the high-risk classification for a given starting point.
Age < 25 is evaluated **at the relevant starting date**
```{r high-risk-fn}
# EAU risk factor columns
eau_risk_cols <- c("metabolic_disorder", "metabolic_syndrome", "hyperpth",
                   "immunosuppression", "transplant_immunosuppression",
                   "pkd", "msk", "bowel_surgery", "ibd", "malabsorption",
                   "sarcoidosis", "spinal_injury", "cf", "pujo", "diverticulum",
                   "ureteric_stricture", "vur", "single_kidney",
                   "ileal_conduit", "eating_disorder", "horshoe_kidney")

build_high_risk_df <- function(starting_point_col) {

  # Pick the relevant date column for computing age at start
  ref_dates <- dates_detailed %>%
    dplyr::select(participant_id, ref_date = !!sym(starting_point_col)) %>%
    filter(!is.na(ref_date)) %>%
    distinct(participant_id, .keep_all = TRUE)

  # Compute age at the starting-point date
  age_at_start <- ref_dates %>%
    left_join(dob_df, by = "participant_id") %>%
    mutate(age_at_start = as.numeric((ref_date - dob) / 365.25)) %>%
    dplyr::select(participant_id, age_at_start)

  # Choose which risk factor columns to use
  risk_cols <- eau_risk_cols

  hr <- dates_detailed %>%
    dplyr::select(participant_id) %>%
    distinct() %>%
    left_join(pmhx_cleaned, by = "participant_id") %>%
    mutate(across(any_of(risk_cols), ~replace_na(., 0))) %>%
    mutate(
      risk_sum = rowSums(across(any_of(risk_cols)), na.rm = TRUE),
      high_risk = if_else(risk_sum < 1, "low_risk", "high_risk")
    ) %>%
    dplyr::select(participant_id, high_risk) %>%
    left_join(age_at_start, by = "participant_id") %>%
    mutate(high_risk = case_when(age_at_start < 25 ~ "high_risk", TRUE ~ high_risk)) %>%
    group_by(participant_id) %>%
    summarise(high_risk = if_else(any(high_risk == "high_risk"), "high_risk", "low_risk"),
              .groups = "drop")

  return(hr)
}

# Preview: index_date version
table(build_high_risk_df("index_date")$high_risk)
```

# Grid Search Configuration

```{r grid-config}
# Starting points
starting_points <- c("index_date", "first_date", "second_date", "third_date")

# Recurrence thresholds (subsequent events from starting point)
recurrence_thresholds <- c(1, 2, 3)
recurrence_labels <- c("\u22651 subsequent stone events", "\u22652 subsequent stone events", "\u22653 subsequent stone events")

# Inter-event time cut-offs in months (for first_date onwards analyses)
time_cutoffs_months <- seq(6, 24, by = 3)

# Follow-up horizon (5 years)
follow_up_years <- 5

colors_rec <- c("#1b9e77", "#d95f02", "#7570b3")
```

# Helper: Build Analysis Dataset for a Given Starting Point

```{r build-dataset-fn}
build_analysis_dataset <- function(starting_point_col,
                                   inter_event_cutoff_months = NULL) {

  # Get the starting date and count subsequent events
  ds <- dates_detailed %>%
    dplyr::select(participant_id, index_date, first_date, second_date, third_date,
                  fourth_date, fifth_date, n_recurrences, mean_time_between,
                  gap_index_to_first_months, gap_first_to_second_months,
                  gap_second_to_third_months) %>%
    mutate(start_date = !!sym(starting_point_col))

  # Remove participants without a valid starting date

  ds <- ds %>% filter(!is.na(start_date))

  # Count subsequent events (episodes after the starting point, >6 months apart)
  # We already have episode dates in dates_detailed, so count how many fall after start_date
  ds <- ds %>%
    mutate(
      subsequent_events = case_when(
        starting_point_col == "index_date" ~ n_recurrences,
        starting_point_col == "first_date" ~ pmax(n_recurrences - 1L, 0L),
        starting_point_col == "second_date" ~ pmax(n_recurrences - 2L, 0L),
        starting_point_col == "third_date" ~ pmax(n_recurrences - 3L, 0L)
      )
    )

  # Get follow-up info
  last_date_df <- overall_follow_up %>% dplyr::select(participant_id, last_date)

  ds <- ds %>%
    left_join(last_date_df, by = "participant_id") %>%
    drop_na(last_date)

  # Compute time to next event from start_date (for KM)
  # Include ALL patients: recurrers are events, non-recurrers are censored at

  # their last follow-up (or follow_up_years, whichever is shorter).
  # Also compute total follow-up from start_date for use in ROC exclusion logic.
  ds <- ds %>%
    mutate(
      next_event_date = case_when(
        starting_point_col == "index_date" ~ first_date,
        starting_point_col == "first_date" ~ second_date,
        starting_point_col == "second_date" ~ third_date,
        starting_point_col == "third_date" ~ fourth_date
      ),
      has_next_event = as.integer(!is.na(next_event_date)),
      # Total follow-up from start date (used for filtering in binary analyses)
      follow_up_from_start_years = as.numeric(last_date - start_date) / 365.25,
      # Time to event or censoring
      time_to_next_years = if_else(
        has_next_event == 1L,
        as.numeric(next_event_date - start_date) / 365.25,
        as.numeric(last_date - start_date) / 365.25
      )
    ) %>%
    filter(time_to_next_years > 0)

  # Add high-risk classification (age assessed at this starting point)
  hr_df <- build_high_risk_df(starting_point_col)
  ds <- ds %>%
    left_join(hr_df, by = "participant_id") %>%
    left_join(age_at_first_stone_df, by = "participant_id")

  # Add initial presentation from first_presentation
  ds <- ds %>%
    left_join(first_presentation %>% dplyr::select(participant_id, initial_presentation),
              by = "participant_id")

  # For first_date onwards: add inter-event time-based high-risk modifier
  if (!is.null(inter_event_cutoff_months) && starting_point_col != "index_date") {
    # Get the gap leading into the starting point
    gap_col <- case_when(
      starting_point_col == "first_date"  ~ "gap_index_to_first_months",
      starting_point_col == "second_date" ~ "gap_first_to_second_months",
      starting_point_col == "third_date"  ~ "gap_second_to_third_months"
    )

    ds <- ds %>%
      mutate(
        prior_gap_months = !!sym(gap_col),
        high_risk_with_time = case_when(
          high_risk == "high_risk" ~ "high_risk",
          !is.na(prior_gap_months) & prior_gap_months <= inter_event_cutoff_months ~ "high_risk",
          TRUE ~ "low_risk"
        )
      )
  } else {
    ds <- ds %>%
      mutate(high_risk_with_time = high_risk)
  }

  return(ds)
}
```

# Helper Functions for Analysis

```{r helper-functions}
prep_roc_grid <- function(ds, thresh, risk_col = "high_risk_with_time") {
  # For binary classification (ROC/PPV/NPV etc.):
  #   - Recurrers (subsequent_events >= thresh): always included (actual = 1)
  #   - Non-recurrers WITH >= follow_up_years follow-up: included (actual = 0)
  #   - Non-recurrers WITHOUT follow_up_years follow-up: EXCLUDED (ambiguous)
  ds %>%
    mutate(
      actual = case_when(
        subsequent_events >= thresh ~ 1L,
        subsequent_events < thresh & follow_up_from_start_years >= follow_up_years ~ 0L,
        TRUE ~ NA_integer_
      ),
      predicted = if_else(!!sym(risk_col) == "high_risk", 1, 0)
    ) %>%
    drop_na(actual, predicted)
}

extract_metrics_grid <- function(roc_obj, label, roc_data = NULL) {
  auc_val <- as.numeric(auc(roc_obj))
  auc_ci  <- ci.auc(roc_obj)
  coords_best <- coords(roc_obj, "best", ret = c("sensitivity", "specificity"),
                        best.method = "youden")

  # Contingency table counts & derived metrics with Wilson CIs
  tp <- fp <- tn <- fn <- NA_integer_
  ppv_val <- npv_val <- sens_val <- spec_val <- NA_real_
  ppv_lo <- ppv_hi <- npv_lo <- npv_hi <- NA_real_
  sens_lo <- sens_hi <- spec_lo <- spec_hi <- NA_real_
  n_total <- n_high_risk <- n_low_risk <- NA_integer_
  n_recurred_high <- n_recurred_low <- NA_integer_
  pct_recurred_high <- pct_recurred_low <- NA_real_
  pct_recurred_high_lo <- pct_recurred_high_hi <- NA_real_
  pct_recurred_low_lo  <- pct_recurred_low_hi  <- NA_real_

  sens_val <- coords_best$sensitivity
  spec_val <- coords_best$specificity

  if (!is.null(roc_data)) {
    tp <- sum(roc_data$predicted == 1 & roc_data$actual == 1)
    fp <- sum(roc_data$predicted == 1 & roc_data$actual == 0)
    tn <- sum(roc_data$predicted == 0 & roc_data$actual == 0)
    fn <- sum(roc_data$predicted == 0 & roc_data$actual == 1)
    n_total <- nrow(roc_data)

    ppv_val <- tp / (tp + fp)
    npv_val <- tn / (tn + fn)

    # Wilson score 95% CIs for proportions
    wilson_ci <- function(x, n) {
      if (n == 0) return(c(NA_real_, NA_real_))
      bt <- binom.test(x, n)
      # Use exact Clopper-Pearson from binom.test
      as.numeric(bt$conf.int)
    }

    # Sensitivity CI:  TP / (TP + FN)
    sens_ci <- wilson_ci(tp, tp + fn)
    sens_lo <- sens_ci[1]; sens_hi <- sens_ci[2]

    # Specificity CI:  TN / (TN + FP)
    spec_ci <- wilson_ci(tn, tn + fp)
    spec_lo <- spec_ci[1]; spec_hi <- spec_ci[2]

    # PPV CI:  TP / (TP + FP)
    ppv_ci <- wilson_ci(tp, tp + fp)
    ppv_lo <- ppv_ci[1]; ppv_hi <- ppv_ci[2]

    # NPV CI:  TN / (TN + FN)
    npv_ci <- wilson_ci(tn, tn + fn)
    npv_lo <- npv_ci[1]; npv_hi <- npv_ci[2]

    # Likelihood of recurrence by risk group
    n_high_risk     <- tp + fp
    n_low_risk      <- tn + fn
    n_recurred_high <- tp
    n_recurred_low  <- fn

    pct_recurred_high <- if (n_high_risk > 0) tp / n_high_risk * 100 else NA_real_
    pct_recurred_low  <- if (n_low_risk > 0)  fn / n_low_risk  * 100 else NA_real_

    if (n_high_risk > 0) {
      hr_ci <- wilson_ci(tp, n_high_risk)
      pct_recurred_high_lo <- hr_ci[1] * 100; pct_recurred_high_hi <- hr_ci[2] * 100
    }
    if (n_low_risk > 0) {
      lr_ci <- wilson_ci(fn, n_low_risk)
      pct_recurred_low_lo <- lr_ci[1] * 100; pct_recurred_low_hi <- lr_ci[2] * 100
    }
  }

  # Return both display-formatted and raw numeric columns
  data.frame(
    Comparison = label,
    N = n_total,
    N_High_Risk = n_high_risk,
    N_Low_Risk = n_low_risk,
    AUC = sprintf("%.3f (%.3f\u2013%.3f)", auc_val, auc_ci[1], auc_ci[3]),
    AUC_val = auc_val,
    AUC_lo = as.numeric(auc_ci[1]),
    AUC_hi = as.numeric(auc_ci[3]),
    Sensitivity = sprintf("%.3f (%.3f\u2013%.3f)", sens_val, sens_lo, sens_hi),
    Sensitivity_val = sens_val,
    Sensitivity_lo = sens_lo,
    Sensitivity_hi = sens_hi,
    Specificity = sprintf("%.3f (%.3f\u2013%.3f)", spec_val, spec_lo, spec_hi),
    Specificity_val = spec_val,
    Specificity_lo = spec_lo,
    Specificity_hi = spec_hi,
    PPV = sprintf("%.3f (%.3f\u2013%.3f)", ppv_val, ppv_lo, ppv_hi),
    PPV_val = ppv_val,
    PPV_lo = ppv_lo,
    PPV_hi = ppv_hi,
    NPV = sprintf("%.3f (%.3f\u2013%.3f)", npv_val, npv_lo, npv_hi),
    NPV_val = npv_val,
    NPV_lo = npv_lo,
    NPV_hi = npv_hi,
    Likelihood_Recurrence_High_Risk_pct = pct_recurred_high,
    Likelihood_Recurrence_High_Risk_lo = pct_recurred_high_lo,
    Likelihood_Recurrence_High_Risk_hi = pct_recurred_high_hi,
    N_Recurred_High_Risk = n_recurred_high,
    Likelihood_Recurrence_Low_Risk_pct = pct_recurred_low,
    Likelihood_Recurrence_Low_Risk_lo = pct_recurred_low_lo,
    Likelihood_Recurrence_Low_Risk_hi = pct_recurred_low_hi,
    N_Recurred_Low_Risk = n_recurred_low,
    stringsAsFactors = FALSE
  )
}

generate_roc_plot_grid <- function(ds, plot_title, risk_col = "high_risk_with_time") {
  roc_combined_df <- data.frame()
  ci_combined_df <- data.frame()
  auc_table_df <- data.frame()

  for (i in seq_along(recurrence_thresholds)) {
    thresh <- recurrence_thresholds[i]
    label <- recurrence_labels[i]

    roc_data <- prep_roc_grid(ds, thresh, risk_col)
    if (nrow(roc_data) < 10 || length(unique(roc_data$actual)) < 2) next

    roc_obj <- roc(roc_data$actual, roc_data$predicted, quiet = TRUE)

    roc_combined_df <- rbind(roc_combined_df, data.frame(
      fpr = 1 - roc_obj$specificities,
      tpr = roc_obj$sensitivities,
      Comparison = label
    ))

    ci_se <- ci.se(roc_obj, specificities = seq(0, 1, length.out = 100))
    ci_combined_df <- rbind(ci_combined_df, data.frame(
      fpr = 1 - as.numeric(rownames(ci_se)),
      tpr_lower = ci_se[, 1],
      tpr_upper = ci_se[, 3],
      Comparison = label
    ))

    auc_val <- as.numeric(auc(roc_obj))
    auc_ci <- ci.auc(roc_obj)
    auc_table_df <- rbind(auc_table_df, data.frame(
      Comparison = label,
      AUC_CI = sprintf("%.2f (%.2f\u2013%.2f)", auc_val, auc_ci[1], auc_ci[3])
    ))
  }

  if (nrow(roc_combined_df) == 0) return(NULL)

  auc_table <- tableGrob(auc_table_df, rows = NULL, theme = ttheme_minimal(base_size = 9))
  auc_table_boxed <- grobTree(
    rectGrob(gp = gpar(col = "black", fill = "white", lwd = 1)),
    auc_table
  )

  ggplot() +
    geom_ribbon(data = ci_combined_df,
                aes(x = fpr, ymin = tpr_lower, ymax = tpr_upper, fill = Comparison),
                alpha = 0.2) +
    geom_line(data = roc_combined_df,
              aes(x = fpr, y = tpr, color = Comparison), linewidth = 1) +
    geom_abline(linetype = "dashed", alpha = 0.6) +
    labs(x = "False Positive Rate", y = "True Positive Rate", title = plot_title) +
    scale_color_manual(values = colors_rec) +
    scale_fill_manual(values = colors_rec) +
    coord_equal() +
    theme_bw(base_size = 12) +
    theme(legend.position = "bottom") +
    annotation_custom(grob = auc_table_boxed,
                      xmin = 0.55, xmax = 1, ymin = 0.05, ymax = 0.3)
}

generate_km_plot_grid <- function(ds, plot_title, risk_col = "high_risk_with_time") {
  km_data <- ds %>%
    rename(risk_group = !!sym(risk_col)) %>%
    filter(!is.na(time_to_next_years), !is.na(risk_group)) %>%
    mutate(recurrence = has_next_event)

  if (nrow(km_data) < 10 || length(unique(km_data$risk_group)) < 2) return(NULL)

  km_fit <- surv_fit(Surv(time_to_next_years, recurrence) ~ risk_group, data = km_data)

  ggsurvplot(
    km_fit,
    data = km_data,
    censor = FALSE, risk.table = TRUE, surv.median.line = "hv",
    conf.int = TRUE, tables.theme = theme_cleantable(),
    break.time.by = 1, xlab = "Time (years)", xlim = c(0, 10),
    title = plot_title, pval = TRUE,
    legend.title = "Risk Status", legend.labs = c("High Risk", "Low Risk"),
    ggtheme = theme_bw()
  )
}

generate_dca_plot_grid <- function(ds, plot_title, risk_col = "high_risk_with_time") {
  dca_list <- lapply(seq_along(recurrence_thresholds), function(i) {
    thresh <- recurrence_thresholds[i]

    dca_data <- ds %>%
      mutate(
        actual = case_when(
          subsequent_events >= thresh ~ 1L,
          subsequent_events == 0L ~ 0L,
          TRUE ~ NA_integer_
        ),
        risk_binary = case_when(
          !!sym(risk_col) == "low_risk" ~ 0,
          !!sym(risk_col) == "high_risk" ~ 1,
          TRUE ~ NA_real_)
      ) %>%
      drop_na(actual, risk_binary)

    if (nrow(dca_data) < 10 || length(unique(dca_data$actual)) < 2) return(NULL)

    dca(actual ~ risk_binary, data = dca_data, thresholds = seq(0, 0.8, by = 0.01))
  })

  dca_list <- dca_list[!sapply(dca_list, is.null)]
  if (length(dca_list) == 0) return(NULL)

  labels_used <- recurrence_labels[seq_along(dca_list)]

  combined_df <- lapply(seq_along(dca_list), function(i) {
    p <- plot(dca_list[[i]])
    p$data %>% mutate(comparison = labels_used[i])
  }) %>% bind_rows()

  ggplot(combined_df, aes(x = threshold, y = net_benefit, colour = label)) +
    geom_line(linewidth = 0.8) +
    facet_wrap(~ comparison, ncol = 3) +
    labs(x = "Probability of Recurrence Threshold",
         y = "Net Benefit", colour = NULL, title = plot_title) +
    theme_bw(base_size = 12) +
    theme(legend.position = "bottom") +
    scale_colour_discrete(labels = c("Follow-up All", "Follow-up None", "Risk Status")) +
    xlim(c(0, 0.6)) +
    geom_vline(xintercept = 0.2, linetype = "dashed")
}
```

# Analysis 1: Index Date (EAU Risk Only)

## From Index Date (1st Stone Event)
```{r analysis-index, fig.width=10, fig.height=8, warning=FALSE, message=FALSE}
ds_index <- build_analysis_dataset("index_date")

cat("N participants from index_date:", nrow(ds_index), "\n")
table(ds_index$subsequent_events)
```

### ROC Curves
```{r roc-index, fig.width=8, fig.height=6, warning=FALSE}
roc_index <- generate_roc_plot_grid(ds_index, "ROC: From Index Date (EAU Risk)")
roc_index
```

### Kaplan-Meier
```{r km-index, fig.width=10, fig.height=7, warning=FALSE}
km_index <- generate_km_plot_grid(ds_index, "KM: From Index Date (EAU Risk)")
km_index
```

### Decision Curve Analysis
```{r dca-index, fig.width=10, fig.height=6, warning=FALSE}
dca_index <- generate_dca_plot_grid(ds_index, "DCA: From Index Date (EAU Risk)")
dca_index
```

### Metrics Table
```{r metrics-index, warning=FALSE}
metrics_index <- lapply(seq_along(recurrence_thresholds), function(i) {
  roc_data <- prep_roc_grid(ds_index, recurrence_thresholds[i])
  if (nrow(roc_data) < 10 || length(unique(roc_data$actual)) < 2) return(NULL)
  roc_obj <- roc(roc_data$actual, roc_data$predicted, quiet = TRUE)
  extract_metrics_grid(roc_obj, recurrence_labels[i], roc_data) %>%
    mutate(Starting_Point = "Index Date", Time_Cutoff_Months = NA_real_)
}) %>% bind_rows()

metrics_index %>% gt() %>% gt_theme_espn()
```

## From First Date (1st Recurrence)

```{r grid-first, fig.width=10, fig.height=8, warning=FALSE, message=FALSE, results='asis'}
results_first <- run_grid_search("first_date", "Second Event")

cat("\n### Metrics Summary\n")
if (nrow(results_first$metrics) > 0) {
  print(
    results_first$metrics %>%
      gt() %>%
      tab_header(title = "Prognostic Accuracy: From Second Event ") %>%
      gt_theme_espn()
  )
}
```

### ROC Curves - First Date 
```{r roc-first, fig.width=8, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_first$roc_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_first$roc_plots[[nm]])
  cat("\n")
}
```

### Kaplan-Meier - First Date 
```{r km-first, fig.width=10, fig.height=7, warning=FALSE, results='asis'}
for (nm in names(results_first$km_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_first$km_plots[[nm]])
  cat("\n")
}
```

### DCA - First Date 
```{r dca-first, fig.width=10, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_first$dca_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_first$dca_plots[[nm]])
  cat("\n")
}
```

## From Second Date (2nd Recurrence)

```{r grid-second, fig.width=10, fig.height=8, warning=FALSE, message=FALSE, results='asis'}
results_second <- run_grid_search("second_date", "Third Event")

cat("\n### Metrics Summary\n")
if (nrow(results_second$metrics) > 0) {
  print(
    results_second$metrics %>%
      gt() %>%
      tab_header(title = "Prognostic Accuracy: From Third Event ") %>%
      gt_theme_espn()
  )
}
```

### ROC Curves - Second Date 
```{r roc-second, fig.width=8, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_second$roc_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_second$roc_plots[[nm]])
  cat("\n")
}
```

### Kaplan-Meier - Second Date 
```{r km-second, fig.width=10, fig.height=7, warning=FALSE, results='asis'}
for (nm in names(results_second$km_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_second$km_plots[[nm]])
  cat("\n")
}
```

### DCA - Second Date 
```{r dca-second, fig.width=10, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_second$dca_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_second$dca_plots[[nm]])
  cat("\n")
}
```

## From Third Date (3rd Recurrence)

```{r grid-third, fig.width=10, fig.height=8, warning=FALSE, message=FALSE, results='asis'}
results_third <- run_grid_search("third_date", "Fourth Event")

cat("\n### Metrics Summary\n")
if (nrow(results_third$metrics) > 0) {
  print(
    results_third$metrics %>%
      gt() %>%
      tab_header(title = "Prognostic Accuracy: From Fourth Event ") %>%
      gt_theme_espn()
  )
}
```

### ROC Curves - Third Date 
```{r roc-third, fig.width=8, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_third$roc_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_third$roc_plots[[nm]])
  cat("\n")
}
```

### Kaplan-Meier - Third Date 
```{r km-third, fig.width=10, fig.height=7, warning=FALSE, results='asis'}
for (nm in names(results_third$km_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_third$km_plots[[nm]])
  cat("\n")
}
```

### DCA - Third Date 
```{r dca-third, fig.width=10, fig.height=6, warning=FALSE, results='asis'}
for (nm in names(results_third$dca_plots)) {
  cat("\n####", gsub("cutoff_", "Gap Cut-off: ", nm), "months\n")
  print(results_third$dca_plots[[nm]])
  cat("\n")
}
```

## AUC

```{r heatmap, fig.width=12, fig.height=8, warning=FALSE}
# Parse AUC values for heatmap
heatmap_data <- all_metrics_combined %>%
  filter(!is.na(Time_Cutoff_Months), Starting_Point != "Index Date") %>%
  mutate(
    AUC_numeric = AUC_val,
    Time_Cutoff_label = paste0("\u2264", Time_Cutoff_Months, "mo")
  ) %>%
  mutate(
    Time_Cutoff_label = factor(Time_Cutoff_label,
                               levels = c(
                                 "≤6mo",
                                  "≤9mo",
                                 "≤12mo",
                                 "≤15mo",
                                 "≤18mo",
                                 "≤21mo",
                                 "≤24mo"
                               )),
    Starting_Point = case_when(
      Starting_Point == "Second Event" ~ "Second Symptomatic Episode",
      Starting_Point == "Third Event" ~ "Third Symptomatic Episode",
      Starting_Point == "Fourth Event" ~ "Fourth Symptomatic Episode"
    ) %>% factor(levels = c("Fourth Symptomatic Episode",
                            "Third Symptomatic Episode",
                            "Second Symptomatic Episode")),
    Comparison = factor(Comparison, levels = c("\u22651 subsequent stone events",
                                               "\u22652 subsequent stone events",
                                               "\u22653 subsequent stone events"))
  )

median_auc <- median(heatmap_data$AUC_numeric)
min_auc <- min(heatmap_data$AUC_numeric)
max_auc <- max(heatmap_data$AUC_numeric)

if (nrow(heatmap_data) > 0) {
  auc_heatmap <- ggplot(heatmap_data,
         aes(x = Time_Cutoff_label, y = Starting_Point, fill = AUC_numeric)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(aes(label = sprintf("%.2f", AUC_numeric)), size = 3) +
    facet_wrap(~ Comparison, nrow = 1) +
    scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                         midpoint = median_auc, name = "AUC", limits = c(min_auc, max_auc)) +
    labs(x = "Threshold for 'Short Time' Definition",
         y = "Starting Point",
         title = "AUC",
         subtitle = "            Subsequent Symptomatic Events needed for 'Recurrence' Definition") +
    theme_bw(base_size = 11) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "bold"),
          legend.position = "right")
}
auc_heatmap
```

## Sensitivity
```{r}
median_sens <- median(heatmap_data$Sensitivity_val, na.rm = TRUE)
min_sens <- min(heatmap_data$Sensitivity_val, na.rm = TRUE)
max_sens <- max(heatmap_data$Sensitivity_val, na.rm = TRUE)

if (nrow(heatmap_data) > 0) {
  sens_heatmap <- ggplot(heatmap_data,
         aes(x = Time_Cutoff_label, y = Starting_Point, fill = Sensitivity_val)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(aes(label = sprintf("%.2f", Sensitivity_val)), size = 3) +
    facet_wrap(~ Comparison, nrow = 1) +
    scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                         midpoint = median_sens, name = "Sensitivity", limits = c(min_sens, max_sens)) +
    labs(x = "Threshold for 'Short Time' Definition",
         y = "Starting Point",
         title = "Sensitivity",
         subtitle = "            Subsequent Symptomatic Events needed for 'Recurrence' Definition") +
    theme_bw(base_size = 11) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "bold"),
          legend.position = "right")
}
sens_heatmap
```


## Specificity
```{r}
median_spec <- median(heatmap_data$Specificity_val, na.rm = TRUE)
min_spec <- min(heatmap_data$Specificity_val, na.rm = TRUE)
max_spec <- max(heatmap_data$Specificity_val, na.rm = TRUE)

if (nrow(heatmap_data) > 0) {
  spec_heatmap <- ggplot(heatmap_data,
         aes(x = Time_Cutoff_label, y = Starting_Point, fill = Specificity_val)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(aes(label = sprintf("%.2f", Specificity_val)), size = 3) +
    facet_wrap(~ Comparison, nrow = 1) +
    scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                         midpoint = median_spec, name = "Specificity", limits = c(min_spec, max_spec)) +
    labs(x = "Threshold for 'Short Time' Definition",
         y = "Starting Point",
         title = "Specificity",
         subtitle = "            Subsequent Symptomatic Events needed for 'Recurrence' Definition") +
    theme_bw(base_size = 11) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "bold"),
          legend.position = "right")
}
spec_heatmap
```

## PPV
```{r heatmap-ppv, fig.width=12, fig.height=8, warning=FALSE}
median_ppv <- median(heatmap_data$PPV_val, na.rm = TRUE)
min_ppv <- min(heatmap_data$PPV_val, na.rm = TRUE)
max_ppv <- max(heatmap_data$PPV_val, na.rm = TRUE)

if (nrow(heatmap_data) > 0) {
  ppv_heatmap <- ggplot(heatmap_data,
         aes(x = Time_Cutoff_label, y = Starting_Point, fill = PPV_val)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(aes(label = sprintf("%.2f", PPV_val)), size = 3) +
    facet_wrap(~ Comparison, nrow = 1) +
    scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                         midpoint = median_ppv, name = "PPV", limits = c(min_ppv, max_ppv)) +
    labs(x = "Threshold for 'Short Time' Definition",
         y = "Starting Point",
         title = "Positive Predictive Value",
         subtitle = "            Subsequent Symptomatic Events needed for 'Recurrence' Definition") +
    theme_bw(base_size = 11) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "bold"),
          legend.position = "right")
}
ppv_heatmap
```

## NPV
```{r heatmap-npv, fig.width=12, fig.height=8, warning=FALSE}
median_npv <- median(heatmap_data$NPV_val, na.rm = TRUE)
min_npv <- min(heatmap_data$NPV_val, na.rm = TRUE)
max_npv <- max(heatmap_data$NPV_val, na.rm = TRUE)

if (nrow(heatmap_data) > 0) {
  npv_heatmap <- ggplot(heatmap_data,
         aes(x = Time_Cutoff_label, y = Starting_Point, fill = NPV_val)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(aes(label = sprintf("%.2f", NPV_val)), size = 3) +
    facet_wrap(~ Comparison, nrow = 1) +
    scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                         midpoint = median_npv, name = "NPV", limits = c(min_npv, max_npv)) +
    labs(x = "Threshold for 'Short Time' Definition",
         y = "Starting Point",
         title = "Negative Predictive Value",
         subtitle = "            Subsequent Symptomatic Events needed for 'Recurrence' Definition") +
    theme_bw(base_size = 11) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "bold"),
          legend.position = "right")
}
npv_heatmap
```

## Likelihood of Recurrence by Risk Group

This heatmap shows the proportion of participants in each risk group who
experienced recurrence, across all grid-search combinations.

```{r likelihood-heatmap, fig.width=12, fig.height=10, warning=FALSE, message=FALSE}
# Build likelihood data across all grid-search combinations (excluding index date)
likelihood_rows <- list()

for (sp_col in c("first_date", "second_date", "third_date")) {
  sp_label <- switch(sp_col,
                     first_date  = "Second Event",
                     second_date = "Third Event",
                     third_date  = "Fourth Event")

  for (cutoff in time_cutoffs_months) {
      ds <- build_analysis_dataset(sp_col, inter_event_cutoff_months = cutoff)
      if (nrow(ds) < 20) next

      for (i in seq_along(recurrence_thresholds)) {
        thresh <- recurrence_thresholds[i]
        label  <- recurrence_labels[i]

        tmp <- ds %>%
          mutate(recurred = as.integer(subsequent_events >= thresh)) %>%
          group_by(high_risk_with_time) %>%
          summarise(n = n(),
                    n_recurred = sum(recurred, na.rm = TRUE),
                    .groups = "drop") %>%
          mutate(
            pct_recurred = n_recurred / n * 100,
            Starting_Point = sp_label,
            Time_Cutoff_Months = cutoff,
            Comparison = label,
            
          )
        likelihood_rows <- c(likelihood_rows, list(tmp))
      }
    }
  }
}

likelihood_df <- bind_rows(likelihood_rows) %>%
  mutate(
    Time_Cutoff_label = paste0("\u2264", Time_Cutoff_Months, "mo"),
    Time_Cutoff_label = factor(Time_Cutoff_label,
                               levels = c("\u22646mo", "\u22649mo", "\u226412mo",
                                          "\u226415mo", "\u226418mo", "\u226421mo",
                                          "\u226424mo")),
    Starting_Point = factor(Starting_Point,
                            levels = c("Fourth Event",
                                       "Third Event",
                                       "Second Event")),
    Comparison = factor(Comparison, levels = recurrence_labels),
    risk_label = case_when(
      high_risk_with_time == "high_risk" ~ "High Risk",
      high_risk_with_time == "low_risk"  ~ "Low Risk"
    )
  )

# High-risk recurrence rate
lr_high <- likelihood_df %>% filter(risk_label == "High Risk")
median_hr <- median(lr_high$pct_recurred, na.rm = TRUE)

high_risk_likelihood <- ggplot(lr_high,
       aes(x = Time_Cutoff_label, y = Starting_Point, fill = pct_recurred)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = sprintf("%.1f%%", pct_recurred)), size = 2.8) +
  facet_wrap(~ Comparison, nrow = 1) +
  scale_fill_gradient2(low = "#1a9850", mid = "yellow", high = "red3",
                       midpoint = median_hr, name = "% Recurred") +
  labs(x = "Threshold for 'Short Time' Definition",
       y = "Starting Point",
       title = "Likelihood of Recurrence: High-Risk Group",
       subtitle = "            Subsequent Symptomatic Events needed for 'Recurrence' Definition") +
  theme_bw(base_size = 11) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(face = "bold"),
        legend.position = "right")
high_risk_likelihood

# Low-risk recurrence rate
lr_low <- likelihood_df %>% filter(risk_label == "Low Risk")
median_lr <- median(lr_low$pct_recurred, na.rm = TRUE)

low_risk_likelihood <- ggplot(lr_low,
       aes(x = Time_Cutoff_label, y = Starting_Point, fill = pct_recurred)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = sprintf("%.1f%%", pct_recurred)), size = 2.8) +
  facet_wrap(~ Comparison, nrow = 1) +
  scale_fill_gradient2(low = "#1a9850", mid = "yellow", high = "red3",
                       midpoint = median_lr, name = "% Recurred") +
  labs(x = "Threshold for 'Short Time' Definition",
       y = "Starting Point",
       title = "Likelihood of Recurrence: Low-Risk Group",
       subtitle = "            Subsequent Symptomatic Events needed for 'Recurrence' Definition") +
  theme_bw(base_size = 11) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(face = "bold"),
        legend.position = "right")
low_risk_likelihood
```

## Combine Heatmap Plots
```{r combine-heatmaps, fig.width=12, fig.height=30, warning=FALSE}
auc_heatmap / sens_heatmap / spec_heatmap / ppv_heatmap / npv_heatmap + plot_layout(axes = "collect")
```


# Save Outputs

```{r save-outputs, warning=FALSE}
# Build comprehensive results CSV with 95% CIs and likelihood of recurrence
csv_output <- all_metrics_combined %>%
  dplyr::select(
    Starting_Point,
    Time_Cutoff_Months,
    Recurrence_Definition = Comparison,
    N,
    N_High_Risk,
    N_Low_Risk,
    AUC_val, AUC_lo, AUC_hi,
    Sensitivity_val, Sensitivity_lo, Sensitivity_hi,
    Specificity_val, Specificity_lo, Specificity_hi,
    PPV_val, PPV_lo, PPV_hi,
    NPV_val, NPV_lo, NPV_hi,
    Likelihood_Recurrence_High_Risk_pct,
    Likelihood_Recurrence_High_Risk_lo,
    Likelihood_Recurrence_High_Risk_hi,
    N_Recurred_High_Risk,
    Likelihood_Recurrence_Low_Risk_pct,
    Likelihood_Recurrence_Low_Risk_lo,
    Likelihood_Recurrence_Low_Risk_hi,
    N_Recurred_Low_Risk
  ) %>%
  # Add formatted display columns for convenience
  mutate(
    AUC_95CI = sprintf("%.3f (%.3f-%.3f)", AUC_val, AUC_lo, AUC_hi),
    Sensitivity_95CI = sprintf("%.3f (%.3f-%.3f)", Sensitivity_val, Sensitivity_lo, Sensitivity_hi),
    Specificity_95CI = sprintf("%.3f (%.3f-%.3f)", Specificity_val, Specificity_lo, Specificity_hi),
    PPV_95CI = sprintf("%.3f (%.3f-%.3f)", PPV_val, PPV_lo, PPV_hi),
    NPV_95CI = sprintf("%.3f (%.3f-%.3f)", NPV_val, NPV_lo, NPV_hi),
    Likelihood_High_Risk_95CI = sprintf("%.1f%% (%.1f-%.1f%%)",
      Likelihood_Recurrence_High_Risk_pct,
      Likelihood_Recurrence_High_Risk_lo,
      Likelihood_Recurrence_High_Risk_hi),
    Likelihood_Low_Risk_95CI = sprintf("%.1f%% (%.1f-%.1f%%)",
      Likelihood_Recurrence_Low_Risk_pct,
      Likelihood_Recurrence_Low_Risk_lo,
      Likelihood_Recurrence_Low_Risk_hi)
  )

write.csv(csv_output, "prognostic_accuracy_grid_search_results.csv",
          row.names = FALSE)

cat("CSV saved with", nrow(csv_output), "rows\n")
csv_output %>%
  dplyr::select(Starting_Point, Time_Cutoff_Months, Recurrence_Definition,
                N, N_High_Risk, N_Low_Risk,
                AUC_95CI, Sensitivity_95CI, Specificity_95CI,
                PPV_95CI, NPV_95CI,
                Likelihood_High_Risk_95CI, Likelihood_Low_Risk_95CI) %>%
  gt() %>%
  tab_header(title = "Complete Results with 95% Confidence Intervals") %>%
  gt_theme_espn()

# Save index date plots
if (!is.null(roc_index)) ggsave("grid_search_roc_index_date.pdf", plot = roc_index, width = 8, height = 6)
if (!is.null(dca_index)) ggsave("grid_search_dca_index_date.pdf", plot = dca_index, width = 10, height = 6)
if (!is.null(km_index)) {
  pdf("grid_search_km_index_date.pdf", width = 10, height = 7)
  print(km_index)
  dev.off()
}

# Save grid search plots
save_grid_plots <- function(results, prefix) {
  for (nm in names(results$roc_plots)) {
    ggsave(paste0("grid_search_roc_", prefix, "_", nm, ".pdf"),
           plot = results$roc_plots[[nm]], width = 8, height = 6)
  }
  for (nm in names(results$km_plots)) {
    pdf(paste0("grid_search_km_", prefix, "_", nm, ".pdf"), width = 10, height = 7)
    print(results$km_plots[[nm]])
    dev.off()
  }
  for (nm in names(results$dca_plots)) {
    ggsave(paste0("grid_search_dca_", prefix, "_", nm, ".pdf"),
           plot = results$dca_plots[[nm]], width = 10, height = 6)
  }
}

save_grid_plots(results_first, "first_date")
save_grid_plots(results_first, "first_date")
save_grid_plots(results_second, "second_date")
save_grid_plots(results_second, "second_date")
save_grid_plots(results_third, "third_date")
save_grid_plots(results_third, "third_date")

# Save heatmaps
if (nrow(heatmap_data) > 0) {
  ggsave("grid_search_heatmap_auc.pdf", plot = auc_heatmap, width = 12, height = 8)
  ggsave("grid_search_heatmap_sensitivity.pdf", plot = sens_heatmap, width = 12, height = 8)
  ggsave("grid_search_heatmap_specificity.pdf", plot = spec_heatmap, width = 12, height = 8)
  ggsave("grid_search_heatmap_ppv.pdf", plot = ppv_heatmap, width = 12, height = 8)
  ggsave("grid_search_heatmap_npv.pdf", plot = npv_heatmap, width = 12, height = 8)
  ggsave("grid_search_heatmap_likelihood_high_risk.pdf", plot = high_risk_likelihood, width = 12, height = 10)
  ggsave("grid_search_heatmap_likelihood_low_risk.pdf", plot = low_risk_likelihood, width = 12, height = 10)
}

cat("All outputs saved.\n")
```

# Recurrent Disease Definition

This section investigates whether **number of previous stone events** (i.e. "recurrent disease") is itself a useful risk classifier, and whether combining it with short inter-event time improves prognostication.

## Long-Format Transition Tibble

We reshape the data so that each row represents one participant-transition (e.g. 1→2, 2→3, 3→4, 4→5), with the outcome being whether the next event occurred within the follow-up window.

```{r transitions-long}
transition_specs <- tribble(
  ~transition, ~from_col,      ~to_col,       ~from_event_num, ~gap_col,
  "1→2",      "index_date",   "first_date",  1L,              NA_character_,
  "2→3",      "first_date",   "second_date", 2L,              "gap_index_to_first_months",
  "3→4",      "second_date",  "third_date",  3L,              "gap_first_to_second_months",
  "4→5",      "third_date",   "fourth_date", 4L,              "gap_second_to_third_months"
)

last_date_df <- overall_follow_up %>% dplyr::select(participant_id, last_date)

transitions_long <- pmap_dfr(transition_specs, function(transition, from_col, to_col,
                                                         from_event_num, gap_col) {
  df <- dates_detailed %>%
    dplyr::select(participant_id, from_date = !!sym(from_col),
                  to_date = !!sym(to_col)) %>%
    filter(!is.na(from_date)) %>%
    left_join(last_date_df, by = "participant_id") %>%
    filter(!is.na(last_date)) %>%
    mutate(
      transition = transition,
      from_event_num = from_event_num,
      had_next_event = if_else(!is.na(to_date), 1L, 0L),
      event_or_censor_date = if_else(!is.na(to_date), to_date, last_date),
      time_to_next_years = as.numeric(event_or_censor_date - from_date) / 365.25,
      # Cap at follow-up horizon
      time_to_next_years = pmin(time_to_next_years, follow_up_years),
      # If event is beyond follow-up horizon, treat as censored
      had_next_event = if_else(
        !is.na(to_date) & as.numeric(to_date - from_date) / 365.25 > follow_up_years,
        0L, had_next_event
      ),
      n_previous_events = from_event_num
    )

  # Add prior gap if applicable
  if (!is.na(gap_col)) {
    gap_vals <- dates_detailed %>%
      dplyr::select(participant_id, prior_gap_months = !!sym(gap_col))
    df <- df %>% left_join(gap_vals, by = "participant_id")
  } else {
    df <- df %>% mutate(prior_gap_months = NA_real_)
  }

  df %>%
    dplyr::select(participant_id, transition, from_event_num, from_date,
                  to_date, last_date, time_to_next_years, had_next_event,
                  n_previous_events, prior_gap_months) %>%
    filter(time_to_next_years > 0)
})

# Summary
cat("Transitions summary:\n")
transitions_long %>%
  group_by(transition) %>%
  summarise(
    n = n(),
    n_events = sum(had_next_event),
    pct_event = round(100 * mean(had_next_event), 1),
    median_time_yrs = round(median(time_to_next_years), 2),
    .groups = "drop"
  ) %>%
  print()
```

## KM by Event Number

Kaplan-Meier curves stratified by transition type (1→2, 2→3, 3→4, 4→5). This shows whether later transitions have different recurrence dynamics compared to earlier ones.

```{r km-by-event-number, fig.width=10, fig.height=7}
transitions_long$transition <- factor(transitions_long$transition,
                                       levels = c("1→2", "2→3", "3→4", "4→5"))

fit_transition <- surv_fit(Surv(time_to_next_years, had_next_event) ~ transition,
                           data = transitions_long)

km_by_event <- ggsurvplot(
  fit_transition,
  data = transitions_long,
  pval = TRUE,
  pval.method = TRUE,
  risk.table = TRUE,
  risk.table.height = 0.3,
  conf.int = TRUE,
  censor = FALSE,
  xlab = "Time (years)",
  ylab = "Event-free probability",
  title = "Time to Next Stone Event by Transition",
  surv.median.line = "hv",
  legend.title = "Transition",
  palette = c("#1b9e77", "#d95f02", "#7570b3", "#e7298a"),
  xlim = c(0, follow_up_years),
  break.time.by = 1
)
print(km_by_event)

ggsave("recurrent_disease_km_by_transition.pdf",
       plot = km_by_event$plot, width = 10, height = 7)
```

### Faceted by Transition, Stratified by Total Event Count

Within each transition (1→2, 2→3, etc.), we stratify by the **total number of stone events** the individual experienced across the entire study period (1, 2, 3, 4, >4). This reveals whether individuals who go on to have many events already show different dynamics at earlier transitions.

```{r km-by-transition-total-events, fig.width=14, fig.height=10}
# Add total event count from dates_detailed (n_recurrences = events after index)
total_events <- dates_detailed %>%
  dplyr::select(participant_id, n_recurrences) %>%
  mutate(total_events = n_recurrences + 1L)  # +1 for the index event

transitions_long <- transitions_long %>%
  left_join(total_events, by = "participant_id") %>%
  mutate(
    total_events_grp = case_when(
      total_events == 1 ~ "1 event",
      total_events == 2 ~ "2 events",
      total_events == 3 ~ "3 events",
      total_events == 4 ~ "4 events",
      total_events >= 5 ~ ">4 events"
    ),
    total_events_grp = factor(total_events_grp,
                               levels = c("1 event", "2 events", "3 events",
                                          "4 events", ">4 events"))
  )

# For each transition facet, only certain total-event groups are possible
# e.g. transition 1→2 can include people with 1 event (censored) or 2+ events
# transition 2→3 requires at least 2 events to enter, etc.

# Build KM fits per transition facet
transition_levels <- levels(transitions_long$transition)

facet_km_plots <- lapply(transition_levels, function(tr) {
  tr_data <- transitions_long %>% filter(transition == tr)

  # Drop groups with too few observations
  grp_counts <- tr_data %>% count(total_events_grp) %>% filter(n >= 5)
  tr_data <- tr_data %>% filter(total_events_grp %in% grp_counts$total_events_grp) %>%
    droplevels()

  if (nlevels(tr_data$total_events_grp) < 2) return(NULL)

  fit <- surv_fit(Surv(time_to_next_years, had_next_event) ~ total_events_grp,
                  data = tr_data)

  p <- ggsurvplot(
    fit,
    data = tr_data,
    pval = TRUE,
    pval.method = TRUE,
    conf.int = TRUE,
    censor = FALSE,
    risk.table = TRUE,
    risk.table.height = 0.35,
    surv.median.line = "hv",
    xlab = "Time (years)",
    ylab = "Event-free probability",
    title = paste0("Transition ", tr, ": Stratified by Total Events"),
    legend.title = "Total Events",
    palette = "jco",
    xlim = c(0, follow_up_years),
    break.time.by = 1
  )
  p
})

# Print each plot
for (p in facet_km_plots) {
  if (!is.null(p)) print(p)
}

# Save individual PDFs
for (i in seq_along(transition_levels)) {
  if (!is.null(facet_km_plots[[i]])) {
    fname <- paste0("recurrent_disease_km_transition_",
                    gsub("→", "to", transition_levels[i]),
                    "_by_total_events.pdf")
    ggsave(fname, plot = facet_km_plots[[i]]$plot, width = 10, height = 7)
  }
}
```

## KM by "Recurrent Disease" (Event Count)

Pool all transitions together and classify participants as "high risk" based on how many prior events they have experienced.

### ≥2 Previous Events = High Risk

```{r km-recurrent-2plus, fig.width=10, fig.height=7}
transitions_long <- transitions_long %>%
  mutate(
    recurrent_2plus = if_else(from_event_num >= 2,
                              "High Risk (≥2 events)",
                              "Low Risk (1 event)")
  )

fit_2plus <- surv_fit(Surv(time_to_next_years, had_next_event) ~ recurrent_2plus,
                      data = transitions_long)

km_2plus <- ggsurvplot(
  fit_2plus,
  data = transitions_long,
  pval = TRUE,
  pval.method = TRUE,
  conf.int = TRUE,
  censor = FALSE,
  risk.table = TRUE,
  risk.table.height = 0.25,
  surv.median.line = "hv",
  xlab = "Time (years)",
  ylab = "Event-free probability",
  title = "Recurrent Disease: ≥2 Previous Events vs 1 Event",
  legend.title = "Risk Group",
  palette = c("#d95f02", "#1b9e77"),
  xlim = c(0, follow_up_years),
  break.time.by = 1
)
print(km_2plus)

ggsave("recurrent_disease_km_2plus.pdf",
       plot = km_2plus$plot, width = 10, height = 7)

# --- Extract 5-year KM-based recurrence rate by event-count group ---
# This drives Figure 3 of the paper (likelihood by 1st Event vs ≥2 Events).
km_5y_summary <- summary(fit_2plus, times = follow_up_years, extend = TRUE)

km_5y_df <- data.frame(
  Group        = sub("recurrent_2plus=", "", as.character(km_5y_summary$strata)),
  N_at_risk    = km_5y_summary$n.risk,
  N_events     = km_5y_summary$n.event,
  surv_5y      = km_5y_summary$surv,
  surv_lo_5y   = km_5y_summary$lower,
  surv_hi_5y   = km_5y_summary$upper
) %>%
  mutate(
    rec_5y_pct    = (1 - surv_5y) * 100,
    # CI for cumulative incidence: 1 - upper, 1 - lower (note CI flip)
    rec_5y_lo_pct = (1 - surv_hi_5y) * 100,
    rec_5y_hi_pct = (1 - surv_lo_5y) * 100,
    Cohort        = "UKB"
  )

write.csv(km_5y_df, "km_5y_recurrence_by_event_count.csv", row.names = FALSE)
cat("KM 5-year recurrence rates (UKB):\n"); print(km_5y_df)
```

### ≥3 Previous Events = High Risk

```{r km-recurrent-3plus, fig.width=10, fig.height=7}
transitions_long <- transitions_long %>%
  mutate(
    recurrent_3plus = if_else(from_event_num >= 3,
                              "High Risk (≥3 events)",
                              "Low Risk (<3 events)")
  )

fit_3plus <- surv_fit(Surv(time_to_next_years, had_next_event) ~ recurrent_3plus,
                      data = transitions_long)

km_3plus <- ggsurvplot(
  fit_3plus,
  data = transitions_long,
  pval = TRUE,
  pval.method = TRUE,
  conf.int = TRUE,
  censor = FALSE,
  risk.table = TRUE,
  risk.table.height = 0.25,
  surv.median.line = "hv",
  xlab = "Time (years)",
  ylab = "Event-free probability",
  title = "Recurrent Disease: ≥3 Previous Events vs <3 Events",
  legend.title = "Risk Group",
  palette = c("#d95f02", "#1b9e77"),
  xlim = c(0, follow_up_years),
  break.time.by = 1
)
print(km_3plus)

ggsave("recurrent_disease_km_3plus.pdf",
       plot = km_3plus$plot, width = 10, height = 7)
```

## Adding Short Inter-Event Time

For participants with ≥2 previous events, we investigate whether a short gap between the two most recent events further stratifies risk. We test cutoffs of 12, 18, and 24 months.

```{r km-recurrent-short-time, fig.width=10, fig.height=18}
# Only transitions 2→3 onwards have a prior gap
transitions_with_gap <- transitions_long %>%
  filter(from_event_num >= 2, !is.na(prior_gap_months))

km_short_plots <- list()

for (cutoff in c(12, 18, 24)) {
  transitions_with_gap <- transitions_with_gap %>%
    mutate(
      !!paste0("risk_short_", cutoff) := case_when(
        prior_gap_months <= cutoff ~ paste0("High Risk (recurrent + gap ≤", cutoff, "mo)"),
        TRUE ~ paste0("Recurrent (gap >", cutoff, "mo)")
      )
    )

  risk_col <- paste0("risk_short_", cutoff)

  fit_short <- surv_fit(
    as.formula(paste0("Surv(time_to_next_years, had_next_event) ~ ", risk_col)),
    data = transitions_with_gap
  )

  km_short <- ggsurvplot(
    fit_short,
    data = transitions_with_gap,
    pval = TRUE,
    pval.method = TRUE,
    risk.table = TRUE,
    risk.table.height = 0.25,
    conf.int = TRUE,
    censor = FALSE,
    median.surv.line = "hv",
    xlab = "Time (years)",
    ylab = "Event-free probability",
    title = paste0("Recurrent Patients: Short Gap (≤", cutoff, " months) vs Long Gap"),
    legend.title = "Risk Group",
    palette = c("#d95f02", "#1b9e77"),
    xlim = c(0, follow_up_years),
    break.time.by = 1
  )

  km_short_plots[[as.character(cutoff)]] <- km_short
  print(km_short)

  ggsave(paste0("recurrent_disease_km_short_gap_", cutoff, "mo.pdf"),
         plot = km_short$plot, width = 10, height = 7)
}
```

### Three-Group Comparison (First Event vs Recurrent Long Gap vs Recurrent Short Gap)

```{r km-three-group, fig.width=10, fig.height=18}
for (cutoff in c(12, 18, 24)) {
  transitions_long <- transitions_long %>%
    mutate(
      !!paste0("three_group_", cutoff) := case_when(
        from_event_num == 1 ~ "First Event",
        from_event_num >= 2 & !is.na(prior_gap_months) & prior_gap_months <= cutoff ~
          paste0("Recurrent + Short Gap (≤", cutoff, "mo)"),
        from_event_num >= 2 ~ paste0("Recurrent + Long Gap (>", cutoff, "mo)")
      )
    )

  risk_col <- paste0("three_group_", cutoff)

  fit_3g <- surv_fit(
    as.formula(paste0("Surv(time_to_next_years, had_next_event) ~ ", risk_col)),
    data = transitions_long
  )

  km_3g <- ggsurvplot(
    fit_3g,
    data = transitions_long,
    pval = TRUE,
    pval.method = TRUE,
    risk.table = TRUE,
    censor = FALSE,
    conf.int = TRUE,
    risk.table.height = 0.3,
    xlab = "Time (years)",
    ylab = "Event-free probability",
    title = paste0("Three-Group Risk: First Event vs Recurrent (Gap ≤/>", cutoff, " months)"),
    legend.title = "Risk Group",
    palette = c("#1b9e77", "#d95f02", "#7570b3"),
    xlim = c(0, follow_up_years),
    break.time.by = 1
  )

  print(km_3g)

  ggsave(paste0("recurrent_disease_km_three_group_", cutoff, "mo.pdf"),
         plot = km_3g$plot, width = 10, height = 7)
}
```

## Combined EAU + Recurrent Disease

Compare the enhanced definition (EAU high risk OR recurrent disease with short gap) to the EAU-only definition. We use the 12-month cutoff for the short gap definition.

```{r combined-eau-recurrent, fig.width=10, fig.height=14}
# Get EAU risk classification at each starting point
eau_risk_by_start <- bind_rows(
  build_high_risk_df("index_date") %>%
    mutate(from_col = "index_date"),
  build_high_risk_df("first_date") %>%
    mutate(from_col = "first_date"),
  build_high_risk_df("second_date") %>%
    mutate(from_col = "second_date"),
  build_high_risk_df("third_date") %>%
    mutate(from_col = "third_date")
)

# Map from_col to from_event_num
eau_risk_by_start <- eau_risk_by_start %>%
  mutate(from_event_num = case_when(
    from_col == "index_date"  ~ 1L,
    from_col == "first_date"  ~ 2L,
    from_col == "second_date" ~ 3L,
    from_col == "third_date"  ~ 4L
  ))

# Join EAU risk into transitions_long
transitions_long <- transitions_long %>%
  left_join(
    eau_risk_by_start %>% dplyr::select(participant_id, from_event_num, eau_risk = high_risk),
    by = c("participant_id", "from_event_num")
  )

# Define combined risk using 12-month cutoff
transitions_long <- transitions_long %>%
  mutate(
    recurrent_short_12 = from_event_num >= 2 & !is.na(prior_gap_months) & prior_gap_months <= 12,
    # EAU only
    risk_eau_only = if_else(eau_risk == "high_risk", "EAU High Risk", "Low Risk"),
    # Combined: EAU OR (recurrent + short gap)
    risk_combined = case_when(
      eau_risk == "high_risk" | recurrent_short_12 ~ "High Risk (EAU or Recurrent+Short)",
      TRUE ~ "Low Risk"
    ),
    # Four-group for detailed view
    risk_four_group = case_when(
      eau_risk == "high_risk" & recurrent_short_12 ~ "EAU High + Recurrent Short Gap",
      eau_risk == "high_risk" & !recurrent_short_12 ~ "EAU High Only",
      eau_risk != "high_risk" & recurrent_short_12 ~ "Recurrent Short Gap Only",
      TRUE ~ "Low Risk"
    )
  )

# KM: EAU-only risk
fit_eau <- surv_fit(Surv(time_to_next_years, had_next_event) ~ risk_eau_only,
                    data = transitions_long)

km_eau <- ggsurvplot(
  fit_eau,
  data = transitions_long,
  pval = TRUE,
  pval.method = TRUE,
  conf.int = TRUE,
  censor = FALSE,
  risk.table = TRUE,
  risk.table.height = 0.25,
  surv.median.line = "hv",
  xlab = "Time (years)",
  ylab = "Event-free probability",
  title = "EAU Risk Classification Only (Pooled Transitions)",
  legend.title = "Risk Group",
  palette = c("#d95f02", "#1b9e77"),
  xlim = c(0, follow_up_years),
  break.time.by = 1
)
print(km_eau)

# KM: Combined risk
fit_combined <- surv_fit(Surv(time_to_next_years, had_next_event) ~ risk_combined,
                         data = transitions_long)

km_combined <- ggsurvplot(
  fit_combined,
  data = transitions_long,
  pval = TRUE,
  pval.method = TRUE,
  conf.int = TRUE,
  censor = FALSE,
  risk.table = TRUE,
  risk.table.height = 0.25,
  surv.median.line = "hv",
  xlab = "Time (years)",
  ylab = "Event-free probability",
  title = "Combined Risk: EAU OR Recurrent Disease (≥2 events + gap ≤12mo)",
  legend.title = "Risk Group",
  palette = c("#d95f02", "#1b9e77"),
  xlim = c(0, follow_up_years),
  break.time.by = 1
)
print(km_combined)

ggsave("recurrent_disease_km_eau_only_pooled.pdf",
       plot = km_eau$plot, width = 10, height = 7)
ggsave("recurrent_disease_km_combined_eau_recurrent.pdf",
       plot = km_combined$plot, width = 10, height = 7)
```

### Four-Group Detailed Breakdown

```{r four-group-detail, fig.width=12, fig.height=8}
fit_four <- surv_fit(Surv(time_to_next_years, had_next_event) ~ risk_four_group,
                     data = transitions_long)

km_four <- ggsurvplot(
  fit_four,
  data = transitions_long,
  pval = TRUE,
  pval.method = TRUE,
  conf.int = TRUE,
  censor = FALSE,
  risk.table = TRUE,
  risk.table.height = 0.35,
  surv.median.line = "hv",
  xlab = "Time (years)",
  ylab = "Event-free probability",
  title = "Four-Group Risk Breakdown: EAU × Recurrent Disease (12mo cutoff)",
  legend.title = "Risk Group",
  palette = c("#e7298a", "#d95f02", "#7570b3", "#1b9e77"),
  xlim = c(0, follow_up_years),
  break.time.by = 1
)
print(km_four)

ggsave("recurrent_disease_km_four_group.pdf",
       plot = km_four$plot, width = 12, height = 8)
```

### Summary Table: Reclassification

```{r reclassification-summary}
# How many participants are reclassified by adding recurrent disease?
reclass <- transitions_long %>%
  mutate(
    eau_high = eau_risk == "high_risk",
    combined_high = eau_risk == "high_risk" | recurrent_short_12
  ) %>%
  summarise(
    n_total = n(),
    n_eau_high = sum(eau_high, na.rm = TRUE),
    n_combined_high = sum(combined_high, na.rm = TRUE),
    n_reclassified = sum(!eau_high & recurrent_short_12, na.rm = TRUE),
    pct_reclassified = round(100 * n_reclassified / n_total, 1)
  )

cat("Reclassification summary (adding recurrent disease to EAU):\n")
print(reclass)

# Event rates in reclassified group
reclassified_events <- transitions_long %>%
  filter(eau_risk != "high_risk", recurrent_short_12) %>%
  summarise(
    n = n(),
    n_events = sum(had_next_event),
    event_rate = round(100 * mean(had_next_event), 1)
  )

cat("\nEvent rate in reclassified group (EAU low but recurrent + short gap):\n")
print(reclassified_events)

cat("\nRecurrent Disease Definition section complete.\n")
```

## Prognostic Accuracy (Recurrent Disease Combined Classifier) - No time cut-off

For each of the 7 gap cutoffs, we evaluate two risk classifiers per transition type:

- **EAU Only**: EAU high-risk factors (including age < 25)
- **EAU + Recurrent Disease**: EAU high-risk + ≥2 previous events

Each transition is analysed separately to avoid repeated-measures confounding.

### Recurrence metrics with no 'short time' cut-off
```{r}
rec_metrics_list <- list()
rec_roc_plots_no_time_cut_off <- list()
rec_dca_plots_no_time_cut_off    <- list()
rec_delong_tests <- list()

# store DeLong p-values
rec_delong_df <- data.frame(
  Transition = character(),
  delong_p   = numeric(),
  stringsAsFactors = FALSE
)

rec_label <- "\u22651 subsequent stone event"

for (tr in levels(transitions_long$transition)) {

  tl <- transitions_long %>%
    filter(transition == tr) %>%
    mutate(
      recurrent_any = from_event_num >= 2,

      risk_combined = if_else(
        !is.na(eau_risk) & (eau_risk == "high_risk" | recurrent_any),
        "high_risk", "low_risk"
      ),

      risk_eau = if_else(
        !is.na(eau_risk) & eau_risk == "high_risk",
        "high_risk", "low_risk"
      )
    )

  # -------------------------------
  # ROC + metrics + DeLong
  # -------------------------------
  roc_list <- list()
  roc_overlay_df <- data.frame()

  for (risk_def in c("EAU Only", "EAU + Recurrent Disease")) {

    risk_col <- if (risk_def == "EAU Only") "risk_eau" else "risk_combined"

    rd <- tl %>%
      mutate(
        actual = case_when(
          had_next_event == 1 ~ 1L,
          had_next_event == 0 & time_to_next_years >= follow_up_years ~ 0L,
          TRUE ~ NA_integer_
        ),
        predicted = if_else(!!sym(risk_col) == "high_risk", 1, 0)
      ) %>%
      drop_na(actual, predicted)

    if (nrow(rd) < 10 || length(unique(rd$actual)) < 2) next

    ro <- roc(rd$actual, rd$predicted, quiet = TRUE)
    roc_list[[risk_def]] <- ro

    auc_val <- round(as.numeric(auc(ro)), 3)

    # metrics
    m <- extract_metrics_grid(ro, rec_label, rd) %>%
      mutate(
        Transition      = tr,
        Starting_Point  = tr,
        Risk_Definition = risk_def,
        Comparison      = rec_label
      )

    rec_metrics_list[[paste(tr, risk_def, sep = "_")]] <- m

    # ROC df
    roc_overlay_df <- rbind(
      roc_overlay_df,
      data.frame(
        fpr = 1 - ro$specificities,
        tpr = ro$sensitivities,
        Definition = paste0(risk_def, " (AUC=", auc_val, ")")
      )
    )
  }

  # --- DeLong test ---
  if (all(c("EAU Only", "EAU + Recurrent Disease") %in% names(roc_list))) {

    delong_test <- roc.test(
      roc_list[["EAU Only"]],
      roc_list[["EAU + Recurrent Disease"]],
      method = "delong"
    )

    p_val <- as.numeric(delong_test$p.value)

    # store p-value
    rec_delong_df <- rbind(
      rec_delong_df,
      data.frame(
        Transition = tr,
        delong_p   = p_val
      )
    )

    rec_delong_tests[[tr]] <- delong_test

    cat("\n--- DeLong test:", tr, "---\n")
    print(delong_test)
  }

  # --- ROC plot ---
  if (nrow(roc_overlay_df) > 0) {

    p_roc <- ggplot(roc_overlay_df,
                    aes(x = fpr, y = tpr, colour = Definition)) +
      geom_line(linewidth = 1) +
      geom_abline(linetype = "dashed", alpha = 0.5) +
      coord_equal() +
      labs(
        x = "False Positive Rate",
        y = "True Positive Rate",
        title = paste0("ROC: Transition ", tr, " (5-year recurrence)"),
        colour = "Risk Definition"
      ) +
      scale_colour_manual(values = c("#7570b3", "#d95f02")) +
      theme_bw(base_size = 12) +
      theme(legend.position = "bottom")

    safe_tr <- gsub("\u2192", "to", tr)
    rec_roc_plots_no_time_cut_off[[paste0("transition_", safe_tr)]] <- p_roc
  }

  # -------------------------------
  # DCA
  # -------------------------------
  tl_dca <- tl %>%
    mutate(
      actual = case_when(
        had_next_event == 1 & time_to_next_years <= follow_up_years ~ 1L,
        had_next_event == 0 & time_to_next_years >= follow_up_years ~ 0L,
        TRUE ~ NA_integer_
      ),
      risk_binary = if_else(risk_combined == "high_risk", 1, 0)
    ) %>%
    drop_na(actual, risk_binary)

  if (nrow(tl_dca) >= 10 && length(unique(tl_dca$actual)) >= 2) {

    dca_res <- dca(actual ~ risk_binary, data = tl_dca,
                   thresholds = seq(0, 0.8, by = 0.01))

    dca_df <- plot(dca_res)$data

    p_dca <- ggplot(dca_df,
                    aes(x = threshold, y = net_benefit, colour = label)) +
      geom_line(linewidth = 0.8) +
      theme_bw(base_size = 12) +
      theme(legend.position = "bottom") +
      labs(
        x = "Probability Threshold",
        y = "Net Benefit",
        colour = NULL,
        title = paste0("DCA: Transition ", tr, " (5-year)")
      ) +
      xlim(c(0, 0.6)) +
      geom_vline(xintercept = 0.2, linetype = "dashed")

    safe_tr <- gsub("\u2192", "to", tr)
    rec_dca_plots_no_time_cut_off[[paste0("transition_", safe_tr)]] <- p_dca
  }
}

# -------------------------------
# Combine metrics + join DeLong p-values
# -------------------------------
rec_metrics_df_no_time_cut_off <- bind_rows(rec_metrics_list) %>%
  mutate(
    Transition = factor(Transition,
                        levels = c("1\u21922", "2\u21923", "3\u21924", "4\u21925")),
    Risk_Definition = factor(Risk_Definition,
                             levels = c("EAU Only", "EAU + Recurrent Disease"))
  ) %>%
  left_join(rec_delong_df, by = "Transition") %>%
  mutate(
    delong_p_fmt = ifelse(is.na(delong_p), NA,
                          ifelse(delong_p < 0.001, "<0.001",
                                 sprintf("%.3f", delong_p)))
  )

cat("\nDone:",
    nrow(rec_metrics_df_no_time_cut_off), "rows across",
    n_distinct(rec_metrics_df_no_time_cut_off$Transition), "transitions.\n")
```
### ROC Curves (no cut-off)

```{r rec-roc-plots, fig.width=8, fig.height=6, warning=FALSE}
for (nm in names(rec_roc_plots_no_time_cut_off)) {
  cat("\n#### Transition:", gsub("_", " ", gsub("transition_|_cutoff_12", "", nm)), "\n")
  print(rec_roc_plots_no_time_cut_off[[nm]])
  cat("\n")
}
```

### Decision Curve Analysis (no cut-off)

```{r rec-dca-plots, fig.width=10, fig.height=6, warning=FALSE}
for (nm in names(rec_dca_plots_no_time_cut_off)) {
  cat("\n#### Transition:", gsub("_", " ", gsub("transition_|_cutoff_12", "", nm)), "\n")
  print(rec_dca_plots_no_time_cut_off[[nm]])
  cat("\n")
}
```

### Metrics Table

```{r rec-metrics-table, warning=FALSE}
rec_metrics_df_no_time_cut_off %>%
  dplyr::select(Transition, Risk_Definition,
                N, N_High_Risk, N_Low_Risk,
                AUC, delong_p_fmt, Sensitivity, Specificity, PPV, NPV) %>%
  arrange(Transition, Risk_Definition) %>%
  gt() %>%
  tab_header(title = "Prognostic Accuracy: Recurrent Disease Classifier vs EAU Only") %>%
  gt_theme_espn()
```

### Save Recurrent Disease Metrics CSV

```{r rec-save-csv, warning=FALSE}
write.csv(
  rec_metrics_df_no_time_cut_off %>%
    dplyr::select(Transition, Starting_Point, Risk_Definition,
                  N, N_High_Risk, N_Low_Risk,
                  AUC_val, AUC_lo, AUC_hi,
                  Sensitivity_val, Sensitivity_lo, Sensitivity_hi,
                  Specificity_val, Specificity_lo, Specificity_hi,
                  PPV_val, PPV_lo, PPV_hi,
                  NPV_val, NPV_lo, NPV_hi,
                  Likelihood_Recurrence_High_Risk_pct,
                  Likelihood_Recurrence_High_Risk_lo,
                  Likelihood_Recurrence_High_Risk_hi,
                  Likelihood_Recurrence_Low_Risk_pct,
                  Likelihood_Recurrence_Low_Risk_lo,
                  Likelihood_Recurrence_Low_Risk_hi),
  "recurrent_disease_prognostic_accuracy_results_no_time_cut_off.csv", row.names = FALSE
)
cat("Recurrent disease metrics CSV saved.\n")
```

## Prognostic Accuracy (Recurrent Disease Combined Classifier) - Time cut-off

For each of the 7 gap cutoffs, we evaluate two risk classifiers per transition type:

- **EAU Only**: EAU high-risk factors (including age < 25)
- **EAU + Recurrent Disease**: EAU high-risk OR (≥2 previous events AND prior inter-event gap ≤ cutoff)

Each transition is analysed separately to avoid repeated-measures confounding.

### Recurrence metrics with 'short time' cut-off
```{r rec-disease-prognostic-accuracy-setup, warning=FALSE, message=FALSE}
rec_metrics_list <- list()
rec_roc_plots    <- list()
rec_km_plots     <- list()
rec_dca_plots    <- list()

# One representative label per transition for recurrence threshold
rec_label <- "\u22651 subsequent stone event"

for (cutoff in time_cutoffs_months) {
  for (tr in levels(transitions_long$transition)) {
    tl <- transitions_long %>%
      filter(transition == tr) %>%
      mutate(
        recurrent_short = from_event_num >= 2 &
          !is.na(prior_gap_months) & prior_gap_months <= cutoff,
        risk_combined_cut = if_else(
          !is.na(eau_risk) & (eau_risk == "high_risk" | recurrent_short),
          "high_risk", "low_risk"
        ),
        risk_eau = if_else(!is.na(eau_risk) & eau_risk == "high_risk",
                           "high_risk", "low_risk"),
        subsequent_events     = had_next_event,
        follow_up_from_start_years = time_to_next_years,
        has_next_event        = had_next_event
      )

    for (risk_def in c("EAU Only", "EAU + Recurrent Disease")) {
      risk_col <- if (risk_def == "EAU Only") "risk_eau" else "risk_combined_cut"

      roc_data <- tl %>%
        mutate(
          actual = case_when(
            had_next_event == 1 ~ 1L,
            had_next_event == 0 & time_to_next_years >= follow_up_years ~ 0L,
            TRUE ~ NA_integer_
          ),
          predicted = if_else(!!sym(risk_col) == "high_risk", 1, 0)
        ) %>%
        drop_na(actual, predicted)

      if (nrow(roc_data) < 10 || length(unique(roc_data$actual)) < 2) next

      roc_obj <- roc(roc_data$actual, roc_data$predicted, quiet = TRUE)
      m <- extract_metrics_grid(roc_obj, rec_label, roc_data) %>%
        mutate(
          Transition       = tr,
          Starting_Point   = tr,
          Time_Cutoff_Months = cutoff,
          Risk_Definition  = risk_def,
          Comparison       = rec_label
        )
      rec_metrics_list[[paste(tr, cutoff, risk_def, sep = "_")]] <- m
    }

    # At 12mo cutoff: generate ROC, KM, DCA plots per transition
    if (cutoff == 12) {
      tl12 <- tl

      # --- ROC: overlay EAU Only vs Combined ---
      roc_overlay_df <- data.frame()
      for (risk_def in c("EAU Only", "EAU + Recurrent Disease")) {
        risk_col <- if (risk_def == "EAU Only") "risk_eau" else "risk_combined_cut"
        rd <- tl12 %>%
          mutate(
            actual    = case_when(
              had_next_event == 1 ~ 1L,
              had_next_event == 0 & time_to_next_years >= follow_up_years ~ 0L,
              TRUE ~ NA_integer_
            ),
            predicted = if_else(!!sym(risk_col) == "high_risk", 1, 0)
          ) %>% drop_na(actual, predicted)
        if (nrow(rd) < 10 || length(unique(rd$actual)) < 2) next
        ro <- roc(rd$actual, rd$predicted, quiet = TRUE)
        auc_val <- round(as.numeric(auc(ro)), 3)
        roc_overlay_df <- rbind(roc_overlay_df, data.frame(
          fpr        = 1 - ro$specificities,
          tpr        = ro$sensitivities,
          Definition = paste0(risk_def, " (AUC=", auc_val, ")")
        ))
      }
      if (nrow(roc_overlay_df) > 0) {
        p_roc <- ggplot(roc_overlay_df, aes(x = fpr, y = tpr, colour = Definition)) +
          geom_line(linewidth = 1) +
          geom_abline(linetype = "dashed", alpha = 0.5) +
          coord_equal() +
          labs(x = "False Positive Rate", y = "True Positive Rate",
               title = paste0("ROC: Transition ", tr, " (gap \u2264 12mo)"),
               colour = "Risk Definition") +
          scale_colour_manual(values = c(
            grep("EAU Only",             unique(roc_overlay_df$Definition), value=TRUE),
            grep("EAU \\+ Recurrent",    unique(roc_overlay_df$Definition), value=TRUE)
          ) %>% setNames(c("#7570b3", "#d95f02"), .) %>% rev()) +
          theme_bw(base_size = 12) +
          theme(legend.position = "bottom")
        safe_tr <- gsub("\u2192", "to", tr)
        rec_roc_plots[[paste0("transition_", safe_tr, "_cutoff_12")]] <- p_roc
      }

      # --- KM: EAU + Recurrent Disease combined risk ---
      tl_km <- tl12 %>%
        rename(risk_group = risk_combined_cut) %>%
        filter(!is.na(time_to_next_years), !is.na(risk_group))

      if (nrow(tl_km) >= 10 && length(unique(tl_km$risk_group)) >= 2) {
        km_fit <- surv_fit(Surv(time_to_next_years, had_next_event) ~ risk_group,
                           data = tl_km)
        km_p <- ggsurvplot(
          km_fit, data = tl_km,
          pval = TRUE, pval.method = TRUE,
          conf.int = TRUE, censor = FALSE,
          risk.table = TRUE, risk.table.height = 0.28,
          surv.median.line = "hv", break.time.by = 1,
          xlab = "Time (years)", xlim = c(0, follow_up_years),
          title = paste0("KM: Transition ", tr,
                         " – EAU + Recurrent Disease (gap \u2264 12mo)"),
          pval.size = 4,
          legend.title = "Risk Status",
          legend.labs = c("High Risk", "Low Risk"),
          palette = c("#d95f02", "#1b9e77"),
          ggtheme = theme_bw()
        )
        safe_tr <- gsub("\u2192", "to", tr)
        rec_km_plots[[paste0("transition_", safe_tr, "_cutoff_12")]] <- km_p
      }

      # --- DCA: EAU + Recurrent Disease ---
      tl_dca <- tl12 %>%
        mutate(
          actual       = as.integer(had_next_event == 1),
          risk_binary  = if_else(risk_combined_cut == "high_risk", 1, 0)
        ) %>% drop_na(actual, risk_binary)

      if (nrow(tl_dca) >= 10 && length(unique(tl_dca$actual)) >= 2) {
        dca_res <- dca(actual ~ risk_binary, data = tl_dca,
                       thresholds = seq(0, 0.8, by = 0.01))
        dca_df  <- plot(dca_res)$data
        p_dca <- ggplot(dca_df, aes(x = threshold, y = net_benefit, colour = label)) +
          geom_line(linewidth = 0.8) +
          labs(x = "Probability Threshold", y = "Net Benefit", colour = NULL,
               title = paste0("DCA: Transition ", tr,
                              " – EAU + Recurrent Disease (gap \u2264 12mo)")) +
          theme_bw(base_size = 12) +
          theme(legend.position = "bottom") +
          xlim(c(0, 0.6)) +
          geom_vline(xintercept = 0.2, linetype = "dashed")
        safe_tr <- gsub("\u2192", "to", tr)
        rec_dca_plots[[paste0("transition_", safe_tr, "_cutoff_12")]] <- p_dca
      }
    }
  }
}

rec_metrics_df <- bind_rows(rec_metrics_list) %>%
  mutate(
    Time_Cutoff_label = paste0("\u2264", Time_Cutoff_Months, "mo"),
    Time_Cutoff_label = factor(Time_Cutoff_label,
      levels = c("\u22646mo", "\u22649mo", "\u226412mo",
                 "\u226415mo", "\u226418mo", "\u226421mo", "\u226424mo")),
    Transition = factor(Transition, levels = c("1\u21922", "2\u21923",
                                               "3\u21924", "4\u21925")),
    Risk_Definition = factor(Risk_Definition,
                             levels = c("EAU Only", "EAU + Recurrent Disease"))
  )

cat("Recurrent disease prognostic accuracy computed for",
    nrow(rec_metrics_df), "rows across",
    n_distinct(rec_metrics_df$Transition), "transitions and",
    n_distinct(rec_metrics_df$Time_Cutoff_Months), "cutoffs.\n")
```

### ROC Curves (12mo cutoff, per transition)

```{r rec-roc-plots, fig.width=8, fig.height=6, warning=FALSE}
for (nm in names(rec_roc_plots)) {
  cat("\n#### Transition:", gsub("_", " ", gsub("transition_|_cutoff_12", "", nm)), "\n")
  print(rec_roc_plots[[nm]])
  cat("\n")
}
```

### Kaplan-Meier (12mo cutoff, per transition)

```{r rec-km-plots, fig.width=10, fig.height=7, warning=FALSE}
for (nm in names(rec_km_plots)) {
  cat("\n#### Transition:", gsub("_", " ", gsub("transition_|_cutoff_12", "", nm)), "\n")
  print(rec_km_plots[[nm]])
  cat("\n")
}
```

### Decision Curve Analysis (12mo cutoff, per transition)

```{r rec-dca-plots, fig.width=10, fig.height=6, warning=FALSE}
for (nm in names(rec_dca_plots)) {
  cat("\n#### Transition:", gsub("_", " ", gsub("transition_|_cutoff_12", "", nm)), "\n")
  print(rec_dca_plots[[nm]])
  cat("\n")
}
```

### Metrics Table

```{r rec-metrics-table, warning=FALSE}
rec_metrics_df %>%
  dplyr::select(Transition, Time_Cutoff_label, Risk_Definition,
                N, N_High_Risk, N_Low_Risk,
                AUC, Sensitivity, Specificity, PPV, NPV) %>%
  arrange(Transition, Time_Cutoff_label, Risk_Definition) %>%
  gt() %>%
  tab_header(title = "Prognostic Accuracy: Recurrent Disease Classifier vs EAU Only") %>%
  gt_theme_espn()
```

### Save Recurrent Disease Metrics CSV

```{r rec-save-csv, warning=FALSE}
write.csv(
  rec_metrics_df %>%
    dplyr::select(Transition, Starting_Point, Time_Cutoff_Months, Risk_Definition,
                  N, N_High_Risk, N_Low_Risk,
                  AUC_val, AUC_lo, AUC_hi,
                  Sensitivity_val, Sensitivity_lo, Sensitivity_hi,
                  Specificity_val, Specificity_lo, Specificity_hi,
                  PPV_val, PPV_lo, PPV_hi,
                  NPV_val, NPV_lo, NPV_hi,
                  Likelihood_Recurrence_High_Risk_pct,
                  Likelihood_Recurrence_High_Risk_lo,
                  Likelihood_Recurrence_High_Risk_hi,
                  Likelihood_Recurrence_Low_Risk_pct,
                  Likelihood_Recurrence_Low_Risk_lo,
                  Likelihood_Recurrence_Low_Risk_hi),
  "recurrent_disease_prognostic_accuracy_results.csv", row.names = FALSE
)
cat("Recurrent disease metrics CSV saved.\n")
```

## Updated Heatmaps: EAU Only vs EAU + Recurrent Disease

These heatmaps compare the prognostic accuracy of the EAU-only classifier against the
combined EAU + Recurrent Disease classifier, across all transitions and inter-event time cutoffs.

```{r rec-heatmap-data, warning=FALSE}
rec_hm <- rec_metrics_df %>%
  mutate(
    Transition = factor(Transition,
                        levels = rev(levels(Transition)))  # bottom-to-top ordering
  )
```

### AUC

```{r rec-heatmap-auc, fig.width=13, fig.height=7, warning=FALSE}
med_auc_r <- median(rec_hm$AUC_val, na.rm = TRUE)

rec_auc_heatmap <- ggplot(rec_hm,
    aes(x = Time_Cutoff_label, y = Transition, fill = AUC_val)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = sprintf("%.2f", AUC_val)), size = 3) +
  facet_wrap(~ Risk_Definition, nrow = 1) +
  scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                       midpoint = med_auc_r, name = "AUC") +
  labs(x = "Gap Threshold", y = "Transition",
       title = "AUC: EAU Only vs EAU + Recurrent Disease",
       subtitle = "Rows = stone event transitions; columns = inter-event gap cutoff") +
  theme_bw(base_size = 11) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(face = "bold"),
        legend.position = "right")
rec_auc_heatmap
```

### Sensitivity

```{r rec-heatmap-sens, fig.width=13, fig.height=7, warning=FALSE}
med_sens_r <- median(rec_hm$Sensitivity_val, na.rm = TRUE)

rec_sens_heatmap <- ggplot(rec_hm,
    aes(x = Time_Cutoff_label, y = Transition, fill = Sensitivity_val)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = sprintf("%.2f", Sensitivity_val)), size = 3) +
  facet_wrap(~ Risk_Definition, nrow = 1) +
  scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                       midpoint = med_sens_r, name = "Sensitivity") +
  labs(x = "Gap Threshold", y = "Transition",
       title = "Sensitivity: EAU Only vs EAU + Recurrent Disease") +
  theme_bw(base_size = 11) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(face = "bold"),
        legend.position = "right")
rec_sens_heatmap
```

### Specificity

```{r rec-heatmap-spec, fig.width=13, fig.height=7, warning=FALSE}
med_spec_r <- median(rec_hm$Specificity_val, na.rm = TRUE)

rec_spec_heatmap <- ggplot(rec_hm,
    aes(x = Time_Cutoff_label, y = Transition, fill = Specificity_val)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = sprintf("%.2f", Specificity_val)), size = 3) +
  facet_wrap(~ Risk_Definition, nrow = 1) +
  scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                       midpoint = med_spec_r, name = "Specificity") +
  labs(x = "Gap Threshold", y = "Transition",
       title = "Specificity: EAU Only vs EAU + Recurrent Disease") +
  theme_bw(base_size = 11) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(face = "bold"),
        legend.position = "right")
rec_spec_heatmap
```

### PPV

```{r rec-heatmap-ppv, fig.width=13, fig.height=7, warning=FALSE}
med_ppv_r <- median(rec_hm$PPV_val, na.rm = TRUE)

rec_ppv_heatmap <- ggplot(rec_hm,
    aes(x = Time_Cutoff_label, y = Transition, fill = PPV_val)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = sprintf("%.2f", PPV_val)), size = 3) +
  facet_wrap(~ Risk_Definition, nrow = 1) +
  scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                       midpoint = med_ppv_r, name = "PPV") +
  labs(x = "Gap Threshold", y = "Transition",
       title = "PPV: EAU Only vs EAU + Recurrent Disease") +
  theme_bw(base_size = 11) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(face = "bold"),
        legend.position = "right")
rec_ppv_heatmap
```

### NPV

```{r rec-heatmap-npv, fig.width=13, fig.height=7, warning=FALSE}
med_npv_r <- median(rec_hm$NPV_val, na.rm = TRUE)

rec_npv_heatmap <- ggplot(rec_hm,
    aes(x = Time_Cutoff_label, y = Transition, fill = NPV_val)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = sprintf("%.2f", NPV_val)), size = 3) +
  facet_wrap(~ Risk_Definition, nrow = 1) +
  scale_fill_gradient2(low = "red3", mid = "yellow", high = "#1a9850",
                       midpoint = med_npv_r, name = "NPV") +
  labs(x = "Gap Threshold", y = "Transition",
       title = "NPV: EAU Only vs EAU + Recurrent Disease") +
  theme_bw(base_size = 11) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(face = "bold"),
        legend.position = "right")
rec_npv_heatmap
```

### Save Recurrent Disease Heatmaps & Plots

```{r rec-save-outputs, warning=FALSE}
ggsave("recurrent_disease_heatmap_auc.pdf",
       plot = rec_auc_heatmap, width = 13, height = 7)
ggsave("recurrent_disease_heatmap_sensitivity.pdf",
       plot = rec_sens_heatmap, width = 13, height = 7)
ggsave("recurrent_disease_heatmap_specificity.pdf",
       plot = rec_spec_heatmap, width = 13, height = 7)
ggsave("recurrent_disease_heatmap_ppv.pdf",
       plot = rec_ppv_heatmap, width = 13, height = 7)
ggsave("recurrent_disease_heatmap_npv.pdf",
       plot = rec_npv_heatmap, width = 13, height = 7)

# Save individual ROC / KM / DCA plots
for (nm in names(rec_roc_plots)) {
  ggsave(paste0("recurrent_disease_roc_", nm, ".pdf"),
         plot = rec_roc_plots[[nm]], width = 8, height = 6)
}
for (nm in names(rec_km_plots)) {
  pdf(paste0("recurrent_disease_km_prognostic_", nm, ".pdf"), width = 10, height = 7)
  print(rec_km_plots[[nm]])
  dev.off()
}
for (nm in names(rec_dca_plots)) {
  ggsave(paste0("recurrent_disease_dca_", nm, ".pdf"),
         plot = rec_dca_plots[[nm]], width = 10, height = 6)
}

cat("All recurrent disease outputs saved.\n")
```

# EAU vs EAU + Prior Event Count (No Time Cutoff)

This section answers a focused question: **does simply adding "number of prior stone events" (with no time-gap requirement) improve prognostic accuracy over EAU stratification alone?**

We sweep the count threshold across ≥2, ≥3, ≥4 prior events. To avoid repeated-measures confounding we run two complementary analyses:

1. **Per-transition analysis** — each transition (1→2, 2→3, 3→4, 4→5) is analysed separately. Within a transition, all participants share the same `from_event_num`, so only thresholds strictly greater than that value provide discrimination (other thresholds are reported as not applicable).
2. **Pooled analysis** — each participant contributes exactly one row (their latest observed transition with ≥5-year follow-up or event), so `from_event_num` varies across the sample and the count threshold is genuinely discriminatory.

## Per-Transition: Sweep Count Thresholds

```{r eau-vs-count-per-transition, warning=FALSE, message=FALSE}
count_thresholds <- c(2L, 3L, 4L)

pertr_metrics_list <- list()
pertr_roc_plots    <- list()
pertr_delong_rows  <- list()

for (tr in levels(transitions_long$transition)) {

  tl <- transitions_long %>%
    filter(transition == tr) %>%
    mutate(
      risk_eau = if_else(!is.na(eau_risk) & eau_risk == "high_risk",
                         "high_risk", "low_risk")
    )

  # Base (EAU only) ROC for this transition
  rd_eau <- tl %>%
    mutate(
      actual = case_when(
        had_next_event == 1 ~ 1L,
        had_next_event == 0 & time_to_next_years >= follow_up_years ~ 0L,
        TRUE ~ NA_integer_
      ),
      predicted = if_else(risk_eau == "high_risk", 1, 0)
    ) %>%
    drop_na(actual, predicted)

  if (nrow(rd_eau) < 10 || length(unique(rd_eau$actual)) < 2) next

  ro_eau <- roc(rd_eau$actual, rd_eau$predicted, quiet = TRUE)
  auc_eau <- round(as.numeric(auc(ro_eau)), 3)

  m_eau <- extract_metrics_grid(ro_eau, "\u22651 subsequent stone event", rd_eau) %>%
    mutate(
      Transition      = tr,
      Risk_Definition = "EAU Only",
      Count_Threshold = NA_integer_
    )
  pertr_metrics_list[[paste(tr, "EAU_Only", sep = "_")]] <- m_eau

  roc_overlay_df <- data.frame(
    fpr = 1 - ro_eau$specificities,
    tpr = ro_eau$sensitivities,
    Definition = paste0("EAU Only (AUC=", auc_eau, ")")
  )

  # Sweep count thresholds
  for (ct in count_thresholds) {

    tl2 <- tl %>%
      mutate(
        recurrent_count = from_event_num >= ct,
        risk_combined = if_else(
          !is.na(eau_risk) & (eau_risk == "high_risk" | recurrent_count),
          "high_risk", "low_risk"
        )
      )

    rd_c <- tl2 %>%
      mutate(
        actual = case_when(
          had_next_event == 1 ~ 1L,
          had_next_event == 0 & time_to_next_years >= follow_up_years ~ 0L,
          TRUE ~ NA_integer_
        ),
        predicted = if_else(risk_combined == "high_risk", 1, 0)
      ) %>%
      drop_na(actual, predicted)

    # If the count threshold does not discriminate within this transition
    # (i.e. everyone in the transition satisfies or fails it), the combined
    # classifier collapses to EAU-only or to "all high risk" — record but
    # mark as not-applicable-for-discrimination.
    all_count_same <- length(unique(rd_c$predicted)) < 2 &&
                      all((tl2$from_event_num >= ct) == (tl2$from_event_num[1] >= ct))

    if (nrow(rd_c) < 10 || length(unique(rd_c$actual)) < 2) next

    ro_c <- roc(rd_c$actual, rd_c$predicted, quiet = TRUE)
    auc_c <- round(as.numeric(auc(ro_c)), 3)

    m_c <- extract_metrics_grid(ro_c,
                                "\u22651 subsequent stone event",
                                rd_c) %>%
      mutate(
        Transition      = tr,
        Risk_Definition = paste0("EAU + \u2265", ct, " events"),
        Count_Threshold = ct
      )
    pertr_metrics_list[[paste(tr, "count", ct, sep = "_")]] <- m_c

    roc_overlay_df <- rbind(
      roc_overlay_df,
      data.frame(
        fpr = 1 - ro_c$specificities,
        tpr = ro_c$sensitivities,
        Definition = paste0("EAU + \u2265", ct, " events (AUC=", auc_c, ")")
      )
    )

    # DeLong
    dl <- tryCatch(
      roc.test(ro_eau, ro_c, method = "delong"),
      error = function(e) NULL
    )
    pertr_delong_rows[[paste(tr, ct, sep = "_")]] <- data.frame(
      Transition      = tr,
      Count_Threshold = ct,
      Risk_Definition = paste0("EAU + \u2265", ct, " events"),
      delong_p        = if (is.null(dl)) NA_real_ else as.numeric(dl$p.value)
    )
  }

  # ROC overlay plot
  p_roc <- ggplot(roc_overlay_df,
                  aes(x = fpr, y = tpr, colour = Definition)) +
    geom_line(linewidth = 1) +
    geom_abline(linetype = "dashed", alpha = 0.5) +
    coord_equal() +
    labs(
      x = "False Positive Rate",
      y = "True Positive Rate",
      title = paste0("ROC: Transition ", tr,
                     " \u2014 EAU vs EAU + prior event count"),
      colour = "Risk Definition"
    ) +
    scale_colour_manual(values = c("#7570b3", "#d95f02", "#1b9e77", "#e7298a")) +
    theme_bw(base_size = 12) +
    theme(legend.position = "bottom") +
    guides(colour = guide_legend(nrow = 2))

  safe_tr <- gsub("\u2192", "to", tr)
  pertr_roc_plots[[paste0("transition_", safe_tr)]] <- p_roc
}

pertr_metrics_df <- bind_rows(pertr_metrics_list) %>%
  mutate(
    Transition = factor(Transition,
                        levels = c("1\u21922", "2\u21923", "3\u21924", "4\u21925")),
    Risk_Definition = factor(
      Risk_Definition,
      levels = c("EAU Only",
                 "EAU + \u22652 events",
                 "EAU + \u22653 events",
                 "EAU + \u22654 events")
    )
  )

pertr_delong_df <- bind_rows(pertr_delong_rows) %>%
  mutate(delong_p_fmt = ifelse(is.na(delong_p), NA,
                               ifelse(delong_p < 0.001, "<0.001",
                                      sprintf("%.3f", delong_p))))

cat("Per-transition sweep complete:",
    nrow(pertr_metrics_df), "classifier x transition rows.\n")
```

### ROC Overlays per Transition

```{r eau-vs-count-roc-plots, fig.width=9, fig.height=7, warning=FALSE}
for (nm in names(pertr_roc_plots)) {
  cat("\n#### ", gsub("transition_", "Transition ", nm), "\n")
  print(pertr_roc_plots[[nm]])
  cat("\n")
}
```

### Metrics Table (Per Transition)

```{r eau-vs-count-metrics-table, warning=FALSE}
pertr_metrics_df %>%
  left_join(pertr_delong_df %>%
              dplyr::select(Transition, Risk_Definition, delong_p_fmt),
            by = c("Transition", "Risk_Definition")) %>%
  dplyr::select(Transition, Risk_Definition,
                N, N_High_Risk, N_Low_Risk,
                AUC, delong_p_fmt,
                Sensitivity, Specificity, PPV, NPV) %>%
  arrange(Transition, Risk_Definition) %>%
  gt() %>%
  tab_header(title = "Per-Transition: EAU Only vs EAU + Prior Event Count (no time cutoff)",
             subtitle = "DeLong p-value compares each combined classifier to EAU Only within the same transition") %>%
  gt_theme_espn()
```

## Pooled: One Row per Participant (Latest Transition)

To obtain a single pooled AUC comparison, we take each participant's **latest** available transition — i.e. the highest `from_event_num` for which they have either an observed next event or ≥ `follow_up_years` of follow-up. This preserves independence (one row per participant) while letting `from_event_num` vary.

```{r eau-vs-count-pooled-build, warning=FALSE, message=FALSE}
pooled_df <- transitions_long %>%
  mutate(
    usable = case_when(
      had_next_event == 1 ~ TRUE,
      had_next_event == 0 & time_to_next_years >= follow_up_years ~ TRUE,
      TRUE ~ FALSE
    )
  ) %>%
  filter(usable) %>%
  group_by(participant_id) %>%
  arrange(desc(from_event_num)) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(
    actual = case_when(
      had_next_event == 1 ~ 1L,
      had_next_event == 0 & time_to_next_years >= follow_up_years ~ 0L,
      TRUE ~ NA_integer_
    ),
    risk_eau = if_else(!is.na(eau_risk) & eau_risk == "high_risk",
                       "high_risk", "low_risk")
  ) %>%
  drop_na(actual)

cat("Pooled analysis N =", nrow(pooled_df),
    "unique participants\n",
    "  from_event_num distribution:\n")
print(table(pooled_df$from_event_num))
```

```{r eau-vs-count-pooled-metrics, warning=FALSE, message=FALSE}
pooled_metrics_list <- list()
pooled_roc_list     <- list()
pooled_roc_overlay  <- data.frame()
pooled_delong_rows  <- list()

# EAU Only baseline
rd_eau_p <- pooled_df %>%
  mutate(predicted = if_else(risk_eau == "high_risk", 1, 0)) %>%
  drop_na(actual, predicted)

ro_eau_p <- roc(rd_eau_p$actual, rd_eau_p$predicted, quiet = TRUE)
auc_eau_p <- round(as.numeric(auc(ro_eau_p)), 3)

pooled_roc_list[["EAU Only"]] <- ro_eau_p

pooled_metrics_list[["EAU_Only"]] <-
  extract_metrics_grid(ro_eau_p,
                       "\u22651 subsequent stone event",
                       rd_eau_p) %>%
  mutate(Risk_Definition = "EAU Only",
         Count_Threshold = NA_integer_)

pooled_roc_overlay <- rbind(
  pooled_roc_overlay,
  data.frame(
    fpr = 1 - ro_eau_p$specificities,
    tpr = ro_eau_p$sensitivities,
    Definition = paste0("EAU Only (AUC=", auc_eau_p, ")")
  )
)

# Sweep count thresholds
for (ct in count_thresholds) {

  rd_c_p <- pooled_df %>%
    mutate(
      recurrent_count = from_event_num >= ct,
      risk_combined = if_else(
        !is.na(eau_risk) & (eau_risk == "high_risk" | recurrent_count),
        "high_risk", "low_risk"
      ),
      predicted = if_else(risk_combined == "high_risk", 1, 0)
    ) %>%
    drop_na(actual, predicted)

  if (length(unique(rd_c_p$predicted)) < 2) next

  ro_c_p <- roc(rd_c_p$actual, rd_c_p$predicted, quiet = TRUE)
  auc_c_p <- round(as.numeric(auc(ro_c_p)), 3)

  pooled_roc_list[[paste0("EAU + \u2265", ct, " events")]] <- ro_c_p

  pooled_metrics_list[[paste0("count_", ct)]] <-
    extract_metrics_grid(ro_c_p,
                         "\u22651 subsequent stone event",
                         rd_c_p) %>%
    mutate(Risk_Definition = paste0("EAU + \u2265", ct, " events"),
           Count_Threshold = ct)

  pooled_roc_overlay <- rbind(
    pooled_roc_overlay,
    data.frame(
      fpr = 1 - ro_c_p$specificities,
      tpr = ro_c_p$sensitivities,
      Definition = paste0("EAU + \u2265", ct, " events (AUC=", auc_c_p, ")")
    )
  )

  dl_p <- tryCatch(
    roc.test(ro_eau_p, ro_c_p, method = "delong"),
    error = function(e) NULL
  )
  pooled_delong_rows[[as.character(ct)]] <- data.frame(
    Count_Threshold = ct,
    Risk_Definition = paste0("EAU + \u2265", ct, " events"),
    delong_p        = if (is.null(dl_p)) NA_real_ else as.numeric(dl_p$p.value)
  )
}

pooled_metrics_df <- bind_rows(pooled_metrics_list) %>%
  mutate(Risk_Definition = factor(
    Risk_Definition,
    levels = c("EAU Only",
               "EAU + \u22652 events",
               "EAU + \u22653 events",
               "EAU + \u22654 events")
  ))

pooled_delong_df <- bind_rows(pooled_delong_rows) %>%
  mutate(delong_p_fmt = ifelse(is.na(delong_p), NA,
                               ifelse(delong_p < 0.001, "<0.001",
                                      sprintf("%.3f", delong_p))))

cat("Pooled sweep complete.\n")
```

### Pooled ROC Overlay

```{r eau-vs-count-pooled-roc, fig.width=9, fig.height=7, warning=FALSE}
pooled_roc_plot <- ggplot(pooled_roc_overlay,
                          aes(x = fpr, y = tpr, colour = Definition)) +
  geom_line(linewidth = 1) +
  geom_abline(linetype = "dashed", alpha = 0.5) +
  coord_equal() +
  labs(
    x = "False Positive Rate",
    y = "True Positive Rate",
    title = "Pooled ROC: EAU vs EAU + Prior Event Count (no time cutoff)",
    subtitle = paste0("N = ", nrow(pooled_df),
                      " (one row per participant, latest observed transition)"),
    colour = "Risk Definition"
  ) +
  scale_colour_manual(values = c("#7570b3", "#d95f02", "#1b9e77", "#e7298a")) +
  theme_bw(base_size = 12) +
  theme(legend.position = "bottom") +
  guides(colour = guide_legend(nrow = 2))

pooled_roc_plot
```

### Pooled Metrics Table

```{r eau-vs-count-pooled-table, warning=FALSE}
pooled_metrics_df %>%
  left_join(pooled_delong_df %>%
              dplyr::select(Risk_Definition, delong_p_fmt),
            by = "Risk_Definition") %>%
  dplyr::select(Risk_Definition,
                N, N_High_Risk, N_Low_Risk,
                AUC, delong_p_fmt,
                Sensitivity, Specificity, PPV, NPV) %>%
  arrange(Risk_Definition) %>%
  gt() %>%
  tab_header(title = "Pooled: EAU Only vs EAU + Prior Event Count (no time cutoff)",
             subtitle = "DeLong p-value compares each combined classifier to EAU Only") %>%
  gt_theme_espn()
```

## Save Outputs

```{r eau-vs-count-save, warning=FALSE}
# Per-transition outputs
write.csv(
  pertr_metrics_df %>%
    left_join(pertr_delong_df %>%
                dplyr::select(Transition, Risk_Definition, delong_p),
              by = c("Transition", "Risk_Definition")) %>%
    dplyr::select(Transition, Risk_Definition, Count_Threshold,
                  N, N_High_Risk, N_Low_Risk,
                  AUC_val, AUC_lo, AUC_hi, delong_p,
                  Sensitivity_val, Sensitivity_lo, Sensitivity_hi,
                  Specificity_val, Specificity_lo, Specificity_hi,
                  PPV_val, PPV_lo, PPV_hi,
                  NPV_val, NPV_lo, NPV_hi),
  "eau_vs_count_no_timecutoff_per_transition.csv",
  row.names = FALSE
)

for (nm in names(pertr_roc_plots)) {
  ggsave(paste0("eau_vs_count_no_timecutoff_roc_", nm, ".pdf"),
         plot = pertr_roc_plots[[nm]], width = 9, height = 7)
}

# Pooled outputs
write.csv(
  pooled_metrics_df %>%
    left_join(pooled_delong_df %>%
                dplyr::select(Risk_Definition, delong_p),
              by = "Risk_Definition") %>%
    dplyr::select(Risk_Definition, Count_Threshold,
                  N, N_High_Risk, N_Low_Risk,
                  AUC_val, AUC_lo, AUC_hi, delong_p,
                  Sensitivity_val, Sensitivity_lo, Sensitivity_hi,
                  Specificity_val, Specificity_lo, Specificity_hi,
                  PPV_val, PPV_lo, PPV_hi,
                  NPV_val, NPV_lo, NPV_hi),
  "eau_vs_count_no_timecutoff_pooled.csv",
  row.names = FALSE
)

ggsave("eau_vs_count_no_timecutoff_pooled_roc.pdf",
       plot = pooled_roc_plot, width = 9, height = 7)

cat("EAU vs count-threshold (no time cutoff) outputs saved.\n")
```

# Does Restricting Inter-Event Time Attenuate the Recurrent-Disease Effect?

Framed as prognostic accuracy: does requiring a short prior inter-event gap change the AUC of the "prior recurrence" classifier? If the any-recurrence signal is genuinely driven by short-gap recurrers, then:

1. Restricting positives to **recent** recurrence (≥2 events AND short gap) should yield a similar or higher AUC than any recurrence.
2. Restricting positives to **distant** recurrence (≥2 events AND long gap) should collapse AUC toward 0.5.
3. Within a subsample of *first-event + distant-recurrence* only, `from_event_num ≥ 2` should no longer discriminate (its AUC 95% CI should cross 0.5).

DeLong's test is used throughout on the pooled, one-row-per-participant sample.

## Build the Pooled Sample (if not already present)

```{r attenuate-pooled-build, warning=FALSE, message=FALSE}
# Re-derive pooled_df to be self-contained (no-op if identical to earlier chunk)
pooled_df <- transitions_long %>%
  mutate(usable = case_when(
    had_next_event == 1 ~ TRUE,
    had_next_event == 0 & time_to_next_years >= follow_up_years ~ TRUE,
    TRUE ~ FALSE)) %>%
  filter(usable) %>%
  group_by(participant_id) %>%
  arrange(desc(from_event_num)) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(actual = case_when(
    had_next_event == 1 ~ 1L,
    had_next_event == 0 & time_to_next_years >= follow_up_years ~ 0L,
    TRUE ~ NA_integer_)) %>%
  drop_na(actual)

cat("Pooled N =", nrow(pooled_df), "\n")
```

## Three Classifiers + DeLong at Each Gap Cutoff

```{r attenuate-delong-sweep, warning=FALSE, message=FALSE}
gap_cutoffs <- c(12, 18, 24)

attenuate_metrics_list <- list()
attenuate_delong_list  <- list()
attenuate_roc_plots    <- list()

for (cutoff in gap_cutoffs) {

  df_c <- pooled_df %>%
    mutate(
      any_rec    = as.integer(from_event_num >= 2),
      recent_rec = as.integer(from_event_num >= 2 &
                              !is.na(prior_gap_months) &
                              prior_gap_months <= cutoff),
      distant_rec = as.integer(from_event_num >= 2 &
                               (is.na(prior_gap_months) |
                                prior_gap_months > cutoff))
    )

  ro_any     <- roc(df_c$actual, df_c$any_rec,     quiet = TRUE)
  ro_recent  <- roc(df_c$actual, df_c$recent_rec,  quiet = TRUE)
  ro_distant <- roc(df_c$actual, df_c$distant_rec, quiet = TRUE)

  # Helper: AUC + 95% CI
  auc_ci <- function(ro) {
    ci <- ci.auc(ro)
    c(auc = as.numeric(auc(ro)),
      lo  = as.numeric(ci[1]),
      hi  = as.numeric(ci[3]))
  }

  s_any     <- auc_ci(ro_any)
  s_recent  <- auc_ci(ro_recent)
  s_distant <- auc_ci(ro_distant)

  rd_any     <- df_c %>% dplyr::rename(predicted = any_rec)
  rd_recent  <- df_c %>% dplyr::rename(predicted = recent_rec)
  rd_distant <- df_c %>% dplyr::rename(predicted = distant_rec)

  m_any <- extract_metrics_grid(ro_any,
    "\u22651 subsequent stone event", rd_any) %>%
    mutate(Gap_Cutoff_Months = cutoff,
           Classifier = "Any recurrence (\u22652 events)")
  m_recent <- extract_metrics_grid(ro_recent,
    "\u22651 subsequent stone event", rd_recent) %>%
    mutate(Gap_Cutoff_Months = cutoff,
           Classifier = paste0("Recent recurrence (gap \u2264", cutoff, "mo)"))
  m_distant <- extract_metrics_grid(ro_distant,
    "\u22651 subsequent stone event", rd_distant) %>%
    mutate(Gap_Cutoff_Months = cutoff,
           Classifier = paste0("Distant recurrence (gap >", cutoff, "mo)"))

  attenuate_metrics_list[[paste0("cut_", cutoff)]] <-
    bind_rows(m_any, m_recent, m_distant)

  # DeLong tests
  dl_any_vs_recent  <- tryCatch(roc.test(ro_any, ro_recent,  method = "delong"),
                                error = function(e) NULL)
  dl_any_vs_distant <- tryCatch(roc.test(ro_any, ro_distant, method = "delong"),
                                error = function(e) NULL)
  dl_recent_vs_dist <- tryCatch(roc.test(ro_recent, ro_distant, method = "delong"),
                                error = function(e) NULL)

  attenuate_delong_list[[paste0("cut_", cutoff)]] <- data.frame(
    Gap_Cutoff_Months = cutoff,
    Comparison = c("Any vs Recent", "Any vs Distant", "Recent vs Distant"),
    delong_p = c(
      if (is.null(dl_any_vs_recent))  NA_real_ else as.numeric(dl_any_vs_recent$p.value),
      if (is.null(dl_any_vs_distant)) NA_real_ else as.numeric(dl_any_vs_distant$p.value),
      if (is.null(dl_recent_vs_dist)) NA_real_ else as.numeric(dl_recent_vs_dist$p.value)
    )
  )

  cat(sprintf(
    "\n--- Gap cutoff: %dmo ---\n  Any    AUC = %.3f (%.3f, %.3f)\n  Recent AUC = %.3f (%.3f, %.3f)\n  Distant AUC = %.3f (%.3f, %.3f)\n  DeLong Any vs Recent:  p = %s\n  DeLong Any vs Distant: p = %s\n  DeLong Recent vs Distant: p = %s\n",
    cutoff,
    s_any["auc"], s_any["lo"], s_any["hi"],
    s_recent["auc"], s_recent["lo"], s_recent["hi"],
    s_distant["auc"], s_distant["lo"], s_distant["hi"],
    ifelse(is.null(dl_any_vs_recent),  "NA", format.pval(dl_any_vs_recent$p.value,  digits = 3)),
    ifelse(is.null(dl_any_vs_distant), "NA", format.pval(dl_any_vs_distant$p.value, digits = 3)),
    ifelse(is.null(dl_recent_vs_dist), "NA", format.pval(dl_recent_vs_dist$p.value, digits = 3))
  ))

  # ROC overlay plot
  auc_any_r     <- round(s_any["auc"],     3)
  auc_recent_r  <- round(s_recent["auc"],  3)
  auc_distant_r <- round(s_distant["auc"], 3)

  roc_ov <- rbind(
    data.frame(fpr = 1 - ro_any$specificities,
               tpr = ro_any$sensitivities,
               Classifier = paste0("Any recurrence (AUC=", auc_any_r, ")")),
    data.frame(fpr = 1 - ro_recent$specificities,
               tpr = ro_recent$sensitivities,
               Classifier = paste0("Recent recurrence \u2264",
                                   cutoff, "mo (AUC=", auc_recent_r, ")")),
    data.frame(fpr = 1 - ro_distant$specificities,
               tpr = ro_distant$sensitivities,
               Classifier = paste0("Distant recurrence >",
                                   cutoff, "mo (AUC=", auc_distant_r, ")"))
  )

  p_roc <- ggplot(roc_ov, aes(x = fpr, y = tpr, colour = Classifier)) +
    geom_line(linewidth = 1) +
    geom_abline(linetype = "dashed", alpha = 0.5) +
    coord_equal() +
    labs(x = "False Positive Rate", y = "True Positive Rate",
         title = paste0("Does the time restriction attenuate the effect? ",
                        "Gap cutoff ", cutoff, "mo"),
         subtitle = paste0("Pooled N = ", nrow(pooled_df),
                           " (one row per participant, latest transition)"),
         colour = "Classifier") +
    scale_colour_manual(values = c("#1b9e77", "#d95f02", "#7570b3")) +
    theme_bw(base_size = 12) +
    theme(legend.position = "bottom") +
    guides(colour = guide_legend(nrow = 3))

  attenuate_roc_plots[[paste0("cut_", cutoff)]] <- p_roc
}

attenuate_metrics_df <- bind_rows(attenuate_metrics_list)
attenuate_delong_df  <- bind_rows(attenuate_delong_list) %>%
  mutate(delong_p_fmt = ifelse(is.na(delong_p), NA,
                               ifelse(delong_p < 0.001, "<0.001",
                                      sprintf("%.3f", delong_p))))
```

### ROC Overlays

```{r attenuate-roc-plots, fig.width=9, fig.height=7, warning=FALSE}
for (nm in names(attenuate_roc_plots)) print(attenuate_roc_plots[[nm]])
```

### AUC + CI Table

```{r attenuate-auc-table, warning=FALSE}
attenuate_metrics_df %>%
  dplyr::select(Gap_Cutoff_Months, Classifier,
                N, N_High_Risk, N_Low_Risk,
                AUC, Sensitivity, Specificity, PPV, NPV) %>%
  arrange(Gap_Cutoff_Months, Classifier) %>%
  gt() %>%
  tab_header(title = "Time-restriction attenuation test: AUC + metrics per classifier",
             subtitle = "Pooled (one row per participant, latest transition)") %>%
  gt_theme_espn()
```

### DeLong Comparisons

```{r attenuate-delong-table, warning=FALSE}
attenuate_delong_df %>%
  dplyr::select(Gap_Cutoff_Months, Comparison, delong_p_fmt) %>%
  gt() %>%
  tab_header(title = "DeLong comparisons across classifiers",
             subtitle = "Tests whether the time restriction changes AUC vs any-recurrence") %>%
  gt_theme_espn()
```

## Subgroup Test: Is `from_event_num ≥ 2` Still Informative Among Long-Gap Recurrers?

Within a subsample consisting of **first-event cases + distant-recurrence cases only**, we test whether the event-count classifier retains predictive value. If the confidence interval for AUC crosses 0.5, the "attenuates" wording is supported.

```{r attenuate-subgroup, warning=FALSE, message=FALSE}
attenuate_subgroup_list <- list()

for (cutoff in gap_cutoffs) {

  sub_df <- pooled_df %>%
    filter(
      from_event_num == 1 |
      (from_event_num >= 2 & (is.na(prior_gap_months) | prior_gap_months > cutoff))
    ) %>%
    mutate(predicted = as.integer(from_event_num >= 2))

  if (length(unique(sub_df$predicted)) < 2 ||
      length(unique(sub_df$actual))    < 2) next

  ro_sub <- roc(sub_df$actual, sub_df$predicted, quiet = TRUE)
  ci_sub <- ci.auc(ro_sub)

  # Bootstrap p-value for AUC vs 0.5
  n_boot <- 1000
  set.seed(42)
  boot_aucs <- replicate(n_boot, {
    idx <- sample(seq_len(nrow(sub_df)), replace = TRUE)
    boot_df <- sub_df[idx, ]
    if (length(unique(boot_df$actual)) < 2) return(NA_real_)
    as.numeric(auc(roc(boot_df$actual, boot_df$predicted, quiet = TRUE)))
  })
  boot_aucs <- boot_aucs[!is.na(boot_aucs)]
  # Two-sided empirical p-value vs null of 0.5
  p_vs_half <- 2 * min(mean(boot_aucs <= 0.5), mean(boot_aucs >= 0.5))

  m_sub <- extract_metrics_grid(ro_sub,
    "\u22651 subsequent stone event", sub_df) %>%
    mutate(Gap_Cutoff_Months = cutoff,
           N_total = nrow(sub_df),
           boot_p_vs_0.5 = p_vs_half)

  attenuate_subgroup_list[[paste0("cut_", cutoff)]] <- m_sub

  cat(sprintf(
    "\nSubgroup (first-event + distant recurrence), gap > %dmo\n  N = %d   AUC = %.3f (%.3f, %.3f)   boot p vs 0.5 = %.3f\n",
    cutoff, nrow(sub_df),
    as.numeric(auc(ro_sub)), ci_sub[1], ci_sub[3], p_vs_half
  ))
}

attenuate_subgroup_df <- bind_rows(attenuate_subgroup_list)

attenuate_subgroup_df %>%
  dplyr::select(Gap_Cutoff_Months, N_total, N_High_Risk, N_Low_Risk,
                AUC, boot_p_vs_0.5, Sensitivity, Specificity, PPV, NPV) %>%
  mutate(boot_p_vs_0.5 = ifelse(boot_p_vs_0.5 < 0.001, "<0.001",
                                sprintf("%.3f", boot_p_vs_0.5))) %>%
  gt() %>%
  tab_header(title = "Subgroup: event-count classifier restricted to long-gap recurrers + first-event cases",
             subtitle = "AUC CI crossing 0.5 OR bootstrap p > 0.05 supports 'attenuates' wording") %>%
  gt_theme_espn()
```

## Save Attenuation-Test Outputs

```{r attenuate-save, warning=FALSE}
write.csv(attenuate_metrics_df,
          "attenuation_test_auc_metrics.csv", row.names = FALSE)
write.csv(attenuate_delong_df,
          "attenuation_test_delong.csv", row.names = FALSE)
write.csv(attenuate_subgroup_df,
          "attenuation_test_subgroup.csv", row.names = FALSE)

for (nm in names(attenuate_roc_plots)) {
  ggsave(paste0("attenuation_test_roc_", nm, ".pdf"),
         plot = attenuate_roc_plots[[nm]], width = 9, height = 7)
}

cat("attenuation-test outputs saved.\n")
```
